### 2017-04-20 src/problem.tex
problem definition

We are given a virtual DAG $D_v = (V_v, A_v)$ 
with a source and destination vertices $s_v, t_v$ respectively, 
a physical DAG $D_p = (V_p, A_p)$
with a source and destination vertices $s_p, t_p$ respectively,
demand functions $p_d : V_v \to \R$, $b_d : E_v \to \R$,
capacity functions $p_c : V_p \to \R$, $b_c : E_p \to \R$,
and a cost function $c: V_v \times V_p \to \R$.

Given a virtual $s_vt_v$-path $p$ of length $l$,
let $i_1, \ldots, i_l$ be the indices of the vertices of this path.
We denote a partition of $p$ into subpaths by the indices of the last vertex in
each subpath i.e. we use $j_1, \ldots, j_k$ to denote the partition 
$((v_{i_1}, \ldots, v_{i_{j_1}}), \ldots, (v_{i_{j_{k-1} + 1}}, \ldots,
v_{i_{j_k}}))$.
Given a partition $(j_1, \ldots, j_k)$ we denote by $V(j_i)$ the vertices of the
$i$th subpath.
A (feasible) \emph{embedding} of a virtual path into the physical DAG 
w.r.t partition $P = (j_1, \ldots,j_k)$ is a mapping $e_P : P \to V_p$ such that
for all $1 \leq i \leq k$ it holds that:
\begin{enumerate}
  \item $p_c(e_P(j_i)) \geq \sum_{v \in V(j_i)} p_d(v)$
  \item There is a physical path from $e_P(j_i)$ to $e_P(j_{i+1})$ with a
  bottleneck at least $b_d(v_{j_i}, v_{j_{i+1}})$.
\end{enumerate}
The \emph{cost} of a (feasible) embedding, $e_P$ is given by:
$\sum_{i = 1}^k \sum_{v \in V(j_i)} c(v, e_P(j_i))$.

In the \todo{choose a name for the problem} VPN problem the goal is to find a
feasible embedding of a virtual path into the physical DAG that minimizes the
cost.

\begin{figure}[ht]
\centering
\scalebox{.87}{
\input{fig-embedding}
}

\end{figure}

### 2017-04-26 src/hardness.tex
going to sleep

In this section we show that the problem in its general form cannot be
approximated at all assuming $P \neq NP$.
We also show that the problem remains NP-hard even when restricted to DAGS.

Consider the problem in its general form. 
Given an undirected graph $G$

### 2017-04-26 src/problem.tex
moved to lualatex
going to sleep

@@
 We are given a virtual DAG $D_v = (V_v, A_v)$ 
-with a source and destination vertices $s_v, t_v$ respectively, 
+with source and destination vertices $s_v, t_v$ respectively, 
 a physical DAG $D_p = (V_p, A_p)$
-with a source and destination vertices $s_p, t_p$ respectively,
+with source and destination vertices $s_p, t_p$ respectively,
 demand functions $p_d : V_v \to \R$, $b_d : E_v \to \R$,
@@
 \centering
-\scalebox{.87}{
+\scalebox{1}{
 \input{fig-embedding}

### 2017-04-26 src/fig-reduction.tex
adding hardness

\begin{tikzpicture}[every node/.style={default node}, very thick]

\begin{scope}[layered layout, grow=right, sibling distance=2cm, level distance=2cm]

\node(v1p) {$v_1^+$};
\node(v1m) {$v_1^+$};
\node(v2p) {$v_2^-$};
\node(v2m) {$v_2^-$};
\node[clear node, inner sep=5mm](dotsp) {$\ldots$};
\node[clear node, inner sep=5mm](dotsm) {$\ldots$};
\node(vnp) {$v_n^-$};
\node(vnm) {$v_n^-$};

\graph{
	s -> {(v1p), (v1m)};
	(v1p) -> {(v2p), (v2m)};
	(v1m) -> {(v2p), (v2m)};
	(v2p) -> {(dotsp), (dotsm)};
	(v2m) -> {(dotsp), (dotsm)};
	(dotsp) -> {(vnp), (vnm)};
	(dotsm) -> {(vnp), (vnm)};
	{(vnp), (vnm)} -> t;
};

\end{scope}

\end{tikzpicture}

### 2017-04-26 src/hardness.tex
adding hardness

@@
 approximated at all assuming $P \neq NP$.
+\todo{Is it true ?}
 We also show that the problem remains NP-hard even when restricted to DAGS.
@@
 Given an undirected graph $G$
+\todo{finish}
+
+We now show that the problem restricted to DAG is still NP-hard.
+We present a polynomial reduction from partition.
+Let $\{a_1, \ldots, a_n\}$ be an instance of the partition problem, 
+consider the instance of the VPN problem 
+$D_v = (V_v, A_v), D_p = ({v}, \emptyset)$, 
+where:
+\begin{align}
+V_v = \{s, t\} \cup \{v_1^+, \ldots, v_n^+\} \cup \{v_1^-, \ldots, v_n^-\}
+\\
+A_v = \{\{v_i^+, v_i^-\} \times \{v_{i + 1}^+, v_{i + 1}^-\}\} 
+\cup \{(s, v_1^+), (s, v_1^-), (v_n^+, t), (v_n^-, t)\}
+&&
+\forall i \in [n-1]
+\\
+p_d(v_i^+) = a_i && \forall i \in [n]
+\\
+p_d(v_i^-) = 0 && \forall i \in [n]
+\\
+c(v_i^+, v) = 0 && \forall i \in [n]
+\\
+c(v_i^-, v) = a_i && \forall i \in [n] 
+\\
+p_c(v) = \inv{2}\sum_{i = 1}^n a_i
+\end{align}
+Note that the bandwidth function does not plays a role here because the physical graph
+is just a single vertex.
+
+The following figure illustrate the reduction.
+\begin{figure}[ht]
+\centering
+\input{fig-reduction}
+\end{figure}

### 2017-04-26 src/main.tex
adding hardness

\nonstopmode
\documentclass[draft]{article}

\input{libs}
\input{def}
\input{tikz}

\input{title}
\input{authors}

\begin{document}
\maketitle

\input{outline}

\bibliographystyle{plain}
\bibliography{main}

\end{document}

### 2017-04-26 src/problem.tex
adding hardness

@@
 $i$th subpath.
-A (feasible) \emph{embedding} of a virtual path into the physical DAG 
-w.r.t partition $P = (j_1, \ldots,j_k)$ is a mapping $e_P : P \to V_p$ such that
+A (feasible) \emph{embedding} of a virtual path into the physical graph 
+w.r.t partition $P = (j_1, \ldots,j_k)$ is a mapping $\psi : P \to V_p$ such that
 for all $1 \leq i \leq k$ it holds that:
 \begin{enumerate}
-  \item $p_c(e_P(j_i)) \geq \sum_{v \in V(j_i)} p_d(v)$
-  \item There is a physical path from $e_P(j_i)$ to $e_P(j_{i+1})$ with a
+  \item $p_c(\psi(j_i)) \geq \sum_{v \in V(j_i)} p_d(v)$
+  \item There is a physical path, $\pi_i$ from $\psi(j_i)$ to $\psi(j_{i+1})$ with a
   bottleneck at least $b_d(v_{j_i}, v_{j_{i+1}})$.

### 2017-04-26 src/algorithm.tex
done for today

In this section we present an FPTAS algorithm to the VPN problem.
We are given an instance of the VPN problem 
\begin{align}
D_v = (V_v, A_v)			\\
D_p = (V_p, A_p)			\\
(s_v, t_v, s_p, t_p)	\\
(p_d, b_d, p_c, b_c)	\\
c
\end{align}
For now assume all values are integral and polynomial bounded in the size of the input.
Sort the DAGs topologically and assume w.l.o.g that $s_v = s_p = 1$,
$t_v = n$, and $t_p = m$.
Let $O(i, j)$ be the optimal embedding of any $1i$ virtual path, 
into a $1j$ physical path.
We can compute $O(i, j)$ as follow:
$$
O(i, j) = \min_{a \text{ ancestor of } i} \min_{b \text{ ancestor of } j} O(a, b)
+ \min_(ai, bj)
$$
Where $\min(ai, bj)$ is the optimal embedding of a virtual 
path starting at any child of $a$, $a'$ and ending at $i$ into node $j$
that respect the bottleneck constraint, i.e. $b_d(a, a') \leg bn(b, j)$.
\todo{define bn(i, j) to be the bottleneck between i and j}
We claim that $\min(ai, bj)$ can be found efficiently 
\todo{describe how}

\todo{argue about scaling and rounding}

### 2017-04-26 src/latency.tex
done for today

\todo{Are we going to talk about the problem also with latency constraint ?}

### 2017-04-27 src/algorithm.tex
latency

@@
 For now assume all values are integral and polynomial bounded in the size of the input.
-Sort the DAGs topologically and assume w.l.o.g that $s_v = s_p = 1$,
-$t_v = n$, and $t_p = m$.
-Let $O(i, j)$ be the optimal embedding of any $1i$ virtual path, 
-into a $1j$ physical path.
-We can compute $O(i, j)$ as follow:
-$$
-O(i, j) = \min_{a \text{ ancestor of } i} \min_{b \text{ ancestor of } j} O(a, b)
-+ \min_(ai, bj)
-$$
-Where $\min(ai, bj)$ is the optimal embedding of a virtual 
-path starting at any child of $a$, $a'$ and ending at $i$ into node $j$
-that respect the bottleneck constraint, i.e. $b_d(a, a') \leg bn(b, j)$.
+
+We start with the following:
+For an ancestor $a_v$ of $t'_v$ denote by $C(a_v)$ its children.
+Let $a_p$ be an ancestor of $t'_p$ we want to find an embedding of minimum cost
+of some virtual $c_vt'_v$-path into the node $t'_p$, 
+where $c_v \in C(a_v)$.
+Observe that once $c_v$ is chosen the arc $(a_v, c_v)$ determines completely
+whether a physical path with a feasible bottleneck exists, namely, a physical
+path exists if and only if there is a physical $s'_vt'_v$-path containing only
+arcs with bandwidth at least $b_d(a_v, c_v)$.
+On the other hand, the set of $c_vt'_v$-paths
+determine completely the cost (and processing-wise feasibility) of the embedding.
+Among all the $c_vt'_v$-paths we want to select the one that minimize the
+embedding cost under the processing capacity constraints.
+Figure \todo{} depicts the above observations.
+
+\begin{figure}[ht]
+\centering
+\input{fig-dp}
+\end{figure}
+
 \todo{define bn(i, j) to be the bottleneck between i and j}

### 2017-04-27 src/fig-dp.tex
latency

\begin{tikzpicture}[every node/.style={default node}, very thick, -latex]

\node[clear node] at(-3, 0) {$\dots$};

\node(s) at(-2,0) {$a_v$};

\node(c1) at(1,1) {$c_1$};
\node[clear node] at (2,0) {$\vdots$};
\node(c2) at(1,-1) {$c_d$};

\node(t) at(5, 0) {$t'_v$};

\node[clear node] at(6, 0) {$\dots$};

\draw (s) to[] (c1);
\draw (s) to[]
node[clear node, pos=0.5](c1n){}
(c2);

\begin{scope}[path]
\draw[decorate] (c1.north) to[out=90, in=90] (t.north east);
\draw[decorate] (c1) to[out=45, in=135] (t);
\draw[decorate] (c1.south east) to[out=0, in=135] (t.south west);

\draw[decorate] (c2.north east) to[out=0, in=-135] (t.north west);
\draw[decorate] (c2) to[out=-45, in=-135] (t);
\draw[decorate] (c2.south) to[out=-90,in=-90] (t.south east);
\end{scope}

\draw[group]
(c2.west)		to[out=-90,in=-90, looseness=1.8] node[clear node, pos=0.9](j){}
(t.east)		to[out=90,in=0]
(t.north)		to[out=180,in=45]
(c2.north west)	to[out=-135,in=90]
(c2.west)
;

\node[clear node] at (-3,-5) {$\dots$};

\node(sp) at(-2, -5) {$s'_p$};
\node(tp) at(5, -5) {$t'_p$};

\node[clear node] at (6,-5) {$\dots$};

\begin{scope}[path]
\draw[decorate]	(sp.north east) to[bend left] 
node[pos=0.5, clear node](p1){}
(tp.north west)
;
\draw[decorate] (sp) to[] 
node[pos=0.3, clear node](p2){}
(tp);
\draw[decorate]	(sp.south east) to[bend right] (tp.south west);
\end{scope}

\draw[group, ->] (j) to[bend left] (tp);

\begin{scope}[blue, -Rays, every to/.style={bend right}]
\draw (c1n) to[] (p1);
\draw (c1n) to[] (p2);
\end{scope}
\end{tikzpicture}

### 2017-04-27 src/latency.tex
latency

@@
 \todo{Are we going to talk about the problem also with latency constraint ?}
+We now extend the problem by adding a global latency constraint.
+Formally, we are given a latency function $l : A_v \times A_p \to \R$,
+and a latency constraint $L$.
+The goal is to find a min-cost embedding that also respect the latency
+constraint.
+Observe that given two physical vertices $s_p$, $t_p$ and a virtual edge $e_v$
+a $s_pt_p$-path that minimize the latency can be efficiently found by using any
+standard shortest path algorithm where the "distance" function is replaced by
+the appropriate latency.
+Observe that this can also be done if we restrict ourselves to use only physical
+edges with a lower bound on their bandwidth.
+We now show that if all values are integral and polynomial bounded, we can
+efficiently find a feasible embedding with a cost bounded by $C$ that minimize
+the latency.
+
+Let $O(t'_v, t'_p, C)$ be an embedding of some virtual $s_vt'_v$-path 
+into a physical $s_pt'_p$-path that has cost not more than $C$ and that
+minimizes the latency.

### 2017-04-27 src/algorithm.tex
foo

@@
 (s_v, t_v, s_p, t_p)	\\
-(p_d, b_d, p_c, b_c)	\\
-c
+(p_d, b_d, p_c, b_c, c)	\\
 \end{align}
@@
 
-We start with the following:
-For an ancestor $a_v$ of $t'_v$ denote by $C(a_v)$ its children.
-Let $a_p$ be an ancestor of $t'_p$ we want to find an embedding of minimum cost
-of some virtual $c_vt'_v$-path into the node $t'_p$, 
-where $c_v \in C(a_v)$.
-Observe that once $c_v$ is chosen the arc $(a_v, c_v)$ determines completely
-whether a physical path with a feasible bottleneck exists, namely, a physical
-path exists if and only if there is a physical $s'_vt'_v$-path containing only
-arcs with bandwidth at least $b_d(a_v, c_v)$.
+For a vertex $v$ let $C(v)$ be the set of its children.
+Let $O'(s'_v, t'_v, s'_p, t'_p)$ be the optimal embedding of some virtual
+$C(s'v)t'_v$-path into the physical vertex $t'_p$ such that the bottleneck
+between $s'_p$ and $t'_p$ is at least $b_d(s'_v, t'_v)$.
+Let $c_v \in C(s'_v)$ and observe that once $c_v$ is chosen the arc 
+$(s'_v, c_v)$ determines completely whether a physical path with a feasible
+bottleneck exists, namely, 
+a physical path exists if and only if there is a physical $s'_vt'_v$-path containing only
+arcs with bandwidth at least $b_d(s'_v, c_v)$.
 On the other hand, the set of $c_vt'_v$-paths
 determine completely the cost (and processing-wise feasibility) of the embedding.
-Among all the $c_vt'_v$-paths we want to select the one that minimize the
-embedding cost under the processing capacity constraints.
 Figure \todo{} depicts the above observations.
@@
 \input{fig-dp}
+\caption[]{
+\begin{enumerate*}
+\item Computing $O'(s'_v, t'_v, s'_p, t'_p)$.
+\item The set of $c_dt'_v$-paths determines completely the cost of the embedding
+\item 
+The arc $(s'_v, c_d)$ determines completely the connectivity of $s'_p$ and
+$t'_p$, i.e. physical arcs with bandwidth less than $b_d(s'_v, c_d)$ can not be
+used.
+\end{enumerate*}
+}
 \end{figure}
 
-\todo{define bn(i, j) to be the bottleneck between i and j}
-We claim that $\min(ai, bj)$ can be found efficiently 
+Among all the $c_vt'_v$-paths we want to select the one that minimize the
+embedding cost under the processing capacity constraints.
+This can be done... 
 \todo{describe how}
+Calculating $O'(s'_v, t'_v, s'_p, t'_p)$ can be done simply by finding the
+optimal path among all children of $s'_v$.
 
+Let $O(t'_v, t'_p)$ be the optimal embedding of some virtual $s_vt'_v$-path
+into some physical $s_pt'_p$-path then $O(t_v, t_p)$ is the global optimal
+embedding.
+Also $O(t'_v, s_p)$ can be computed efficiently for every $t'_v$ as described
+above, and $O(s_v, t'_v)$ is simply the minimum cost of embedding $s_v$ in any
+physical vertex $s'_p$ such that a physical $s'_pt'_v$-path exists.
+For an arbitrary vertices $t'_v$, and $t'_p$, $O(t'_v, t'_p)$ can be computed
+efficiently using dynamic programming with the following recursion formula:
+$$
+O(t'_v, t'_p) = 
+\min_{\substack{
+s'_v \in P(t'_v)
+\\
+s'_p \in P(t'_p)
+}}
+O(s'_v, s'_p) + O'(s'_v, t'_v, s'_p, t'_p)
+$$ 
 \todo{argue about scaling and rounding}

### 2017-04-28 src/hardness.tex
done for today
foo

@@
-In this section we show that the problem in its general form cannot be
-approximated at all assuming $P \neq NP$.
-\todo{Is it true ?}
+The VPN problem, in its general form, can not be approximated at all.
+To see this, consider an instance of the problem where the virtual graph is a simple path of $n = |V_p|$ vertices, $p_d \equiv p_c \equiv 1$, 
+$b_d \equiv b_c \equiv 1$,
+and $c \equiv 0$.
+In this instance any feasible embedding has cost 0, furthermore, one exists if and only if there is an Hamiltonian path in the physical graph.
+Thus, any algorithm that returns a feasible embedding also finds an Hamiltonian path.
+
 We also show that the problem remains NP-hard even when restricted to DAGS.
@@
 \\
-p_c(v) = \inv{2}\sum_{i = 1}^n a_i
+p_c(v) = \frac{1}{2}\sum_{i = 1}^n a_i
 \end{align}
@@
 \end{figure}
+
+\todo{finish}

### 2017-04-28 src/problem.tex
foo

@@
-We are given a virtual DAG $D_v = (V_v, A_v)$ 
+We are given a virtual directed graph $D_v = (V_v, A_v)$ 
 with source and destination vertices $s_v, t_v$ respectively, 
-a physical DAG $D_p = (V_p, A_p)$
+a physical directed graph $D_p = (V_p, A_p)$
 with source and destination vertices $s_p, t_p$ respectively,
@@
   bottleneck at least $b_d(v_{j_i}, v_{j_{i+1}})$.
+  \item $\bigcup_{i = 1}^k \pi_i$ is a simple path.
 \end{enumerate}

### 2017-06-18 src/authors.tex
dror

%\author[1]{Gilad Kutiel%
%\thanks{E-mail: \texttt{gkutiel@cs.technion.ac.il}}}

%\author[2]{Dror Rawitz%
%\thanks{Partially supported by the Israel Science Foundation
%  (grant no.~497/14).  E-mail: \texttt{dror.rawitz@biu.ac.il}}}

%\affil[1]{Department of Computer Science, Technion, Haifa, Israel}
%\affil[2]{Faculty of Engineering, Bar Ilan University, Ramt-Gan, Israel}

\author[1]{%
Gilad Kutiel
\and
Dror Rawitz%
\thanks{Partially supported by the Israel Science Foundation
  (grant no.~497/14).  }
}

\institute{%
Department of Computer Science, Technion, Haifa 32000, Israel. \\
\email{gkutiel@cs.technion.ac.il}
\and
Faculty of Engineering, Bar Ilan University, Ramt-Gan 52900, Israel.\\
\email{dror.rawitz@biu.ac.il}
}

### 2017-06-18 src/intro.tex
dror

Computer communication networks are in constant need of expansion to
cope with the ever growing traffic.  As networks grow, management and
maintenance become more and more complicated.
%
Current developments aim to improve the utilization of network
resources include the detachment of network applications from network
infrastructure and the transition from network planning to network
programming.

One aspect of network programming is to manage resources from a
central point of view, namely to make decisions based on availability,
network status, required quality of service, and the identity of the
client.  Hence, a central issue is a central agent that is able to
received reports from network components and client requests, and as a
result can alter the allocation of resources in the networks.  This
approach is called Software Defined Networking (SDN), where there is a
separation between the physical layer and the routing and management
layers.

A complimentary approach is Network Function Virtualization (NFV).
Instead of relying on special purpose machines, network applications
become virtual network functions (VNF) that are executed on generic
machines and can be placed in various locations in the network.
Virtualization increases the flexibility of resource allocation and
thus the utilization of the network resources.
%
Internet Service Providers (ISPs) that provide services to clients
benefit from NFV, since it helps to better utilize their physical
network.  In addition, when network services are virtualized, an ISP
may support \emph{service chaining}, namely a compound service that
consists of a sequence of VNFs.  Furthermore, one may offer a compound
service a service that may be obtained using one of several sequences
of VNFs.

In this paper we study the allocation problem of a compund request for
a service chain in a software-defined network that supports NFV.
Given a (physical) network that contains servers with limited
processing power and of links with limited bandwidth, a service chain
is a sequence of virtual network functions (VNFs) that service a
certain flow request in the network.
%
The allocation of a service chain consists of routing and VNF
placement.  That is, each VNF from the seqeunce is placed in a server
along a path, and it is feasible if each server can handle the VNFs
that are assigned to it, and if each link on the path can carry the
flow that is assigned to it.
%
A request for service is composed of a source and a destination in the
network, an upper bound on the total latency, and a specification of
all service chains that are considered valid for this request.
%
Each pair of server and VNF are associated with a cost for placing the
network function in the server.  This cost measures compatibility of a
VNF to a server (infinite costs means ``incompatible'').  Given a
request, the goal is to find a valid service chain of minimum total
cost or to identify that a valid service chain does not exist.

????? References!!! ?????

?????  Explain one shot approach ?????

\paragraph*{\bf Related work.}
%

\paragraph*{\bf Our results.}
%
We show that even the feasibility problem is NP-hard in general
di-graphs.  Hence we first focus on directed acyclic graphs (DAGs).
We show that the problem is still NP-hard in DAGs and present an
FPTAS.
%
Based on out PTAS, we also provide a randomized algorithm for
instances in which the service chain passes through a bounded number
of servers whose degree is larger than two.

?????

\bigskip

### 2017-06-18 src/problem.tex
fix errors

@@
 
-In the \todo{choose a name for the problem} VPN problem the goal is to find a
+In the Service Chain Placement in SDN problem the goal is to find a
 feasible embedding of a virtual path into the physical DAG that minimizes the
@@
 \centering
-\scalebox{1}{
+\scalebox{.8}{
 \input{fig-embedding}

### 2017-06-18 src/hardness.tex
fix errors
problem + hardness

@@
-The VPN problem, in its general form, can not be approximated at all.
-To see this, consider an instance of the problem where the virtual graph is a simple path of $n = |V_p|$ vertices, $p_d \equiv p_c \equiv 1$, 
+In this section we show that even the feasibility decision problem, 
+i.e. deciding if there is a feasible embedding given a request graph and a
+physical network, 
+is NP-hard.
+This implies that the problem cannot be (multiplicatively) approximated at all.  
+To see this, 
+consider an instance of the problem where the virtual graph is a simple path of 
+$n = |V_p|$ vertices, 
+$p_d \equiv p_c \equiv 1$, 
 $b_d \equiv b_c \equiv 1$,
 and $c \equiv 0$.
-In this instance any feasible embedding has cost 0, furthermore, one exists if and only if there is an Hamiltonian path in the physical graph.
+In this instance any feasible embedding has cost 0, 
+furthermore, 
+one exists if and only if there is an Hamiltonian path in the physical graph.
 Thus, any algorithm that returns a feasible embedding also finds an Hamiltonian path.
 
-We also show that the problem remains NP-hard even when restricted to DAGS.
-
-Consider the problem in its general form. 
-Given an undirected graph $G$
-\todo{finish}
-
-We now show that the problem restricted to DAG is still NP-hard.
-We present a polynomial reduction from partition.
+We also show that the problem remains NP-hard even when the request graph is
+acyclic.
+We present a polynomial reduction from the \textsc{partition problem}.
 Let $\{a_1, \ldots, a_n\}$ be an instance of the partition problem, 
@@
 \end{figure}
-
-\todo{finish}

### 2017-06-18 src/problem.tex
problem + hardness

@@
 
-In the Service Chain Placement in SDN problem the goal is to find a
+In the \VPN problem the goal is to find a
 feasible embedding of a virtual path into the physical DAG that minimizes the
 cost.
+Figure~\ref{fig:problem} illustrate an embedding of a virtual request into a
+physical network.
 
@@
 }
-
+\caption{
+An embedding of a graph representation of a virtual request (on the left) into
+the physical network (on the right).
+The source and destination vertices are dashed, as well as the chosen virtual
+path.
+The numbers on the vertices represent the processing demand and capacity
+respectively, 
+the numbers on the edges represent the bandwidth demand and capacity
+respectively.
+The partition of the virtual path and its embedding are marked by the orange,
+dotted arrows.
+The cost function is not depicts in this figure.
+\label{fig:problem}
+}
 \end{figure}

### 2017-06-18 src/algorithm.tex
fix errors
algo

--- 2017-04-26 src/algorithm.tex
@@
-In this section we present an FPTAS algorithm to the VPN problem.
-We are given an instance of the VPN problem 
-\begin{align}
+In this section we present an FPTAS algorithm to the \VPN problem.
+We are given an instance of the \VPN problem 
+\begin{align*}
 D_v = (V_v, A_v)		\\
@@
 (s_v, t_v, s_p, t_p)	\\
-(p_d, b_d, p_c, b_c)	\\
-c
-\end{align}
+(p_d, b_d, p_c, b_c, c)
+\end{align*}
 For now assume all values are integral and polynomial bounded in the size of the input.
-Sort the DAGs topologically and assume w.l.o.g that $s_v = s_p = 1$,
-$t_v = n$, and $t_p = m$.
-Let $O(i, j)$ be the optimal embedding of any $1i$ virtual path, 
-into a $1j$ physical path.
-We can compute $O(i, j)$ as follow:
-$$
-O(i, j) = \min_{a \text{ ancestor of } i} \min_{b \text{ ancestor of } j} O(a, b)
-+ \min_(ai, bj)
-$$
-Where $\min(ai, bj)$ is the optimal embedding of a virtual 
-path starting at any child of $a$, $a'$ and ending at $i$ into node $j$
-that respect the bottleneck constraint, i.e. $b_d(a, a') \leg bn(b, j)$.
-\todo{define bn(i, j) to be the bottleneck between i and j}
-We claim that $\min(ai, bj)$ can be found efficiently 
-\todo{describe how}
 
-\todo{argue about scaling and rounding}
+Let $T_{v_p}(u_v, w_v, C)$ denote the minimum processing required to embed
+all the virtual vertices, excluding $u_v$, on a $u_vw_v$-path into the physical
+vertex $v_p$ with cost constraint $C$.
+$T$ can be computed recursively as follow:
+\begin{align*}
+&T_{v_p}(u_v, w_v, C) = 
+\min_{v_vv_v \in A_v} T_{v_p}(u_v, v_v, C - c(w_v, v_p))
+\\
+&T(u_v, u_v, C) = 0
+\\
+&T(-, -, 0) = \infty
+\end{align*}
+
+Let $O(v_v, v_p)$ denote the optimal embedding of a $s_vv_v$-path into a
+$s_pv_p$-path.
+Let $pi:V_v \to \N$ be any typological ordering of $V_v$. 
+We claim that $O$ can be computed recursively as follow:
+\begin{align*}
+&O(v_v, v_p) = 
+\min_{\substack{
+u_v : pi(u_v) < pi(v_v), 
+\\
+u_pv_p \in A_p
+}}
+O(u_v, u_p)
++
+\argmin_{C : T_{v_p}(u_v, v_v, C) \leq p_c(v_p)}
+\\
+&O(s_v, v_p) = c(s_v, v_p)
+\end{align*}
+
+% For a physical vertex $v_p$ we define 
+% $c_{v_p}(u_v, v_v):A_v \to \R = c(v_v, v_p)$.
+% Given two virtual vertices $s'_v, t'_v$ and a physical vertex $v_p$, 
+% one can verify that the minimum cost of embedding any 
+% 
+% 
+% we would like to find an optimal embedding of an $s'_vt'_v$-path into
+% $v_p$.
+% A solution to this sub-problem can be found as follow:
+% First we build the \emph{cost graph} correspond to $s'_v, t'_v$ and $v_p$, 
+% the cost graph is a graph that lets us (efficiently) compute the cost of em  
+% 
+% For a vertex $v$ let $C(v)$ be the set of its children.
+% Let $O'(s'_v, t'_v, s'_p, t'_p)$ be the optimal embedding of some virtual
+% $C(s'v)t'_v$-path into the physical vertex $t'_p$ such that the bottleneck
+% between $s'_p$ and $t'_p$ is at least $b_d(s'_v, t'_v)$.
+% Let $c_v \in C(s'_v)$ and observe that once $c_v$ is chosen the arc 
+% $(s'_v, c_v)$ determines completely whether a physical path with a feasible
+% bottleneck exists, namely, 
+% a physical path exists if and only if there is a physical $s'_vt'_v$-path containing only
+% arcs with bandwidth at least $b_d(s'_v, c_v)$.
+% On the other hand, the set of $c_vt'_v$-paths
+% determine completely the cost (and processing-wise feasibility) of the embedding.
+% Figure depicts the above observations.
+% 
+% \begin{figure}[ht]
+% \centering
+% \input{fig-dp}
+% \caption[]{
+% \begin{enumerate*}
+% \item Computing $O'(s'_v, t'_v, s'_p, t'_p)$.
+% \item The set of $c_dt'_v$-paths determines completely the cost of the embedding
+% \item 
+% The arc $(s'_v, c_d)$ determines completely the connectivity of $s'_p$ and
+% $t'_p$, i.e. physical arcs with bandwidth less than $b_d(s'_v, c_d)$ can not be
+% used.
+% \end{enumerate*}
+% }
+% \end{figure}
+% 
+% Among all the $c_vt'_v$-paths we want to select the one that minimize the
+% embedding cost under the processing capacity constraints.
+% This can be done... 
+% Calculating $O'(s'_v, t'_v, s'_p, t'_p)$ can be done simply by finding the
+% optimal path among all children of $s'_v$.
+% 
+% Let $O(t'_v, t'_p)$ be the optimal embedding of some virtual $s_vt'_v$-path
+% into some physical $s_pt'_p$-path then $O(t_v, t_p)$ is the global optimal
+% embedding.
+% Also $O(t'_v, s_p)$ can be computed efficiently for every $t'_v$ as described
+% above, and $O(s_v, t'_v)$ is simply the minimum cost of embedding $s_v$ in any
+% physical vertex $s'_p$ such that a physical $s'_pt'_v$-path exists.
+% For an arbitrary vertices $t'_v$, and $t'_p$, $O(t'_v, t'_p)$ can be computed
+% efficiently using dynamic programming with the following recursion formula:
+% $$
+% O(t'_v, t'_p) = 
+% \min_{\substack{
+% s'_v \in P(t'_v)
+% \\
+% s'_p \in P(t'_p)
+% }}
+% O(s'_v, s'_p) + O'(s'_v, t'_v, s'_p, t'_p)
+% $$ 
+% 
+%

### 2017-06-18 src/algorithm.tex
alg

@@
 \min_{\substack{
-u_v : pi(u_v) < pi(v_v), 
+u_v : pi(u_v) \leq pi(v_v), 
 \\
@@
 \end{align*}
+
+\begin{figure}[ht]
+\centering
+\input{fig-dp1}
+\caption[]{
+The optimal embedding of a $s_vw_v$-path into a $s_pw_p$ path can be efficiently 
+computed by breaking the problem into the problem of embedding a $s_vu_v$-path
+into a $s_pv_p$-path (blue, dashed rectangles) 
+and the problem of embedding a $u_vw_v$-path into $w_p$ (red, dotted
+rectangles).
+}
+\end{figure}
 

### 2017-06-18 src/algorithm.tex
alg

--- 2017-06-18 src/algorithm.tex
@@
 \end{align*}
+
+\begin{figure}[ht]
+\centering
+\input{fig-dp1}
+\caption[]{
+The optimal embedding of a $s_vw_v$-path into a $s_pw_p$ path can be efficiently 
+computed by breaking the problem into the problem of embedding a $s_vu_v$-path
+into a $s_pv_p$-path (blue, dashed rectangles) 
+and the problem of embedding a $u_vw_v$-path into $w_p$ (red, dotted
+rectangles) where $b_d(u_v, v_v) \leq b_c(v_p, w_p)$.
+}
+\end{figure}
 

### 2017-06-18 src/algorithm.tex
alg

--- 2017-06-18 src/algorithm.tex
@@
-In this section we present an FPTAS algorithm to the \VPN problem.
-We are given an instance of the \VPN problem 
+In this section we present an FPTAS algorithm to the \VPN{} problem.
+We are given an instance of the \VPN{} problem 
 \begin{align*}
@@
 \end{align*}
-For now assume all values are integral and polynomial bounded in the size of the input.
+For now, assume all values are integral and polynomial bounded in the size of
+the input.
+Under this assumption we show that an optimal embedding can be computed
+efficiently.
+We then argue that, using a standard scaling and rounding technique, we can use
+the same computation to achieve a solution with a cost only
+$1 + \varepsilon$ times greater that of the optimal solution, for any
+$\varepsilon > 0$.
+Also, for convenient and w.l.o.g, assume that $s_v, t_v$ are dummy vertices, 
+i.e. $c(s_v, v_p) = c(t_v, v_p) = 0$ for every $v_p \in V_p$.
 
-Let $T_{v_p}(u_v, w_v, C)$ denote the minimum processing required to embed
+We start by arguing that the minimum processing time required to embed some
+$u_vw_v$-path into a vertex $v_p$ can be computed efficiently.
+Let $P_{v_p}(u_v, w_v, C)$ denote the minimum processing required to embed
 all the virtual vertices, excluding $u_v$, on a $u_vw_v$-path into the physical
 vertex $v_p$ with cost constraint $C$.
-$T$ can be computed recursively as follow:
+$P$ can be computed recursively as follow:
 \begin{align*}
-&T_{v_p}(u_v, w_v, C) = 
-\min_{v_vv_v \in A_v} T_{v_p}(u_v, v_v, C - c(w_v, v_p))
+&P_{v_p}(u_v, w_v, C) = 
+\min_{v_vv_v \in A_v} P_{v_p}(u_v, v_v, C - c(w_v, v_p))
 \\
-&T(u_v, u_v, C) = 0
+&P(u_v, u_v, C) = 0
 \\
-&T(-, -, 0) = \infty
+&P(-, -, <0) = \infty
 \end{align*}
 
-Let $O(v_v, v_p)$ denote the optimal embedding of a $s_vv_v$-path into a
-$s_pv_p$-path.
-Let $pi:V_v \to \N$ be any typological ordering of $V_v$. 
+We now show how to compute the optimal embedding.
+Let $C(w_v, w_p)$ denote the
+optimal embedding of a $s_vw_v$-path into a $s_pw_p$-path.
+Let $\pi:V_v \to \N$ be any typological ordering of $V_v$. 
 We claim that $O$ can be computed recursively as follow:
 \begin{align*}
-&O(v_v, v_p) = 
+&C(w_v, w_p) = 
 \min_{\substack{
-u_v : pi(u_v) < pi(v_v), 
+u_v : pi(u_v) \leq pi(v_v), 
 \\
-u_pv_p \in A_p
+v_pw_p \in A_p
 }}
-O(u_v, u_p)
+C(u_v, u_p)
 +
-\argmin_{C : T_{v_p}(u_v, v_v, C) \leq p_c(v_p)}
+\argmin_{C : P_{w_p}(v_v, w_v, C) \leq p_c(w_p)}
 \\
-&O(s_v, v_p) = c(s_v, v_p)
+&C(s_v, w_p) = c(s_v, w_p)
 \end{align*}
+We note that in order to obey to the bandwidth constraints, 
+one need to temporally remove all edges $u_vv_v$ with bandwidth greater than
+$b_c(v_p, w_p)$ from the virtual graph and only then compute $P_{w_p}(v_v, w_v,
+C)$.
+The above formulation is illustrated in Figure~\ref{fig:dp1}.
 
-% For a physical vertex $v_p$ we define 
-% $c_{v_p}(u_v, v_v):A_v \to \R = c(v_v, v_p)$.
-% Given two virtual vertices $s'_v, t'_v$ and a physical vertex $v_p$, 
-% one can verify that the minimum cost of embedding any 
-% 
-% 
-% we would like to find an optimal embedding of an $s'_vt'_v$-path into
-% $v_p$.
-% A solution to this sub-problem can be found as follow:
-% First we build the \emph{cost graph} correspond to $s'_v, t'_v$ and $v_p$, 
-% the cost graph is a graph that lets us (efficiently) compute the cost of em  
-% 
-% For a vertex $v$ let $C(v)$ be the set of its children.
-% Let $O'(s'_v, t'_v, s'_p, t'_p)$ be the optimal embedding of some virtual
-% $C(s'v)t'_v$-path into the physical vertex $t'_p$ such that the bottleneck
-% between $s'_p$ and $t'_p$ is at least $b_d(s'_v, t'_v)$.
-% Let $c_v \in C(s'_v)$ and observe that once $c_v$ is chosen the arc 
-% $(s'_v, c_v)$ determines completely whether a physical path with a feasible
-% bottleneck exists, namely, 
-% a physical path exists if and only if there is a physical $s'_vt'_v$-path containing only
-% arcs with bandwidth at least $b_d(s'_v, c_v)$.
-% On the other hand, the set of $c_vt'_v$-paths
-% determine completely the cost (and processing-wise feasibility) of the embedding.
-% Figure depicts the above observations.
-% 
-% \begin{figure}[ht]
-% \centering
-% \input{fig-dp}
-% \caption[]{
-% \begin{enumerate*}
-% \item Computing $O'(s'_v, t'_v, s'_p, t'_p)$.
-% \item The set of $c_dt'_v$-paths determines completely the cost of the embedding
-% \item 
-% The arc $(s'_v, c_d)$ determines completely the connectivity of $s'_p$ and
-% $t'_p$, i.e. physical arcs with bandwidth less than $b_d(s'_v, c_d)$ can not be
-% used.
-% \end{enumerate*}
-% }
-% \end{figure}
-% 
-% Among all the $c_vt'_v$-paths we want to select the one that minimize the
-% embedding cost under the processing capacity constraints.
-% This can be done... 
-% Calculating $O'(s'_v, t'_v, s'_p, t'_p)$ can be done simply by finding the
-% optimal path among all children of $s'_v$.
-% 
-% Let $O(t'_v, t'_p)$ be the optimal embedding of some virtual $s_vt'_v$-path
-% into some physical $s_pt'_p$-path then $O(t_v, t_p)$ is the global optimal
-% embedding.
-% Also $O(t'_v, s_p)$ can be computed efficiently for every $t'_v$ as described
-% above, and $O(s_v, t'_v)$ is simply the minimum cost of embedding $s_v$ in any
-% physical vertex $s'_p$ such that a physical $s'_pt'_v$-path exists.
-% For an arbitrary vertices $t'_v$, and $t'_p$, $O(t'_v, t'_p)$ can be computed
-% efficiently using dynamic programming with the following recursion formula:
-% $$
-% O(t'_v, t'_p) = 
-% \min_{\substack{
-% s'_v \in P(t'_v)
-% \\
-% s'_p \in P(t'_p)
-% }}
-% O(s'_v, s'_p) + O'(s'_v, t'_v, s'_p, t'_p)
-% $$ 
-% 
-%
+\begin{figure}[ht]
+\centering
+\input{fig-dp1}
+\caption[]{
+\label{fig:dp1}
+The optimal embedding of a $s_vw_v$-path into a $s_pw_p$ path can be efficiently 
+computed by breaking the problem into the problem of embedding a $s_vu_v$-path
+into a $s_pv_p$-path (blue, dashed rectangles) 
+and the problem of embedding a $u_vw_v$-path into $w_p$ (red, dotted
+rectangles) where $b_d(u_v, v_v) \leq b_c(v_p, w_p)$.
+}
+\end{figure}

### 2017-06-18 src/latency.tex
fix errors
alg

@@
-\todo{Are we going to talk about the problem also with latency constraint ?}
 We now extend the problem by adding a global latency constraint.
@@
 
-Let $O(t'_v, t'_p, C)$ be an embedding of some virtual $s_vt'_v$-path 
-into a physical $s_pt'_p$-path that has cost not more than $C$ and that
-minimizes the latency.
+Let $L(w_v, w_p, C)$ denote the minimum possible latency result from an
+embedding of some virtual $s_vw_v$-path into a physical $s_pw_p$-path 
+that has cost not more than $C$.
+
+We claim that $L(w_v, w_p, C)$ can be computed efficiently as follow:
+\begin{align*}
+&L(w_v, w_p, C) = \min_{\substack{
+u_v : pi(u_v) \leq pi(v_v), 
+\\
+v_pw_p \in A_p
+\\
+\delta : P(u_v, w_v, \delta) \leq p_c(w_p)
+}}
+l(v_p, w_p) + L(u_v, v_p, C - \delta)
+\\
+&L(s_v, w_p, >=0) = 0
+\\
+&L(-, -, <0) = \infty
+\end{align*}
+
+Now, to compute the optimal embedding with the additional latency constraint,
+$L$, one can simply (binary) search for the minimum value of $C$ such that
+$L(t_v, t_p, C) \leq L$.

### 2017-06-18 src/algorithm.tex
alg

@@
 \end{align*}
-We note that in order to obey to the bandwidth constraints, 
+Now, to compute the optimal embedding, one need to compute $C(t_v, t_p)$. 
+We also note that in order to obey to the bandwidth constraints, 
 one need to temporally remove all edges $u_vv_v$ with bandwidth greater than
-$b_c(v_p, w_p)$ from the virtual graph and only then compute $P_{w_p}(v_v, w_v,
-C)$.
+$b_c(v_p, w_p)$ from the virtual graph and only then compute $P_{w_p}(v_v, w_v, C)$.
 The above formulation is illustrated in Figure~\ref{fig:dp1}.

### 2017-06-18 src/algorithm.tex
alg

--- 2017-06-18 src/algorithm.tex
@@
 \begin{align*}
-D_v = (V_v, A_v)		\\
-D_p = (V_p, A_p)		\\
-(s_v, t_v, s_p, t_p)	\\
+D_v = (\beta , A_v)		\\
+D_p = (v, A_p)		\\
+(\sigma , \tau , s, t)	\\
 (p_d, b_d, p_c, b_c, c)
@@
 $\varepsilon > 0$.
-Also, for convenient and w.l.o.g, assume that $s_v, t_v$ are dummy vertices, 
-i.e. $c(s_v, v_p) = c(t_v, v_p) = 0$ for every $v_p \in V_p$.
+Also, for convenient and w.l.o.g, assume that $\sigma , \tau $ are dummy vertices, 
+i.e. $c(\sigma , v) = c(\tau , v) = 0$ for every $v \in v$.
 
 We start by arguing that the minimum processing time required to embed some
-$u_vw_v$-path into a vertex $v_p$ can be computed efficiently.
-Let $P_{v_p}(u_v, w_v, C)$ denote the minimum processing required to embed
-all the virtual vertices, excluding $u_v$, on a $u_vw_v$-path into the physical
-vertex $v_p$ with cost constraint $C$.
+$\alpha \gamma $-path into a vertex $v$ can be computed efficiently.
+Let $P_{v}(\alpha , \gamma , C)$ denote the minimum processing required to embed
+all the virtual vertices, excluding $\alpha $, on a $\alpha \gamma $-path into the physical
+vertex $v$ with cost constraint $C$.
 $P$ can be computed recursively as follow:
 \begin{align*}
-&P_{v_p}(u_v, w_v, C) = 
-\min_{v_vv_v \in A_v} P_{v_p}(u_v, v_v, C - c(w_v, v_p))
+&P_{v}(\alpha , \gamma , C) = 
+\min_{\alpha \beta  \in A_v} P_{v}(\alpha , \beta , C - c(\gamma , v))
 \\
-&P(u_v, u_v, C) = 0
+&P(\alpha , \alpha , C) = 0
 \\
@@
 We now show how to compute the optimal embedding.
-Let $C(w_v, w_p)$ denote the
-optimal embedding of a $s_vw_v$-path into a $s_pw_p$-path.
-Let $\pi:V_v \to \N$ be any typological ordering of $V_v$. 
+Let $C(\gamma , w_p)$ denote the
+optimal embedding of a $\sigma \gamma $-path into a $sw_p$-path.
+Let $\pi:\beta  \to \N$ be any typological ordering of $\beta $. 
 We claim that $O$ can be computed recursively as follow:
 \begin{align*}
-&C(w_v, w_p) = 
+&C(\gamma , w_p) = 
 \min_{\substack{
-u_v : pi(u_v) \leq pi(v_v), 
+\alpha  : pi(\alpha ) \leq pi(\beta ), 
 \\
-v_pw_p \in A_p
+vw_p \in A_p
 }}
-C(u_v, u_p)
+C(\alpha , u_p)
 +
-\argmin_{C : P_{w_p}(v_v, w_v, C) \leq p_c(w_p)}
+\argmin_{C : P_{w_p}(\beta , \gamma , C) \leq p_c(w_p)}
 \\
-&C(s_v, w_p) = c(s_v, w_p)
+&C(\sigma , w_p) = c(\sigma , w_p)
 \end{align*}
-We note that in order to obey to the bandwidth constraints, 
-one need to temporally remove all edges $u_vv_v$ with bandwidth greater than
-$b_c(v_p, w_p)$ from the virtual graph and only then compute $P_{w_p}(v_v, w_v,
-C)$.
+Now, to compute the optimal embedding, one need to compute $C(\tau , t)$. 
+We also note that in order to obey to the bandwidth constraints, 
+one need to temporally remove all edges $\alpha \beta $ with bandwidth greater than
+$b_c(v, w_p)$ from the virtual graph and only then compute $P_{w_p}(\beta , \gamma , C)$.
 The above formulation is illustrated in Figure~\ref{fig:dp1}.
@@
 \label{fig:dp1}
-The optimal embedding of a $s_vw_v$-path into a $s_pw_p$ path can be efficiently 
-computed by breaking the problem into the problem of embedding a $s_vu_v$-path
-into a $s_pv_p$-path (blue, dashed rectangles) 
-and the problem of embedding a $u_vw_v$-path into $w_p$ (red, dotted
-rectangles) where $b_d(u_v, v_v) \leq b_c(v_p, w_p)$.
+The optimal embedding of a $\sigma \gamma $-path into a $sw_p$ path can be efficiently 
+computed by breaking the problem into the problem of embedding a $\sigma \alpha $-path
+into a $sv$-path (blue, dashed rectangles) 
+and the problem of embedding a $\alpha \gamma $-path into $w_p$ (red, dotted
+rectangles) where $b_d(\alpha , \beta ) \leq b_c(v, w_p)$.
 }

### 2017-06-18 src/algorithm.tex
alg

@@
 We now show how to compute the optimal embedding.
-Let $C(\gamma , w_p)$ denote the
-optimal embedding of a $\sigma \gamma $-path into a $sw_p$-path.
+Let $C(\gamma , w)$ denote the
+optimal embedding of a $\sigma \gamma $-path into a $sw$-path.
 Let $\pi:\beta  \to \N$ be any typological ordering of $\beta $. 
@@
 \begin{align*}
-&C(\gamma , w_p) = 
+&C(\gamma , w) = 
 \min_{\substack{
@@
 \\
-vw_p \in A_p
+vw \in A_p
 }}
-C(\alpha , u_p)
+C(\alpha , u)
 +
-\argmin_{C : P_{w_p}(\beta , \gamma , C) \leq p_c(w_p)}
+\argmin_{C : P_{w}(\beta , \gamma , C) \leq p_c(w)}
 \\
-&C(\sigma , w_p) = c(\sigma , w_p)
+&C(\sigma , w) = c(\sigma , w)
 \end{align*}
@@
 one need to temporally remove all edges $\alpha \beta $ with bandwidth greater than
-$b_c(v, w_p)$ from the virtual graph and only then compute $P_{w_p}(\beta , \gamma , C)$.
+$b_c(v, w)$ from the virtual graph and only then compute $P_{w}(\beta , \gamma , C)$.
 The above formulation is illustrated in Figure~\ref{fig:dp1}.
@@
 \label{fig:dp1}
-The optimal embedding of a $\sigma \gamma $-path into a $sw_p$ path can be efficiently 
+The optimal embedding of a $\sigma \gamma $-path into a $sw$ path can be efficiently 
 computed by breaking the problem into the problem of embedding a $\sigma \alpha $-path
 into a $sv$-path (blue, dashed rectangles) 
-and the problem of embedding a $\alpha \gamma $-path into $w_p$ (red, dotted
-rectangles) where $b_d(\alpha , \beta ) \leq b_c(v, w_p)$.
+and the problem of embedding a $\alpha \gamma $-path into $w$ (red, dotted
+rectangles) where $b_d(\alpha , \beta ) \leq b_c(v, w)$.
 }

### 2017-06-21 src/algorithm.tex
fig
fix

@@
 \centering
-\input{fig-dp1}
+\input{fig-dp2}
 \caption[]{
 \label{fig:dp1}
-The optimal embedding of a $\sigma \gamma $-path into a $sw$ path can be efficiently 
-computed by breaking the problem into the problem of embedding a $\sigma \alpha $-path
-into a $sv$-path (blue, dashed rectangles) 
-and the problem of embedding a $\alpha \gamma $-path into $w$ (red, dotted
-rectangles) where $b_d(\alpha , \beta ) \leq b_c(v, w)$.
+The optimal embedding of a $\sigma \gamma $-path into a $sv$ path can be
+efficiently computed by breaking the problem into the problem of embedding 
+a $\sigma \alpha $-path into a $su$-path (blue, dashed clouds) 
+and the problem of embedding a $\beta \gamma $-path into $v$ (orange, dotted) 
+where $b_d(\alpha , \beta) \leq b_c(u, v)$.
 }

### 2017-06-21 src/algorithm.tex
fix

@@
-In this section we present an FPTAS algorithm to the \VPN{} problem.
+In this section, 
+assuming costs are integral and polynomial bounded in the input length,
+we present an efficient algorithm to the \VPN{} problem.
+We then argue that, using a standard scaling and rounding technique, we can use
+the same computation to achieve a solution with a cost only
+$1 + \varepsilon$ times greater that of the optimal solution, for any
+$\varepsilon > 0$, i.e. an FPTAS also for an arbitrary cost function.
+We also extend our algorithm when every physical arc carry some latency on it
+and a global latency constraint is given.
+
 We are given an instance of the \VPN{} problem 
@@
 \end{align*}
-For now, assume all values are integral and polynomial bounded in the size of
-the input.
-Under this assumption we show that an optimal embedding can be computed
-efficiently.
-We then argue that, using a standard scaling and rounding technique, we can use
-the same computation to achieve a solution with a cost only
-$1 + \varepsilon$ times greater that of the optimal solution, for any
-$\varepsilon > 0$.
 Also, for convenient and w.l.o.g, assume that $\sigma , \tau $ are dummy vertices, 
-i.e. $c(\sigma , v) = c(\tau , v) = 0$ for every $v \in v$.
+i.e. $c(\sigma , v) = c(\tau , v) = 0$ for every $v \in V_p$ and that
+$b_d(\sigma\alpha) = b_d(\alpha\tau) = 0$ for every $\alpha \in V_v$.
 
 We start by arguing that the minimum processing time required to embed some
-$\alpha \gamma $-path into a vertex $v$ can be computed efficiently.
+$\alpha \gamma $-path into a vertex $v$ given a cost constraint can be computed
+efficiently.
 Let $P_{v}(\alpha , \gamma , C)$ denote the minimum processing required to embed
 all the virtual vertices, excluding $\alpha $, on a $\alpha \gamma $-path into the physical
-vertex $v$ with cost constraint $C$.
+vertex $v$ with a cost constraint $C$.
 $P$ can be computed recursively as follow:
@@
 Let $\pi:\beta  \to \N$ be any typological ordering of $\beta $. 
-We claim that $O$ can be computed recursively as follow:
+We claim that $C$ can be computed recursively as follow:
 \begin{align*}
@@
 \min_{\substack{
-\alpha  : pi(\alpha ) \leq pi(\beta ), 
+\alpha  : \pi(\alpha ) \leq \pi(\beta ), 
 \\
@@
 
-\begin{figure}[ht]
+\begin{figure}[h]
 \centering
@@
 where $b_d(\alpha , \beta) \leq b_c(u, v)$.
+Virtual arcs with high bandwidth demand (dashed arc) need to be removed before
+the computation of the optimal path embedding.
 }

### 2017-06-21 src/chain.tex
general

%\nonstopmode
%\documentclass[11pt]{article}
\documentclass[runningheads]{llncs}

\usepackage{amsmath,amssymb,mathtools}
%\usepackage{amsthm}
%\usepackage{fullpage}
\usepackage{xspace}
\usepackage{color,soul}
\usepackage{paralist}

% \usepackage[linesnumbered, ruled]{algorithm2e}

\usepackage[final]{microtype}
\usepackage[final]{hyperref}
\usepackage{subcaption}

% DEBUG
%\usepackage{lipsum}
\usepackage{todonotes}
%\usepackage{lineno}
%\linenumbers

% EXTRA
%\usepackage{authblk}

\input{tikz}

\sloppy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% handy commands

\newcommand{\eqdf}{\stackrel{\scriptscriptstyle \triangle}{=}}
\newcommand{\argmin}{\ensuremath{\mbox{argmin}}}
\newcommand{\argmax}{\ensuremath{\mbox{argmax}}}
\newcommand{\set}[1]{\left\{ #1 \right\}}
\newcommand{\paren}[1]{\left( #1 \right)}
\newcommand{\bit}{\set{0,1}}
\newcommand{\inv}[1]{\frac{1}{#1}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\ceil}[1]{\left\lceil {#1} \right\rceil}
\newcommand{\floor}[1]{\left\lfloor {#1} \right\rfloor}
\newcommand{\half}{\frac{1}{2}}
\newcommand{\threehalves}{\frac{3}{2}}

\newcommand{\naturals}{\mathbb{N}}
\newcommand{\rationals}{\mathbb{Q}}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\integers}{\mathbb{Z}}

\newcommand{\eps}{\varepsilon}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\scp}{\textsc{SCP}\xspace}
\newcommand{\scplong}{\textsc{Service Chain Placement}\xspace}

\newcommand{\calE}{\mathcal{E}}
\newcommand{\calG}{\mathcal{G}}
\newcommand{\calV}{\mathcal{V}}

\newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{\bf Service Chain Placement in SDNs%
\thanks{Research supported in part by Network Programming (Neptune)
  Consortium, Israel.}
}

\titlerunning{Service Chain Placement in SDNs}

%\author[1]{Gilad Kutiel%
%\thanks{E-mail: \texttt{gkutiel@cs.technion.ac.il}}}

%\author[2]{Dror Rawitz%
%\thanks{Partially supported by the Israel Science Foundation
%  (grant no.~497/14).  E-mail: \texttt{dror.rawitz@biu.ac.il}}}

%\affil[1]{Department of Computer Science, Technion, Haifa, Israel}
%\affil[2]{Faculty of Engineering, Bar Ilan University, Ramt-Gan, Israel}

\author{%
Gilad Kutiel
\and
Dror Rawitz%
\thanks{Partially supported by the Israel Science Foundation
  (grant no.~497/14).  }
}

\institute{%
Department of Computer Science, Technion, Haifa 32000, Israel. \\
\email{gkutiel@cs.technion.ac.il}
\and
Faculty of Engineering, Bar Ilan University, Ramt-Gan 52900, Israel.\\
\email{dror.rawitz@biu.ac.il}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle

\begin{abstract}
We study the allocation problem of a \emph{service chain} in a
software-defined network that supports network function
virtualization.
%
Given a network that contains servers with limited processing power
and of links with limited bandwidth, a service chain is a sequence of
virtual network functions (VNFs) that service a certain flow request
in the network.
%
The allocation of a service chain consists of routing and VNF
placement.  That is, each VNF from the seqeunce is placed in a server
along a path, and it is feasible if each server can handle the VNFs
that are assigned to it, and if each link on the path can carry the
flow that is assigned to it.
%
A request for service is composed of a source and a destination in the
network, an upper bound on the total latency, and a specification of
all service chains that are considered valid for this request.
%
Each pair of server and VNF are associated with a cost for placing the
network function in the server, and given a request, the goal is to
find a valid service chain of minimum total cost or to identify that
a valid service chain does not exist.

We show that even the feasibility problem is NP-hard in general
di-graphs.  Hence we first focus on directed acyclic graphs (DAGs).
We show that the problem is still NP-hard in DAGs and present an
FPTAS.
%
Based on out PTAS, we also provide a randomized algorithm for
instances in which the service chain passes through a bounded number
of servers whose degree is larger than two.

?????

Fault tolerant placement: two service chains?

FPT algorithm where the number of servers whose degree is larger than
two is a parameter?
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

Computer communication networks are in constant need of expansion to
cope with the ever growing traffic.  As networks grow, management and
maintenance become more and more complicated.
%
Current developments aim to improve the utilization of network
resources include the detachment of network applications from network
infrastructure and the transition from network planning to network
programming.

One aspect of network programming is to manage resources from a
central point of view, namely to make decisions based on availability,
network status, required quality of service, and the identity of the
client.  Hence, a central issue is a central agent that is able to
received reports from network components and client requests, and as a
result can alter the allocation of resources in the networks.  This
approach is called Software Defined Networking (SDN), where there is a
separation between routing and management (control plane) and the
underlying routers and switches that forward traffic (data plane) (see
Kreutz et al.~\cite{KRVRAU15}).

A complimentary approach is Network Function Virtualization
(NFV)~\cite{NFV12}.  Instead of relying on special purpose machines,
network applications become virtual network functions (VNF) that are
executed on generic machines and can be placed in various locations in
the network.  Virtualization increases the flexibility of resource
allocation and thus the utilization of the network resources.
%
Internet Service Providers (ISPs) that provide services to clients
benefit from NFV, since it helps to better utilize their physical
network.  In addition, when network services are virtualized, an ISP
may support \emph{service chaining}~\cite{ServiceChaining15}, namely a
compound service that consists of a sequence of VNFs.  Furthermore,
one may offer a compound service a service that may be obtained using
one of several sequences of VNFs.

In this paper we study the allocation problem of a compund request for
a service chain in a software-defined network that supports NFV.
Given a (physical) network that contains servers with limited
processing power and of links with limited bandwidth, a service chain
is a sequence of virtual network functions (VNFs) that service a
certain flow request in the network.
%
The allocation of a service chain consists of routing and VNF
placement.  That is, each VNF from the seqeunce is placed in a server
along a path, and it is feasible if each server can handle the VNFs
that are assigned to it, and if each link on the path can carry the
flow that is assigned to it.
%
A request for service is composed of a source and a destination in the
network, an upper bound on the total latency, and a specification of
all service chains that are considered valid for this request.
%
Each pair of server and VNF are associated with a cost for placing the
network function in the server.  This cost measures compatibility of a
VNF to a server (infinite costs means ``incompatible'').  Given a
request, the goal is to find a valid service chain of minimum total
cost or to identify that a valid service chain does not exist.

\dror{Explain one shot approach}

\paragraph*{\bf Related work.}
%

Cohen et al.~\cite{CLNR15} considered VNF placement.  In their model
the input is an undirected graph with a metric distance function on
the edges.  clients are located in various nodes, and each client is
interested in a subset of VNFs.  For each node $v$ and VNF $\alpha$,
there is a setup cost associated with placing a copy of $\alpha$ at
$v$ (multiple copies are allowed), and there is a load that is induced
on $v$ for placing a copy of $\alpha$.  Furthermore, each node has a
limited capacity.  Also, each copy of a VNF can handle a limited
amount of clients A solution is the assignment of each client to a
subset of nodes, each corresponding to one of its required VNFs.  The
cost of a solution is the total setup costs plus the sum of distances
between the clients and the node from which they get service.
%
Cohen et al.~\cite{CLNR15} gave bi-criteria approximation algorithms
for various versions of the problem, namely algorithms that compute
constant factor approximations that violate the load constraints by a
constant factor.
%
It is important to note that in this problem does not consider
routing, and also it assumes unordered VNF subsets.

Even, Medina, and Patt-Shamir~\cite{EMP16} studied online path
computation and VNF placement.  They considered service chain requests
that arrive in an online manner.  Each request is a a flow with a
high-level specification of routing and VNF requirements.  Each VNF
can be performed by a specified subset of servers in the system.  Upon
arrival of a request, the algorithm either rejects the request or
accepts it and with a specific routing and VNF assignment, under given
server capacity constraints.  Each request has a benefit that is
gained if it is accepted, and the goal is to maximize the total
benefit.
%
Even, Medina, and Patt-Shamir~\cite{EMP16} proposed an algorithm that
copes with requests with unknown duration without preemption by using
a third response, which is refer to as “stand by”, whose competitive
ratio is $O(\log (knb_{\max})$, where $n$ is the number of nodes,
$b_{\max}$ is an upper bound on a request benefit per time unit, and
$k$ is the maximum number of VNFs of any service chain.  This
performance guarantee holds for the case where the processing of any
processing request in any possible service chain is never more than
$O(1/(k \log (nk)))$ fraction of the capacity of any network
component.

Even, Rost, and Schmid~\cite{ERS16}

\dror{finish}

\paragraph*{\bf Our results.}
%
We show that even the feasibility problem is NP-hard in general
di-graphs.  Hence we first focus on directed acyclic graphs (DAGs).
We show that the problem is still NP-hard in DAGs and present an
FPTAS.
%
Based on out PTAS, we also provide a randomized algorithm for
instances in which the service chain passes through a bounded number
of servers whose degree is larger than two.

?????

\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Preliminaries}

\paragraph*{\bf Model.}
%
The \scplong (\scp) input is composed of three components, a physical
network, a virtual specification, and placement costs:
\begin{description}
\item[Physical network:]
%
  The physical network is a digraph $G = (V,E)$.  Each node $v \in V$
  has a non-negative processing capacity $p(v)$, and each directed
  edge $e \in A$ has a non-negative bandwidth cap $b(e)$.

\item[Virtual specification:]
%
  The description of a request for a service chain consists of a
  physical source $s \in V$, a physical destination $t \in V$, and a
  directed acyclic graph (DAG) $\calG = (\calV,\calE)$.
%
  Without loss of generality, we assume that $p(s) = p(t) = 0$.  
%
  The DAG $\calG$ has a source node $\sigma \in \calV$ and a
  destination $\tau \in \calV$ Each node $\alpha \in \calV$ represent
  a VNF that has a processing demand $p(\alpha)$.  Without loss of
  generality, we assume that $p(\sigma) = p(\tau) = 0$.  Each edge
  $\eps \in \calE$ has a bandwidth demand $b(\eps)$.

\item[Placement costs:]
%
  There is a non-negative cost $c(\alpha,v)$ for placing the VNF
  $\alpha$ in $v$.  We assume that $c(\sigma,s) = 0$ and $c(\sigma,v)
  = \infty$, for every $v \neq s$.  Similarly, we assume that
  $c(\tau,t) = 0$ and $c(\tau,v) = \infty$, for every $v \neq t$.
\end{description}

A solution consists of the following:
\begin{description}
\item[Virtual path:] A path from $\sigma$ to $\tau$ in $\calG$, namely
  a sequence of vertices $\alpha_0,\ldots,\alpha_\ell$, where
  $\alpha_0 = \sigma$, $\alpha_\ell = \tau$, and
  $(\alpha_j,\alpha_{j+1}) \in \calE$, for every $j \in
  \set{0,\ldots,\ell-1}$.

\item[Physical path:] A simple path from $s$ to $t$ in $G$, namely a
  sequence of node $v_0,\ldots,v_k$, where $v_0 = s$, $v_k = t$, and
  $(v_i,v_{i+1}) \in E$, for every $i \in \set{0,\ldots,k-1}$.

\item[Placement:] A function $f$ that maps the virtual path to the
  physical path.  Formally, a placement is a function $f:
  \set{\alpha_0,\ldots,\alpha_\ell} \to \set{v_0,\ldots,v_k}$
  such that
\begin{enumerate}
\item If $f(\alpha_j) = v_i$ and $f(\alpha_{j+1}) = v_{i'}$, then $i
  \leq i'$.
\item $b(\alpha_j,\alpha_{j+1}) \leq b(v_i,v_{i+1})$, for every
  $(v_i,v_{i+1}) \in \bar{f}(\alpha_j,\alpha_{j+1})$, where
  $\bar{f}(\alpha_j,\alpha_{j+1})$ to be the set of physical edges
  that correspond to it, i.e.,
\[
\bar{f}(\alpha_j,\alpha_{j+1}) \eqdf \set{(v_i,v_{i+1}) : i' \leq i < i''}
~,
\]
  where $f(\alpha_j) = v_{i'}$ and $f(\alpha_{j+1}) = v_{i''}$.

\item $\sum_{\alpha \in f^{-1}(v)} p(\alpha) \leq p(v)$, where
  $f^{-1}(v) \eqdf \set{\alpha : f(\alpha) = v}$.

\end{enumerate}
\end{description}

An example of an \scp instance and a solution is given in
Figure~\ref{fig:solution}.

\begin{figure}
\centering
\scalebox{1}{
\input{fig-embedding}
}
\caption{???}
\label{fig:solution}
\end{figure}

The cost of a placement $f$ is:
\[
\sum_j c(\alpha_j,f(\alpha_j))
~.
\]
In \scp the goal is to find a feasible placement of a virtual path
into the physical DAG that minimizes the cost.

%%%%%

We also consider an extended version of \scp in which each physical
link causes a delay and there is an upper bound $T$ on the total
delay.  More formally, each pair of a virtual edge $\eps$ and physical
edge $e$ is associated with a latency $t(\eps,e)$.
%
Given a placement $f: \set{\alpha_0,\ldots,\alpha_\ell} \to
\set{v_0,\ldots,v_k}$, the total latency of the solution is given by
\[
T(f) = \sum_j \sum_{e \in \bar{f}(\eps)} t(\eps,e)
~.
\]
In this case there is an additional constraint that $T(f) \leq T$.

%%%%%

\paragraph*{\bf Definitions and notation.}
%
Define $n_p \eqdf \abs{V}$ and $m_p \eqdf \abs{E}$.  Similarly, define
$n_v \eqdf \abs{\calV}$ and $m_v \eqdf \abs{\calE}$.

Given a virtual DAG $\calG$, we assume the existence of a topological
sorting of the vertices and write $\alpha \prec_v \beta$ if $\alpha$
precedes $\beta$ in this ordering.  If the physical network is a DAG,
then we make a similar assumption and write $v \prec_p u$ if $v$
precedes $u$ in this ordering.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Hardness}

In this section we present two hardness results.  First, we show that
even the feasibility question of \scp is NP-hard, and therefore no
approximation algorithm exists for \scp.  In addition, we show that
\scp is NP-hard even if $\abs{V \setminus \set{s,t}} = 1$.  We also
show that \scp is NP-hard even if both the physical network and the
virtual DAG are simple paths.

We show that finding a feasible solution is NP-hard.

\begin{theorem}
Feasibility of \scp is NP-hard
\end{theorem}
\begin{proof}
We use a reduction from \textsc{Hamiltonian Path} that is known to be
NP-hard~\cite{GarJoh79}.
%
Given an instance $H$ of \textsc{Hamiltonian Path} we construct an
instance of \scp.  For the physical network we have that $G$, where
$V(G) = V(H) \cup \set{s,t}$, and $E(G) = E(H) \cup \set{(s,v),(v,t) :
  v \in V(H)}$.  In addition, $p(v) = 1$, for every $v$, and $b(e) =
1$, for every $e$.  The virtual DAG $\calG$ is a path containing $n+2$
virtual functions, $\sigma = \alpha_0, \alpha_1, \ldots, \alpha_n,
\alpha_{n+1} = \tau$, where $p(\alpha_i) = 1$, for every $i \in
\set{1,\ldots,n}$.  Also, $b(\alpha_i,\alpha_{i+1}) = 1$, for every
$i$.

The construction can clearly be computed in polynomial time.
%
An Hamiltonian Path in $G$, induces a \scp solution that follows the
path, i.e., $\alpha_i$ is placed in the $i$th vertex along the path.
%
One the other hand, since all demands and capacities are $1$, no two
VNFs can share a physical node.  Hence a \scp solution induces an
Hamiltonian path.
%
\qed
\end{proof}

Next, we show that \scp is NP-hard even if the physical network is a
DAG.

\begin{theorem}
\scp is NP-hard, even if $\abs{V \setminus \set{s,t}} = 1$.
\end{theorem}
\begin{proof}
The prove the theorem using a reduction from \textsc{Partition}.
Given a \textsc{Partition} instance $\set{a_1, \ldots, a_n}$ we
construct an \scp instance as follows.
%
The physical network $G$ contains three nodes: $s$, $v$, and $t$, and
there are two edges $(s,v)$ and $(v,t)$.  The capacity of $v$ is $p(v)
= \half \sum_i a_i$.  Edge capacities are zero.
%
The virtual DAG is composed of $2n+2$ vertices, namely
\[
\calV
= \set{\sigma,\tau}
  \cup \set{\alpha_1, \ldots, \alpha_n}
  \cup \set{\beta_1, \ldots, \beta_n}
~.
\]
Also,
\[
\calE
= \bigcup_i \set{ \set{\alpha_i,\beta_i} \times \set{\alpha_{i+1},\beta_{i+1}} } 
  \cup
  \set{ (\sigma,\alpha_1), (\sigma,\beta_1), (\alpha_n,t), (\beta_n,t) }
~.
\]
The DAG is shown in Figure~\ref{fig:dag}.
%
The demands are $p(\alpha_i) = a_i$ and $p(\beta_i) = 0$, for every
$i$.  Also, $b(\eps) = 0$, for every $\eps \in \calE$.  The costs are:
$c(\alpha_i,v) = 0$ and $c(\beta_i,v) = a_i$, for every $i$.

The \scp instance can be computed in polynomial time.
%
Also, it is not hard to verify that $a \in \textsc{Partition}$ if and
only if there exists a solution whose cost is $\half \sum_i a_i$.
%
\qed
\end{proof}

\begin{figure}
\centering
\input{fig-reduction}
\caption{???}
\label{fig:dag}
\end{figure}

\dror{Figure 2: source and destination should be fixed}

\begin{theorem}
\scp is NP-hard, even if both the physical network and the virtual DAG
are paths.
\end{theorem}
\begin{proof}

\dror{reduction from partition using latency}

%
\qed
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Algorithm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Latency}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{abbrv}
\bibliography{chain}

\end{document}

### 2017-06-21 src/graphs.tex
general

In this section we consider the problem on undirected (physical) graphs.
Once again we seek to embed a virtual $\sigma\tau$-path 
into a simple physical $st$-path.
Note, that we still assume that the virtual graph is a DAG.

We extend our algorithm to work also for this case as well.
Recall that the problem on general graphs cannot be approximate at all,
thus we assume in this section that the there exists an optimal embedding using
at most $k$ \emph{heavy} vertices, thus are vertices with degree greater than two.
The modified algorithm runs in time polynomial in the input length and
exponential in $k$ and achieves the same guarantees as before with high
probability.

The modified algorithm acts as follow:
let $K = {v_1, \ldots, v_k}$ be the set of heavy vertices, and let 
$\pi:[k] \to [k]$ be a random permutation.
Let $v_1, v_l \in K$ be two heavy vertices such that $\pi(v_1) < \pi(v_l)$ and
let $w_1, \ldots, w_l$ any light path between them, i.e. a path that does not
contains any other heavy vertex.
We orient the edges from $u$ to $v$, i.e. $(w_i, w_{i+1})$ for every 
$1 \leq i \leq l - 1$.
One can be verify that this can be done efficiently and that after this process
each edge become an arc and that $G$ is a DAG.

Completing the orientation, we use our previous algorithm to find an optimal
embedding.
We repeat this process, each time with a new independent random permutation, and
keep the best embedding so far.

We claim that with high probability, after $O(k!)$ iterations, the above
algorithm finds the optimal embedding, formally:

\begin{theorem}
With probability at least $1 - e^{-x}$ the algorithm finds the optimal embedding
after $xk!$ iterations.
\end{theorem}

\begin{proof}
Consider an optimal embedding and the order it induces on the heavy vertices,
If the random permutation order the heavy vertices in that order we are
guaranteed to find the optimal embedding.
This happens with probability $1/k!$ and the probability to miss the optimal
embedding after $xk!$ iterations is $1 - (1 - 1/k!)^{xk!} \leq 1 - e^{-x}$.
\end{proof}

### 2017-06-23 src/main.tex
dror
fix errors
alg
foo

@@
-\nonstopmode
-\documentclass[draft]{article}
+%\nonstopmode
+%\documentclass[11pt]{article}
+\documentclass[runningheads]{llncs}
 
-\input{libs}
-\input{def}
+\usepackage{amsmath,amssymb,mathtools}
+%\usepackage{amsthm}
+%\usepackage{fullpage}
+\usepackage{xspace}
+\usepackage{color,soul}
+\usepackage{paralist}
+
+% \usepackage[linesnumbered, ruled]{algorithm2e}
+
+\usepackage[final]{microtype}
+\usepackage[final]{hyperref}
+\usepackage{subcaption}
+
+% DEBUG
+%\usepackage{lipsum}
+\usepackage{todonotes}
+%\usepackage{lineno}
+%\linenumbers
+
+% EXTRA
+%\usepackage{authblk}
+
 \input{tikz}
 
-\input{title}
-\input{authors}
+\def\VPN{Service Chain Placement in SDN}
+\def\R{\mathbb{R}}
+\def\N{\mathbb{N}}
+
+\sloppy
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% handy commands
+
+\newcommand{\eqdf}{\stackrel{\scriptscriptstyle \triangle}{=}}
+\newcommand{\argmin}{\ensuremath{\mbox{argmin}}}
+\newcommand{\argmax}{\ensuremath{\mbox{argmax}}}
+\newcommand{\set}[1]{\left\{ #1 \right\}}
+\newcommand{\paren}[1]{\left( #1 \right)}
+\newcommand{\bit}{\set{0,1}}
+\newcommand{\inv}[1]{\frac{1}{#1}}
+\newcommand{\abs}[1]{\left| #1 \right|}
+\newcommand{\ceil}[1]{\left\lceil {#1} \right\rceil}
+\newcommand{\floor}[1]{\left\lfloor {#1} \right\rfloor}
+\newcommand{\half}{\frac{1}{2}}
+\newcommand{\threehalves}{\frac{3}{2}}
+
+\newcommand{\naturals}{\mathbb{N}}
+\newcommand{\rationals}{\mathbb{Q}}
+\newcommand{\reals}{\mathbb{R}}
+\newcommand{\integers}{\mathbb{Z}}
+
+\newcommand{\eps}{\varepsilon}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newcommand{\scp}{\textsc{SCP}\xspace}
+\newcommand{\scplong}{\textsc{Service Chain Placement}\xspace}
+
+\newcommand{\calE}{\mathcal{E}}
+\newcommand{\calG}{\mathcal{G}}
+\newcommand{\calV}{\mathcal{V}}
+
+\newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title{\bf Service Chain Placement in SDNs%
+\thanks{Research supported in part by Network Programming (Neptune)
+  Consortium, Israel.}
+}
+
+\titlerunning{Service Chain Placement in SDNs}
+
+%\author[1]{Gilad Kutiel%
+%\thanks{E-mail: \texttt{gkutiel@cs.technion.ac.il}}}
+
+%\author[2]{Dror Rawitz%
+%\thanks{Partially supported by the Israel Science Foundation
+%  (grant no.~497/14).  E-mail: \texttt{dror.rawitz@biu.ac.il}}}
+
+%\affil[1]{Department of Computer Science, Technion, Haifa, Israel}
+%\affil[2]{Faculty of Engineering, Bar Ilan University, Ramt-Gan, Israel}
+
+\author{%
+Gilad Kutiel
+\and
+Dror Rawitz%
+\thanks{Partially supported by the Israel Science Foundation
+  (grant no.~497/14).  }
+}
+
+\institute{%
+Department of Computer Science, Technion, Haifa 32000, Israel. \\
+\email{gkutiel@cs.technion.ac.il}
+\and
+Faculty of Engineering, Bar Ilan University, Ramt-Gan 52900, Israel.\\
+\email{dror.rawitz@biu.ac.il}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\input{outline}
+\begin{abstract}
+We study the allocation problem of a \emph{service chain} in a
+software-defined network that supports network function
+virtualization.
+%
+Given a network that contains servers with limited processing power
+and of links with limited bandwidth, a service chain is a sequence of
+virtual network functions (VNFs) that service a certain flow request
+in the network.
+%
+The allocation of a service chain consists of routing and VNF
+placement.  That is, each VNF from the seqeunce is placed in a server
+along a path, and it is feasible if each server can handle the VNFs
+that are assigned to it, and if each link on the path can carry the
+flow that is assigned to it.
+%
+A request for service is composed of a source and a destination in the
+network, an upper bound on the total latency, and a specification of
+all service chains that are considered valid for this request.
+%
+Each pair of server and VNF are associated with a cost for placing the
+network function in the server, and given a request, the goal is to
+find a valid service chain of minimum total cost or to identify that
+a valid service chain does not exist.
 
-\bibliographystyle{plain}
-\bibliography{main}
+We show that even the feasibility problem is NP-hard in general
+di-graphs.  Hence we first focus on directed acyclic graphs (DAGs).
+We show that the problem is still NP-hard in DAGs and present an
+FPTAS.
+%
+Based on out PTAS, we also provide a randomized algorithm for
+instances in which the service chain passes through a bounded number
+of servers whose degree is larger than two.
+
+?????
+
+Fault tolerant placement: two service chains?
+
+FPT algorithm where the number of servers whose degree is larger than
+two is a parameter?
+\end{abstract}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Introduction}
+
+Computer communication networks are in constant need of expansion to
+cope with the ever growing traffic.  As networks grow, management and
+maintenance become more and more complicated.
+%
+Current developments aim to improve the utilization of network
+resources include the detachment of network applications from network
+infrastructure and the transition from network planning to network
+programming.
+
+One aspect of network programming is to manage resources from a
+central point of view, namely to make decisions based on availability,
+network status, required quality of service, and the identity of the
+client.  Hence, a central issue is a central agent that is able to
+received reports from network components and client requests, and as a
+result can alter the allocation of resources in the networks.  This
+approach is called Software Defined Networking (SDN), where there is a
+separation between routing and management (control plane) and the
+underlying routers and switches that forward traffic (data plane) (see
+Kreutz et al.~\cite{KRVRAU15}).
+
+A complimentary approach is Network Function Virtualization
+(NFV)~\cite{NFV12}.  Instead of relying on special purpose machines,
+network applications become virtual network functions (VNF) that are
+executed on generic machines and can be placed in various locations in
+the network.  Virtualization increases the flexibility of resource
+allocation and thus the utilization of the network resources.
+%
+Internet Service Providers (ISPs) that provide services to clients
+benefit from NFV, since it helps to better utilize their physical
+network.  In addition, when network services are virtualized, an ISP
+may support \emph{service chaining}~\cite{ServiceChaining15}, namely a
+compound service that consists of a sequence of VNFs.  Furthermore,
+one may offer a compound service a service that may be obtained using
+one of several sequences of VNFs.
+
+In this paper we study the allocation problem of a compund request for
+a service chain in a software-defined network that supports NFV.
+Given a (physical) network that contains servers with limited
+processing power and of links with limited bandwidth, a service chain
+is a sequence of virtual network functions (VNFs) that service a
+certain flow request in the network.
+%
+The allocation of a service chain consists of routing and VNF
+placement.  That is, each VNF from the seqeunce is placed in a server
+along a path, and it is feasible if each server can handle the VNFs
+that are assigned to it, and if each link on the path can carry the
+flow that is assigned to it.
+%
+A request for service is composed of a source and a destination in the
+network, an upper bound on the total latency, and a specification of
+all service chains that are considered valid for this request.
+%
+Each pair of server and VNF are associated with a cost for placing the
+network function in the server.  This cost measures compatibility of a
+VNF to a server (infinite costs means ``incompatible'').  Given a
+request, the goal is to find a valid service chain of minimum total
+cost or to identify that a valid service chain does not exist.
+
+\dror{Explain one shot approach}
+
+\paragraph*{\bf Related work.}
+%
+
+Cohen et al.~\cite{CLNR15} considered VNF placement.  In their model
+the input is an undirected graph with a metric distance function on
+the edges.  clients are located in various nodes, and each client is
+interested in a subset of VNFs.  For each node $v$ and VNF $\alpha$,
+there is a setup cost associated with placing a copy of $\alpha$ at
+$v$ (multiple copies are allowed), and there is a load that is induced
+on $v$ for placing a copy of $\alpha$.  Furthermore, each node has a
+limited capacity.  Also, each copy of a VNF can handle a limited
+amount of clients A solution is the assignment of each client to a
+subset of nodes, each corresponding to one of its required VNFs.  The
+cost of a solution is the total setup costs plus the sum of distances
+between the clients and the node from which they get service.
+%
+Cohen et al.~\cite{CLNR15} gave bi-criteria approximation algorithms
+for various versions of the problem, namely algorithms that compute
+constant factor approximations that violate the load constraints by a
+constant factor.
+%
+It is important to note that in this problem does not consider
+routing, and also it assumes unordered VNF subsets.
+
+Even, Medina, and Patt-Shamir~\cite{EMP16} studied online path
+computation and VNF placement.  They considered service chain requests
+that arrive in an online manner.  Each request is a a flow with a
+high-level specification of routing and VNF requirements.  Each VNF
+can be performed by a specified subset of servers in the system.  Upon
+arrival of a request, the algorithm either rejects the request or
+accepts it and with a specific routing and VNF assignment, under given
+server capacity constraints.  Each request has a benefit that is
+gained if it is accepted, and the goal is to maximize the total
+benefit.
+%
+Even, Medina, and Patt-Shamir~\cite{EMP16} proposed an algorithm that
+copes with requests with unknown duration without preemption by using
+a third response, which is refer to as “stand by”, whose competitive
+ratio is $O(\log (knb_{\max})$, where $n$ is the number of nodes,
+$b_{\max}$ is an upper bound on a request benefit per time unit, and
+$k$ is the maximum number of VNFs of any service chain.  This
+performance guarantee holds for the case where the processing of any
+processing request in any possible service chain is never more than
+$O(1/(k \log (nk)))$ fraction of the capacity of any network
+component.
+
+Even, Rost, and Schmid~\cite{ERS16}
+
+\dror{finish}
+
+\paragraph*{\bf Our results.}
+%
+We show that even the feasibility problem is NP-hard in general
+di-graphs.  Hence we first focus on directed acyclic graphs (DAGs).
+We show that the problem is still NP-hard in DAGs and present an
+FPTAS.
+%
+Based on out PTAS, we also provide a randomized algorithm for
+instances in which the service chain passes through a bounded number
+of servers whose degree is larger than two.
+
+?????
+
+\bigskip
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Preliminaries}
+
+\paragraph*{\bf Model.}
+%
+The \scplong (\scp) input is composed of three components, a physical
+network, a virtual specification, and placement costs:
+\begin{description}
+\item[Physical network:]
+%
+  The physical network is a digraph $G = (V,E)$.  Each node $v \in V$
+  has a non-negative processing capacity $p(v)$, and each directed
+  edge $e \in A$ has a non-negative bandwidth cap $b(e)$.
+
+\item[Virtual specification:]
+%
+  The description of a request for a service chain consists of a
+  physical source $s \in V$, a physical destination $t \in V$, and a
+  directed acyclic graph (DAG) $\calG = (\calV,\calE)$.
+%
+  Without loss of generality, we assume that $p(s) = p(t) = 0$.  
+%
+  The DAG $\calG$ has a source node $\sigma \in \calV$ and a
+  destination $\tau \in \calV$ Each node $\alpha \in \calV$ represent
+  a VNF that has a processing demand $p(\alpha)$.  Without loss of
+  generality, we assume that $p(\sigma) = p(\tau) = 0$.  Each edge
+  $\eps \in \calE$ has a bandwidth demand $b(\eps)$.
+
+\item[Placement costs:]
+%
+  There is a non-negative cost $c(\alpha,v)$ for placing the VNF
+  $\alpha$ in $v$.  We assume that $c(\sigma,s) = 0$ and $c(\sigma,v)
+  = \infty$, for every $v \neq s$.  Similarly, we assume that
+  $c(\tau,t) = 0$ and $c(\tau,v) = \infty$, for every $v \neq t$.
+\end{description}
+
+A solution consists of the following:
+\begin{description}
+\item[Virtual path:] A path from $\sigma$ to $\tau$ in $\calG$, namely
+  a sequence of vertices $\alpha_0,\ldots,\alpha_\ell$, where
+  $\alpha_0 = \sigma$, $\alpha_\ell = \tau$, and
+  $(\alpha_j,\alpha_{j+1}) \in \calE$, for every $j \in
+  \set{0,\ldots,\ell-1}$.
+
+\item[Physical path:] A simple path from $s$ to $t$ in $G$, namely a
+  sequence of node $v_0,\ldots,v_k$, where $v_0 = s$, $v_k = t$, and
+  $(v_i,v_{i+1}) \in E$, for every $i \in \set{0,\ldots,k-1}$.
+
+\item[Placement:] A function $f$ that maps the virtual path to the
+  physical path.  Formally, a placement is a function $f:
+  \set{\alpha_0,\ldots,\alpha_\ell} \to \set{v_0,\ldots,v_k}$
+  such that
+\begin{enumerate}
+\item If $f(\alpha_j) = v_i$ and $f(\alpha_{j+1}) = v_{i'}$, then $i
+  \leq i'$.
+\item $b(\alpha_j,\alpha_{j+1}) \leq b(v_i,v_{i+1})$, for every
+  $(v_i,v_{i+1}) \in \bar{f}(\alpha_j,\alpha_{j+1})$, where
+  $\bar{f}(\alpha_j,\alpha_{j+1})$ to be the set of physical edges
+  that correspond to it, i.e.,
+\[
+\bar{f}(\alpha_j,\alpha_{j+1}) \eqdf \set{(v_i,v_{i+1}) : i' \leq i < i''}
+~,
+\]
+  where $f(\alpha_j) = v_{i'}$ and $f(\alpha_{j+1}) = v_{i''}$.
+
+\item $\sum_{\alpha \in f^{-1}(v)} p(\alpha) \leq p(v)$, where
+  $f^{-1}(v) \eqdf \set{\alpha : f(\alpha) = v}$.
+
+\end{enumerate}
+\end{description}
+
+An example of an \scp instance and a solution is given in
+Figure~\ref{fig:solution}.
+
+\begin{figure}
+\centering
+\scalebox{1}{
+\input{fig-embedding}
+}
+\caption{???}
+\label{fig:solution}
+\end{figure}
+
+The cost of a placement $f$ is:
+\[
+\sum_j c(\alpha_j,f(\alpha_j))
+~.
+\]
+In \scp the goal is to find a feasible placement of a virtual path
+into the physical DAG that minimizes the cost.
+
+%%%%%
+
+We also consider an extended version of \scp in which each physical
+link causes a delay and there is an upper bound $T$ on the total
+delay.  More formally, each pair of a virtual edge $\eps$ and physical
+edge $e$ is associated with a latency $t(\eps,e)$.
+%
+Given a placement $f: \set{\alpha_0,\ldots,\alpha_\ell} \to
+\set{v_0,\ldots,v_k}$, the total latency of the solution is given by
+\[
+T(f) = \sum_j \sum_{e \in \bar{f}(\eps)} t(\eps,e)
+~.
+\]
+In this case there is an additional constraint that $T(f) \leq T$.
+
+%%%%%
+
+\paragraph*{\bf Definitions and notation.}
+%
+Define $n_p \eqdf \abs{V}$ and $m_p \eqdf \abs{E}$.  Similarly, define
+$n_v \eqdf \abs{\calV}$ and $m_v \eqdf \abs{\calE}$.
+
+Given a virtual DAG $\calG$, we assume the existence of a topological
+sorting of the vertices and write $\alpha \prec_v \beta$ if $\alpha$
+precedes $\beta$ in this ordering.  If the physical network is a DAG,
+then we make a similar assumption and write $v \prec_p u$ if $v$
+precedes $u$ in this ordering.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Hardness}
+
+In this section we present two hardness results.  First, we show that
+even the feasibility question of \scp is NP-hard, and therefore no
+approximation algorithm exists for \scp.  In addition, we show that
+\scp is NP-hard even if $\abs{V \setminus \set{s,t}} = 1$.  We also
+show that \scp is NP-hard even if both the physical network and the
+virtual DAG are simple paths.
+
+We show that finding a feasible solution is NP-hard.
+
+\begin{theorem}
+Feasibility of \scp is NP-hard
+\end{theorem}
+\begin{proof}
+We use a reduction from \textsc{Hamiltonian Path} that is known to be
+NP-hard~\cite{GarJoh79}.
+%
+Given an instance $H$ of \textsc{Hamiltonian Path} we construct an
+instance of \scp.  For the physical network we have that $G$, where
+$V(G) = V(H) \cup \set{s,t}$, and $E(G) = E(H) \cup \set{(s,v),(v,t) :
+  v \in V(H)}$.  In addition, $p(v) = 1$, for every $v$, and $b(e) =
+1$, for every $e$.  The virtual DAG $\calG$ is a path containing $n+2$
+virtual functions, $\sigma = \alpha_0, \alpha_1, \ldots, \alpha_n,
+\alpha_{n+1} = \tau$, where $p(\alpha_i) = 1$, for every $i \in
+\set{1,\ldots,n}$.  Also, $b(\alpha_i,\alpha_{i+1}) = 1$, for every
+$i$.
+
+The construction can clearly be computed in polynomial time.
+%
+An Hamiltonian Path in $G$, induces a \scp solution that follows the
+path, i.e., $\alpha_i$ is placed in the $i$th vertex along the path.
+%
+One the other hand, since all demands and capacities are $1$, no two
+VNFs can share a physical node.  Hence a \scp solution induces an
+Hamiltonian path.
+%
+\qed
+\end{proof}
+
+Next, we show that \scp is NP-hard even if the physical network is a
+DAG.
+
+\begin{theorem}
+\scp is NP-hard, even if $\abs{V \setminus \set{s,t}} = 1$.
+\end{theorem}
+\begin{proof}
+The prove the theorem using a reduction from \textsc{Partition}.
+Given a \textsc{Partition} instance $\set{a_1, \ldots, a_n}$ we
+construct an \scp instance as follows.
+%
+The physical network $G$ contains three nodes: $s$, $v$, and $t$, and
+there are two edges $(s,v)$ and $(v,t)$.  The capacity of $v$ is $p(v)
+= \half \sum_i a_i$.  Edge capacities are zero.
+%
+The virtual DAG is composed of $2n+2$ vertices, namely
+\[
+\calV
+= \set{\sigma,\tau}
+  \cup \set{\alpha_1, \ldots, \alpha_n}
+  \cup \set{\beta_1, \ldots, \beta_n}
+~.
+\]
+Also,
+\[
+\calE
+= \bigcup_i \set{ \set{\alpha_i,\beta_i} \times \set{\alpha_{i+1},\beta_{i+1}} } 
+  \cup
+  \set{ (\sigma,\alpha_1), (\sigma,\beta_1), (\alpha_n,t), (\beta_n,t) }
+~.
+\]
+The DAG is shown in Figure~\ref{fig:dag}.
+%
+The demands are $p(\alpha_i) = a_i$ and $p(\beta_i) = 0$, for every
+$i$.  Also, $b(\eps) = 0$, for every $\eps \in \calE$.  The costs are:
+$c(\alpha_i,v) = 0$ and $c(\beta_i,v) = a_i$, for every $i$.
+
+The \scp instance can be computed in polynomial time.
+%
+Also, it is not hard to verify that $a \in \textsc{Partition}$ if and
+only if there exists a solution whose cost is $\half \sum_i a_i$.
+%
+\qed
+\end{proof}
+
+\begin{figure}
+\centering
+\input{fig-reduction}
+\caption{???}
+\label{fig:dag}
+\end{figure}
+
+\dror{Figure 2: source and destination should be fixed}
+
+\begin{theorem}
+\scp is NP-hard, even if both the physical network and the virtual DAG
+are paths.
+\end{theorem}
+\begin{proof}
+
+\dror{reduction from partition using latency}
+
+%
+\qed
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Algorithm}
+\input{algorithm}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Latency}
+\input{latency}
+
+\section{Undirected Graphs}
+\input{graphs}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibliographystyle{abbrv}
+\bibliography{chain}
 

### 2017-06-23 src/graphs.tex
foo

@@
-In this section we consider the problem on undirected (physical) graphs.
+In this section we consider the problem when the physical network is undirected.
 Once again we seek to embed a virtual $\sigma\tau$-path 
@@
 Recall that the problem on general graphs cannot be approximate at all,
-thus we assume in this section that the there exists an optimal embedding using
-at most $k$ \emph{heavy} vertices, thus are vertices with degree greater than two.
-The modified algorithm runs in time polynomial in the input length and
-exponential in $k$ and achieves the same guarantees as before with high
-probability.
+thus we assume in this section that there exists an optimal embedding that uses
+a physical path with at most $k$ \emph{heavy} vertices, thus are vertices with
+degree greater than two (we do not assume anything about the physical network).
+The modified algorithm includes a preprocessing stage that applies
+random orientation to the physical network, it runs in time polynomial in the
+input length and in $O(k!)$ and finds the optimal embedding with high probability.
 
-The modified algorithm acts as follow:
-let $K = {v_1, \ldots, v_k}$ be the set of heavy vertices, and let 
-$\pi:[k] \to [k]$ be a random permutation.
-Let $v_1, v_l \in K$ be two heavy vertices such that $\pi(v_1) < \pi(v_l)$ and
-let $w_1, \ldots, w_l$ any light path between them, i.e. a path that does not
-contains any other heavy vertex.
-We orient the edges from $u$ to $v$, i.e. $(w_i, w_{i+1})$ for every 
-$1 \leq i \leq l - 1$.
-One can be verify that this can be done efficiently and that after this process
-each edge become an arc and that $G$ is a DAG.
+The preprocessing stage is as follow:
+let $V_h = {v_1, \ldots, v_h}$ be the set of heavy vertices, and let 
+$\pi:[h] \to [h]$ be a random permutation.
+Let $w_1, \ldots, w_l$ be a light path, that is, $w_1, w_l \in V_j$, 
+$\forall 1 < i < l, w_i \notin V_h$, $\pi(w_1) < \pi(w_l)$, then
+we direct the edges from $w_1$ to $w_l$ i.e. $(w_i, w_{i+1})$ for every $1 \leq
+i \leq l - 1$.
+One can verifies that this can be done efficiently and that when this process
+terminates $G$ is a DAG, Figure~\ref{fig:orientation} depicts the preprocessing
+stage.
+
+\begin{figure}[h]
+\input{fig-orientation}
+\caption{
+\label{fig:orientation}
+The preprocessing stage: on the left is the undirected physical network,
+Only the heavy nodes are drawn.
+The numbers represent the permutation and the blue, dashed path represents a
+path of an optimal embedding.
+On the right side is the orientated physical network, 
+note that it is enough that the internal ordering of the nodes on the blue,
+dashed path is "correct" to ensure that the algorithm finds the optimal
+embedding. }
+\end{figure}
 

### 2017-06-23 src/main.tex
foo

--- 2017-04-26 src/main.tex
@@
 \nonstopmode
-\documentclass[draft]{article}
+%\documentclass[11pt]{article}
+\documentclass[runningheads]{llncs}
 
-\input{libs}
-\input{def}
+\usepackage{amsmath,amssymb,mathtools}
+%\usepackage{amsthm}
+%\usepackage{fullpage}
+\usepackage{xspace}
+\usepackage{color,soul}
+\usepackage{paralist}
+
+% \usepackage[linesnumbered, ruled]{algorithm2e}
+
+\usepackage[final]{microtype}
+\usepackage[final]{hyperref}
+\usepackage{subcaption}
+
+% DEBUG
+%\usepackage{lipsum}
+\usepackage{todonotes}
+%\usepackage{lineno}
+%\linenumbers
+
+% EXTRA
+%\usepackage{authblk}
+
 \input{tikz}
 
-\input{title}
-\input{authors}
+\def\VPN{Service Chain Placement in SDN}
+\def\R{\mathbb{R}}
+\def\N{\mathbb{N}}
+
+\sloppy
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% handy commands
+
+\newcommand{\eqdf}{\stackrel{\scriptscriptstyle \triangle}{=}}
+\newcommand{\argmin}{\ensuremath{\mbox{argmin}}}
+\newcommand{\argmax}{\ensuremath{\mbox{argmax}}}
+\newcommand{\set}[1]{\left\{ #1 \right\}}
+\newcommand{\paren}[1]{\left( #1 \right)}
+\newcommand{\bit}{\set{0,1}}
+\newcommand{\inv}[1]{\frac{1}{#1}}
+\newcommand{\abs}[1]{\left| #1 \right|}
+\newcommand{\ceil}[1]{\left\lceil {#1} \right\rceil}
+\newcommand{\floor}[1]{\left\lfloor {#1} \right\rfloor}
+\newcommand{\half}{\frac{1}{2}}
+\newcommand{\threehalves}{\frac{3}{2}}
+
+\newcommand{\naturals}{\mathbb{N}}
+\newcommand{\rationals}{\mathbb{Q}}
+\newcommand{\reals}{\mathbb{R}}
+\newcommand{\integers}{\mathbb{Z}}
+
+\newcommand{\eps}{\varepsilon}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newcommand{\scp}{\textsc{SCP}\xspace}
+\newcommand{\scplong}{\textsc{Service Chain Placement}\xspace}
+
+\newcommand{\calE}{\mathcal{E}}
+\newcommand{\calG}{\mathcal{G}}
+\newcommand{\calV}{\mathcal{V}}
+
+\newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title{\bf Service Chain Placement in SDNs%
+\thanks{Research supported in part by Network Programming (Neptune)
+  Consortium, Israel.}
+}
+
+\titlerunning{Service Chain Placement in SDNs}
+
+%\author[1]{Gilad Kutiel%
+%\thanks{E-mail: \texttt{gkutiel@cs.technion.ac.il}}}
+
+%\author[2]{Dror Rawitz%
+%\thanks{Partially supported by the Israel Science Foundation
+%  (grant no.~497/14).  E-mail: \texttt{dror.rawitz@biu.ac.il}}}
+
+%\affil[1]{Department of Computer Science, Technion, Haifa, Israel}
+%\affil[2]{Faculty of Engineering, Bar Ilan University, Ramt-Gan, Israel}
+
+\author{%
+Gilad Kutiel
+\and
+Dror Rawitz%
+\thanks{Partially supported by the Israel Science Foundation
+  (grant no.~497/14).  }
+}
+
+\institute{%
+Department of Computer Science, Technion, Haifa 32000, Israel. \\
+\email{gkutiel@cs.technion.ac.il}
+\and
+Faculty of Engineering, Bar Ilan University, Ramt-Gan 52900, Israel.\\
+\email{dror.rawitz@biu.ac.il}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\input{outline}
+% \begin{abstract}
+% We study the allocation problem of a \emph{service chain} in a
+% software-defined network that supports network function
+% virtualization.
+% %
+% Given a network that contains servers with limited processing power
+% and of links with limited bandwidth, a service chain is a sequence of
+% virtual network functions (VNFs) that service a certain flow request
+% in the network.
+% %
+% The allocation of a service chain consists of routing and VNF
+% placement.  That is, each VNF from the seqeunce is placed in a server
+% along a path, and it is feasible if each server can handle the VNFs
+% that are assigned to it, and if each link on the path can carry the
+% flow that is assigned to it.
+% %
+% A request for service is composed of a source and a destination in the
+% network, an upper bound on the total latency, and a specification of
+% all service chains that are considered valid for this request.
+% %
+% Each pair of server and VNF are associated with a cost for placing the
+% network function in the server, and given a request, the goal is to
+% find a valid service chain of minimum total cost or to identify that
+% a valid service chain does not exist.
+% 
+% We show that even the feasibility problem is NP-hard in general
+% di-graphs.  Hence we first focus on directed acyclic graphs (DAGs).
+% We show that the problem is still NP-hard in DAGs and present an
+% FPTAS.
+% %
+% Based on out PTAS, we also provide a randomized algorithm for
+% instances in which the service chain passes through a bounded number
+% of servers whose degree is larger than two.
+% 
+% ?????
+% 
+% Fault tolerant placement: two service chains?
+% 
+% FPT algorithm where the number of servers whose degree is larger than
+% two is a parameter?
+% \end{abstract}
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% \section{Introduction}
+% 
+% 
+% Computer communication networks are in constant need of expansion to
+% cope with the ever growing traffic.  As networks grow, management and
+% maintenance become more and more complicated.
+% %
+% Current developments aim to improve the utilization of network
+% resources include the detachment of network applications from network
+% infrastructure and the transition from network planning to network
+% programming.
+% 
+% One aspect of network programming is to manage resources from a
+% central point of view, namely to make decisions based on availability,
+% network status, required quality of service, and the identity of the
+% client.  Hence, a central issue is a central agent that is able to
+% received reports from network components and client requests, and as a
+% result can alter the allocation of resources in the networks.  This
+% approach is called Software Defined Networking (SDN), where there is a
+% separation between routing and management (control plane) and the
+% underlying routers and switches that forward traffic (data plane) (see
+% Kreutz et al.~\cite{KRVRAU15}).
+% 
+% A complimentary approach is Network Function Virtualization
+% (NFV)~\cite{NFV12}.  Instead of relying on special purpose machines,
+% network applications become virtual network functions (VNF) that are
+% executed on generic machines and can be placed in various locations in
+% the network.  Virtualization increases the flexibility of resource
+% allocation and thus the utilization of the network resources.
+% %
+% Internet Service Providers (ISPs) that provide services to clients
+% benefit from NFV, since it helps to better utilize their physical
+% network.  In addition, when network services are virtualized, an ISP
+% may support \emph{service chaining}~\cite{ServiceChaining15}, namely a
+% compound service that consists of a sequence of VNFs.  Furthermore,
+% one may offer a compound service a service that may be obtained using
+% one of several sequences of VNFs.
+% 
+% In this paper we study the allocation problem of a compund request for
+% a service chain in a software-defined network that supports NFV.
+% Given a (physical) network that contains servers with limited
+% processing power and of links with limited bandwidth, a service chain
+% is a sequence of virtual network functions (VNFs) that service a
+% certain flow request in the network.
+% %
+% The allocation of a service chain consists of routing and VNF
+% placement.  That is, each VNF from the seqeunce is placed in a server
+% along a path, and it is feasible if each server can handle the VNFs
+% that are assigned to it, and if each link on the path can carry the
+% flow that is assigned to it.
+% %
+% A request for service is composed of a source and a destination in the
+% network, an upper bound on the total latency, and a specification of
+% all service chains that are considered valid for this request.
+% %
+% Each pair of server and VNF are associated with a cost for placing the
+% network function in the server.  This cost measures compatibility of a
+% VNF to a server (infinite costs means ``incompatible'').  Given a
+% request, the goal is to find a valid service chain of minimum total
+% cost or to identify that a valid service chain does not exist.
+% 
+% 
+% \dror{Explain one shot approach}
+% 
+% \paragraph*{\bf Related work.}
+% %
+% 
+% Cohen et al.~\cite{CLNR15} considered VNF placement.  In their model
+% the input is an undirected graph with a metric distance function on
+% the edges.  clients are located in various nodes, and each client is
+% interested in a subset of VNFs.  For each node $v$ and VNF $\alpha$,
+% there is a setup cost associated with placing a copy of $\alpha$ at
+% $v$ (multiple copies are allowed), and there is a load that is induced
+% on $v$ for placing a copy of $\alpha$.  Furthermore, each node has a
+% limited capacity.  Also, each copy of a VNF can handle a limited
+% amount of clients A solution is the assignment of each client to a
+% subset of nodes, each corresponding to one of its required VNFs.  The
+% cost of a solution is the total setup costs plus the sum of distances
+% between the clients and the node from which they get service.
+% %
+% Cohen et al.~\cite{CLNR15} gave bi-criteria approximation algorithms
+% for various versions of the problem, namely algorithms that compute
+% constant factor approximations that violate the load constraints by a
+% constant factor.
+% %
+% It is important to note that in this problem does not consider
+% routing, and also it assumes unordered VNF subsets.
+% 
+% Even, Medina, and Patt-Shamir~\cite{EMP16} studied online path
+% computation and VNF placement.  They considered service chain requests
+% that arrive in an online manner.  Each request is a a flow with a
+% high-level specification of routing and VNF requirements.  Each VNF
+% can be performed by a specified subset of servers in the system.  Upon
+% arrival of a request, the algorithm either rejects the request or
+% accepts it and with a specific routing and VNF assignment, under given
+% server capacity constraints.  Each request has a benefit that is
+% gained if it is accepted, and the goal is to maximize the total
+% benefit.
+% %
+% Even, Medina, and Patt-Shamir~\cite{EMP16} proposed an algorithm that
+% copes with requests with unknown duration without preemption by using
+% a third response, which is refer to as “stand by”, whose competitive
+% ratio is $O(\log (knb_{\max})$, where $n$ is the number of nodes,
+% $b_{\max}$ is an upper bound on a request benefit per time unit, and
+% $k$ is the maximum number of VNFs of any service chain.  This
+% performance guarantee holds for the case where the processing of any
+% processing request in any possible service chain is never more than
+% $O(1/(k \log (nk)))$ fraction of the capacity of any network
+% component.
+% 
+% Even, Rost, and Schmid~\cite{ERS16}
+% 
+% \dror{finish}
+% 
+% \paragraph*{\bf Our results.}
+% %
+% We show that even the feasibility problem is NP-hard in general
+% di-graphs.  Hence we first focus on directed acyclic graphs (DAGs).
+% We show that the problem is still NP-hard in DAGs and present an
+% FPTAS.
+% %
+% Based on out PTAS, we also provide a randomized algorithm for
+% instances in which the service chain passes through a bounded number
+% of servers whose degree is larger than two.
+% 
+% ?????
+% 
+% \bigskip
+% 
+% 
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% \section{Preliminaries}
+% 
+% 
+% \paragraph*{\bf Model.}
+% %
+% The \scplong (\scp) input is composed of three components, a physical
+% network, a virtual specification, and placement costs:
+% \begin{description}
+% \item[Physical network:]
+% %
+%   The physical network is a digraph $G = (V,E)$.  Each node $v \in V$
+%   has a non-negative processing capacity $p(v)$, and each directed
+%   edge $e \in A$ has a non-negative bandwidth cap $b(e)$.
+% 
+% \item[Virtual specification:]
+% %
+%   The description of a request for a service chain consists of a
+%   physical source $s \in V$, a physical destination $t \in V$, and a
+%   directed acyclic graph (DAG) $\calG = (\calV,\calE)$.
+% %
+%   Without loss of generality, we assume that $p(s) = p(t) = 0$.  
+% %
+%   The DAG $\calG$ has a source node $\sigma \in \calV$ and a
+%   destination $\tau \in \calV$ Each node $\alpha \in \calV$ represent
+%   a VNF that has a processing demand $p(\alpha)$.  Without loss of
+%   generality, we assume that $p(\sigma) = p(\tau) = 0$.  Each edge
+%   $\eps \in \calE$ has a bandwidth demand $b(\eps)$.
+%   
+% \item[Placement costs:]
+% %
+%   There is a non-negative cost $c(\alpha,v)$ for placing the VNF
+%   $\alpha$ in $v$.  We assume that $c(\sigma,s) = 0$ and $c(\sigma,v)
+%   = \infty$, for every $v \neq s$.  Similarly, we assume that
+%   $c(\tau,t) = 0$ and $c(\tau,v) = \infty$, for every $v \neq t$.
+% \end{description}
+% 
+% A solution consists of the following:
+% \begin{description}
+% \item[Virtual path:] A path from $\sigma$ to $\tau$ in $\calG$, namely
+%   a sequence of vertices $\alpha_0,\ldots,\alpha_\ell$, where
+%   $\alpha_0 = \sigma$, $\alpha_\ell = \tau$, and
+%   $(\alpha_j,\alpha_{j+1}) \in \calE$, for every $j \in
+%   \set{0,\ldots,\ell-1}$.
+% 
+% \item[Physical path:] A simple path from $s$ to $t$ in $G$, namely a
+%   sequence of node $v_0,\ldots,v_k$, where $v_0 = s$, $v_k = t$, and
+%   $(v_i,v_{i+1}) \in E$, for every $i \in \set{0,\ldots,k-1}$.
+%   
+% \item[Placement:] A function $f$ that maps the virtual path to the
+%   physical path.  Formally, a placement is a function $f:
+%   \set{\alpha_0,\ldots,\alpha_\ell} \to \set{v_0,\ldots,v_k}$
+%   such that
+% \begin{enumerate}
+% \item If $f(\alpha_j) = v_i$ and $f(\alpha_{j+1}) = v_{i'}$, then $i
+%   \leq i'$.
+% \item $b(\alpha_j,\alpha_{j+1}) \leq b(v_i,v_{i+1})$, for every
+%   $(v_i,v_{i+1}) \in \bar{f}(\alpha_j,\alpha_{j+1})$, where
+%   $\bar{f}(\alpha_j,\alpha_{j+1})$ to be the set of physical edges
+%   that correspond to it, i.e.,
+% \[
+% \bar{f}(\alpha_j,\alpha_{j+1}) \eqdf \set{(v_i,v_{i+1}) : i' \leq i < i''}
+% ~,
+% \]
+%   where $f(\alpha_j) = v_{i'}$ and $f(\alpha_{j+1}) = v_{i''}$.
+% 
+% \item $\sum_{\alpha \in f^{-1}(v)} p(\alpha) \leq p(v)$, where
+%   $f^{-1}(v) \eqdf \set{\alpha : f(\alpha) = v}$.
+%  
+% \end{enumerate}
+% \end{description}
+% 
+% An example of an \scp instance and a solution is given in
+% Figure~\ref{fig:solution}.
+% 
+% \begin{figure}
+% \centering
+% \scalebox{1}{
+% \input{fig-embedding}
+% }
+% \caption{???}
+% \label{fig:solution}
+% \end{figure}
+% 
+% The cost of a placement $f$ is:
+% \[
+% \sum_j c(\alpha_j,f(\alpha_j))
+% ~.
+% \]
+% In \scp the goal is to find a feasible placement of a virtual path
+% into the physical DAG that minimizes the cost.
+% 
+% %%%%%
+% 
+% We also consider an extended version of \scp in which each physical
+% link causes a delay and there is an upper bound $T$ on the total
+% delay.  More formally, each pair of a virtual edge $\eps$ and physical
+% edge $e$ is associated with a latency $t(\eps,e)$.
+% %
+% Given a placement $f: \set{\alpha_0,\ldots,\alpha_\ell} \to
+% \set{v_0,\ldots,v_k}$, the total latency of the solution is given by
+% \[
+% T(f) = \sum_j \sum_{e \in \bar{f}(\eps)} t(\eps,e)
+% ~.
+% \]
+% In this case there is an additional constraint that $T(f) \leq T$.
+% 
+% 
+% %%%%%
+% 
+% \paragraph*{\bf Definitions and notation.}
+% %
+% Define $n_p \eqdf \abs{V}$ and $m_p \eqdf \abs{E}$.  Similarly, define
+% $n_v \eqdf \abs{\calV}$ and $m_v \eqdf \abs{\calE}$.
+% 
+% Given a virtual DAG $\calG$, we assume the existence of a topological
+% sorting of the vertices and write $\alpha \prec_v \beta$ if $\alpha$
+% precedes $\beta$ in this ordering.  If the physical network is a DAG,
+% then we make a similar assumption and write $v \prec_p u$ if $v$
+% precedes $u$ in this ordering.
+% 
+% 
+% 
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% \section{Hardness}
+% 
+% In this section we present two hardness results.  First, we show that
+% even the feasibility question of \scp is NP-hard, and therefore no
+% approximation algorithm exists for \scp.  In addition, we show that
+% \scp is NP-hard even if $\abs{V \setminus \set{s,t}} = 1$.  We also
+% show that \scp is NP-hard even if both the physical network and the
+% virtual DAG are simple paths.
+% 
+% We show that finding a feasible solution is NP-hard.
+% 
+% \begin{theorem}
+% Feasibility of \scp is NP-hard
+% \end{theorem}
+% \begin{proof}
+% We use a reduction from \textsc{Hamiltonian Path} that is known to be
+% NP-hard~\cite{GarJoh79}.
+% %
+% Given an instance $H$ of \textsc{Hamiltonian Path} we construct an
+% instance of \scp.  For the physical network we have that $G$, where
+% $V(G) = V(H) \cup \set{s,t}$, and $E(G) = E(H) \cup \set{(s,v),(v,t) :
+%   v \in V(H)}$.  In addition, $p(v) = 1$, for every $v$, and $b(e) =
+% 1$, for every $e$.  The virtual DAG $\calG$ is a path containing $n+2$
+% virtual functions, $\sigma = \alpha_0, \alpha_1, \ldots, \alpha_n,
+% \alpha_{n+1} = \tau$, where $p(\alpha_i) = 1$, for every $i \in
+% \set{1,\ldots,n}$.  Also, $b(\alpha_i,\alpha_{i+1}) = 1$, for every
+% $i$.
+% 
+% The construction can clearly be computed in polynomial time.
+% %
+% An Hamiltonian Path in $G$, induces a \scp solution that follows the
+% path, i.e., $\alpha_i$ is placed in the $i$th vertex along the path.
+% %
+% One the other hand, since all demands and capacities are $1$, no two
+% VNFs can share a physical node.  Hence a \scp solution induces an
+% Hamiltonian path.
+% %
+% \qed
+% \end{proof}
+% 
+% Next, we show that \scp is NP-hard even if the physical network is a
+% DAG.
+% 
+% \begin{theorem}
+% \scp is NP-hard, even if $\abs{V \setminus \set{s,t}} = 1$.
+% \end{theorem}
+% \begin{proof}
+% The prove the theorem using a reduction from \textsc{Partition}.
+% Given a \textsc{Partition} instance $\set{a_1, \ldots, a_n}$ we
+% construct an \scp instance as follows.
+% %
+% The physical network $G$ contains three nodes: $s$, $v$, and $t$, and
+% there are two edges $(s,v)$ and $(v,t)$.  The capacity of $v$ is $p(v)
+% = \half \sum_i a_i$.  Edge capacities are zero.
+% %
+% The virtual DAG is composed of $2n+2$ vertices, namely
+% \[
+% \calV
+% = \set{\sigma,\tau}
+%   \cup \set{\alpha_1, \ldots, \alpha_n}
+%   \cup \set{\beta_1, \ldots, \beta_n}
+% ~.
+% \]
+% Also,
+% \[
+% \calE
+% = \bigcup_i \set{ \set{\alpha_i,\beta_i} \times \set{\alpha_{i+1},\beta_{i+1}} } 
+%   \cup
+%   \set{ (\sigma,\alpha_1), (\sigma,\beta_1), (\alpha_n,t), (\beta_n,t) }
+% ~.
+% \]
+% The DAG is shown in Figure~\ref{fig:dag}.
+% %
+% The demands are $p(\alpha_i) = a_i$ and $p(\beta_i) = 0$, for every
+% $i$.  Also, $b(\eps) = 0$, for every $\eps \in \calE$.  The costs are:
+% $c(\alpha_i,v) = 0$ and $c(\beta_i,v) = a_i$, for every $i$.
+% 
+% The \scp instance can be computed in polynomial time.
+% %
+% Also, it is not hard to verify that $a \in \textsc{Partition}$ if and
+% only if there exists a solution whose cost is $\half \sum_i a_i$.
+% %
+% \qed
+% \end{proof}
+% 
+% \begin{figure}
+% \centering
+% \input{fig-reduction}
+% \caption{???}
+% \label{fig:dag}
+% \end{figure}
+% 
+% \dror{Figure 2: source and destination should be fixed}
+% 
+% \begin{theorem}
+% \scp is NP-hard, even if both the physical network and the virtual DAG
+% are paths.
+% \end{theorem}
+% \begin{proof}
+% 
+% \dror{reduction from partition using latency}
+%   
+% %
+% \qed
+% \end{proof}
 
-\bibliographystyle{plain}
-\bibliography{main}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Algorithm}
+\input{algorithm}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Latency}
+\input{latency}
+
+\section{Undirected Graphs}
+\input{graphs}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibliographystyle{abbrv}
+\bibliography{chain}
 

### 2017-06-23 src/algorithm.tex
foo

@@
 $1 + \varepsilon$ times greater that of the optimal solution, for any
-$\varepsilon > 0$, i.e. an FPTAS also for an arbitrary cost function.
+$\varepsilon > 0$, i.e. an FPTAS, for an arbitrary cost function.
 We also extend our algorithm when every physical arc carry some latency on it
 and a global latency constraint is given.
+Our algorithms are recursive and can be efficiently computed using dynamic
+programming.
 
@@
 \begin{align*}
-D_v = (\beta , A_v)		\\
-D_p = (v, A_p)		\\
+\calG = (\calV, \calE)		\\
+G = (V, E)		\\
 (\sigma , \tau , s, t)	\\
-(p_d, b_d, p_c, b_c, c)
+(p, b, c)
 \end{align*}
-Also, for convenient and w.l.o.g, assume that $\sigma , \tau $ are dummy vertices, 
-i.e. $c(\sigma , v) = c(\tau , v) = 0$ for every $v \in V_p$ and that
-$b_d(\sigma\alpha) = b_d(\alpha\tau) = 0$ for every $\alpha \in V_v$.
 
-We start by arguing that the minimum processing time required to embed some
-$\alpha \gamma $-path into a vertex $v$ given a cost constraint can be computed
-efficiently.
-Let $P_{v}(\alpha , \gamma , C)$ denote the minimum processing required to embed
-all the virtual vertices, excluding $\alpha $, on a $\alpha \gamma $-path into the physical
+We start by arguing that a minimum cost 
+$\alpha \gamma $-path with respect to vertex $v$ can be
+found efficiently, that is a virtual $\alpha \gamma $-path that can be embedded 
+into $v$ without violating its processing capacity that has the minimum cost
+among all those paths.
+Let $P_{v}(\alpha ,\gamma , C)$ 
+denote the minimum processing required to embed all the virtual vertices, excluding $\alpha $, on a $\alpha \gamma $-path into the physical
 vertex $v$ with a cost constraint $C$.
@@
 &P_{v}(\alpha , \gamma , C) = 
-\min_{\alpha \beta  \in A_v} P_{v}(\alpha , \beta , C - c(\gamma , v))
+\min_{\alpha \beta  \in \calE} P_{v}(\alpha , \beta , C - c(\gamma , v))
 \\
@@
 \end{align*}
+Computing $\min_{C : P_v(\alpha, \gamma, C) \leq p(v)}$ gives the desired
+result.
 
@@
 \\
-vw \in A_p
+vw \in E
 }}
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering

### 2017-06-23 src/graphs.tex
foo

@@
 Note, that we still assume that the virtual graph is a DAG. 
+We extend our algorithm to work for this case as well.
 
-We extend our algorithm to work also for this case as well.
 Recall that the problem on general graphs cannot be approximate at all,
@@
 The modified algorithm includes a preprocessing stage that applies
-random orientation to the physical network, it runs in time polynomial in the
-input length and in $O(k!)$ and finds the optimal embedding with high probability.
+random orientation to the physical network, the entire algorithm runs in
+$O(t(n)k!)$, where $t(n)$ is the time it takes to compute the optimal embedding when the
+physical network is a DAG, and finds the optimal embedding with high
+probability.
 
 The preprocessing stage is as follow:
-let $V_h = {v_1, \ldots, v_h}$ be the set of heavy vertices, and let 
-$\pi:[h] \to [h]$ be a random permutation.
-Let $w_1, \ldots, w_l$ be a light path, that is, $w_1, w_l \in V_j$, 
-$\forall 1 < i < l, w_i \notin V_h$, $\pi(w_1) < \pi(w_l)$, then
-we direct the edges from $w_1$ to $w_l$ i.e. $(w_i, w_{i+1})$ for every $1 \leq
-i \leq l - 1$.
+let $V_h$ be the set of heavy vertices, and let 
+$\pi:V_h \to [|V_h|]$ be a random permutation.
+For every \emph{light path} $w_1, \ldots, w_l$, that is, $w_1, w_l \in
+V_h$, $\pi(w_1) < \pi(w_l)$, and $\forall_{1 < i < l}, w_i \notin V_h$,
+we direct the edges from $w_1$ to $w_l$ i.e. $w_i \to w_{i+1}$ for every $1
+\leq i \leq l - 1$.
 One can verifies that this can be done efficiently and that when this process
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \input{fig-orientation}
@@
 keep the best embedding so far.
-
-We claim that with high probability, after $O(k!)$ iterations, the above
-algorithm finds the optimal embedding, formally:
+Note that if there is an optimal embedding using a physical path with at most
+$k$ heavy vertices then it is sufficient that those vertices are ordered
+"correctly" w.r.t $\pi$, regardless of the order $\pi$ applies to all other
+heavy vertices, to ensure that the algorithm finds the optimal embedding.
+We claim that with high probability, 
+after $O(k!)$ iterations, the above algorithm finds the optimal embedding, formally:
 
@@
 \begin{proof}
-Consider an optimal embedding and the order it induces on the heavy vertices,
-If the random permutation order the heavy vertices in that order we are
-guaranteed to find the optimal embedding.
+Consider an optimal embedding and the order it induces on the heavy vertices in
+the physical path (at most $k$ such vertices), if the random permutation orders
+the heavy vertices correctly, i.e. in that order, we are guaranteed to find the
+optimal embedding.
 This happens with probability $1/k!$ and the probability to miss the optimal

### 2017-06-23 src/algorithm.tex
foo

@@
 $\varepsilon > 0$, i.e. an FPTAS, for an arbitrary cost function.
-We also extend our algorithm when every physical arc carry some latency on it
-and a global latency constraint is given.
-Our algorithms are recursive and can be efficiently computed using dynamic
+It is a recursive algorithm that can be efficiently implemented using dynamic
 programming.
@@
 \end{align*}
-
-We start by arguing that a minimum cost 
-$\alpha \gamma $-path with respect to vertex $v$ can be
-found efficiently, that is a virtual $\alpha \gamma $-path that can be embedded 
-into $v$ without violating its processing capacity that has the minimum cost
-among all those paths.
-Let $P_{v}(\alpha ,\gamma , C)$ 
-denote the minimum processing required to embed all the virtual vertices, excluding $\alpha $, on a $\alpha \gamma $-path into the physical
-vertex $v$ with a cost constraint $C$.
-$P$ can be computed recursively as follow:
-\begin{align*}
-&P_{v}(\alpha , \gamma , C) = 
-\min_{\alpha \beta  \in \calE} P_{v}(\alpha , \beta , C - c(\gamma , v))
-\\
-&P(\alpha , \alpha , C) = 0
-\\
-&P(-, -, <0) = \infty
-\end{align*}
-Computing $\min_{C : P_v(\alpha, \gamma, C) \leq p(v)}$ gives the desired
-result.
-
-We now show how to compute the optimal embedding.
-Let $C(\gamma , w)$ denote the
-optimal embedding of a $\sigma \gamma $-path into a $sw$-path.
-Let $\pi:\beta  \to \N$ be any typological ordering of $\beta $. 
-We claim that $C$ can be computed recursively as follow:
-\begin{align*}
-&C(\gamma , w) = 
-\min_{\substack{
-\alpha  : \pi(\alpha ) \leq \pi(\beta ), 
-\\
-vw \in E
-}}
-C(\alpha , u)
-+
-\argmin_{C : P_{w}(\beta , \gamma , C) \leq p_c(w)}
-\\
-&C(\sigma , w) = c(\sigma , w)
-\end{align*}
-Now, to compute the optimal embedding, one need to compute $C(\tau , t)$. 
-We also note that in order to obey to the bandwidth constraints, 
-one need to temporally remove all edges $\alpha \beta $ with bandwidth greater than
-$b_c(v, w)$ from the virtual graph and only then compute $P_{w}(\beta , \gamma , C)$.
-The above formulation is illustrated in Figure~\ref{fig:dp1}.
+The algorithm maintains a pair of physical and virtual nodes,
+$\gamma$ and $w$ respectively.
+In each step it chooses a virtual edge $\alpha\beta$ and a physical node $v$
+that are ascendant of $\gamma$ and $w$ respectively.
+It then embeds a minimum cost $\beta\gamma$-path into $w$ 
+without violating its processing capacity,
+it also compute a $vw$-path to be used in the solution, 
+making sure the path can carry the bandwidth demand of the edge $\beta\gamma$.
+Finally it finds an optimal embedding to a $\sigma\alpha$-path into a $sv$-path 
+recursively.
+This informal description of the algorithm is illustrated in Figure~\ref{fig:dp1}.
 
@@
 \label{fig:dp1}
-The optimal embedding of a $\sigma \gamma $-path into a $sv$ path can be
+The optimal embedding of a $\sigma \gamma $-path into a $sw$-path can be
 efficiently computed by breaking the problem into the problem of embedding 
-a $\sigma \alpha $-path into a $su$-path (blue, dashed clouds) 
-and the problem of embedding a $\beta \gamma $-path into $v$ (orange, dotted) 
-where $b_d(\alpha , \beta) \leq b_c(u, v)$.
-Virtual arcs with high bandwidth demand (dashed arc) need to be removed before
-the computation of the optimal path embedding.
+a $\sigma\alpha$-path into a $sv$-path (blue, dashed clouds) 
+and the problem of embedding a $\beta\gamma$-path into $w$ (orange, dotted).
+The $vw$-path must carry $b(\alpha\beta)$ bandwidth, 
+The $\beta\gamma$-path is a minimum cost $\beta\gamma$-path 
+that can be embedded into $w$.
 }
 \end{figure}
+
+We now give a more formal description of the algorithm.
+Let $C(\sigma-\gamma , s-w)$ denote the
+minimum cost embedding of a $\sigma\gamma $-path into a $sw$-path.
+Let $\pi$ be a typological ordering 
+(we use $\pi$ to denote a typological ordering of 
+both the virtual and the physical graphs).
+Also let $C(\beta-\gamma, w)$ be the minimum cost embedding of a $\beta\gamma$-path
+into $w$, 
+and let $r_b(v, w)$ be a predicate that is true if $w$ is reachable from $v$
+using only edges with bandwidth at least $b$. 
+We claim that $C$ can be computed recursively as follow:
+\begin{align*}
+&C(\sigma-\gamma , s-w) = 
+\min_{\substack{
+\alpha\beta \in \calE,  
+v \in V:
+\\
+\pi(v) < \pi(w),
+\\
+\pi(\beta ) < \pi(\gamma ), 
+\\
+r_{b(\alpha\beta)}(v,w)
+}}
+C(\sigma-\alpha , s-v)
++
+C(\beta-\gamma, w)
+\\
+&C(\sigma-\sigma , s-v) = 0
+\\
+&C(\sigma-\alpha , s-s) = \infty
+\end{align*}
+Computing $C(\sigma-\tau , s-t)$ gives the optimal embedding. 
+It is clear that $r_b(v,w)$ can be computed efficiently by removing all the edges
+with bandwidth less than $b$ and checking connectivity.
+We now argue that $C(\beta-\gamma, w)$ can be computed efficiently as well.
+Let $P_w(\alpha-\gamma, c)$ 
+be the minimum processing required to embed a virtual, 
+$\alpha\gamma$-path into $w$ with a cost constraint $c$, 
+then $P$ can be computed recursively as follow:
+\begin{align*}
+&P_{w}(\alpha-\gamma, c) = 
+\min_{\beta\gamma  \in \calE} P_{w}(\alpha-\beta, c - c(\gamma, w))
+\\
+&P_w(\alpha-\alpha, c) = 
+\begin{cases}
+p(\alpha) & c(\alpha, w) \leq c
+\\
+\infty & \text{otherwise}
+\end{cases}
+\\
+&P(\cdot, \cdot, <0) = \infty
+\end{align*}
+To complete our argument observe that the following holds:
+$$C(\beta-\gamma, w) = \smashoperator{\min_{c : P_w(\beta-\gamma, c) \leq p(w)}}c$$

### 2017-06-23 src/fig-reduction2.tex
foo

\begin{tikzpicture}[every node/.style={default node}]
\node[draw=none] at(3, 1) {Virtual Path};

\node(alpha1) at(0,0) {$\alpha_1$};
\node(alpha2) at(2,0) {$\alpha_2$};
\node[draw=none] at(6,0) {$\cdots$};
\node(alphan) at(10,0) {$\alpha_n$};
\node(tau) at(12,0) {$\tau$};

\draw (alpha1) -- (alpha2);
\draw (alpha2) -- +(2, 0);
\draw ($(alphan) + (-2,0)$) -- (alphan);
\draw (alphan) -- (tau);

\node(v1-) at(0, -2) {$v_1^-$};
\node(v1+) at(0, -4) {$v_1^+$};
\node(v2-) at(2, -2) {$v_2^-$};
\node(v2+) at(2, -4) {$v_2^+$};

\node[draw=none] at(6,-2) {$\cdots$};
\node[draw=none] at(6,-4) {$\cdots$};

\node(vn-) at(10, -2) {$v_n^-$};
\node(vn+) at(10, -4) {$v_n^+$};
\node(t) at(12, -2) {$t$};

\draw (v1-) -- (v1+) node[label above] {$a_1$};
\draw (v1+) -- (v2-) node[label below] {$0$};
\draw (v2-) -- (v2+) node[label above] {$a_2$};
\draw (v2+) -- +(2, 2)node[label below] {$0$};

\draw ($(vn-) + (-2,-2)$) -- (vn-)node[label below] {$0$};;
\draw (vn-) -- (vn+)node[label above] {$a_n$};
\draw (vn+) -- (t)node[label below] {$0$};;

\begin{scope}[every node/.style={label above, orange}]
\draw[group, ->] (alpha1) to[bend left] node {$0$} (v1-);
\draw[group, ->] (alpha1) to[bend right] node {$a_1$} (v1+);
\draw[group, ->] (alpha2) to[bend left] node {$0$} (v2-);
\draw[group, ->] (alpha2) to[bend right] node {$a_2$} (v2+);
\draw[group, ->] (alphan) to[bend left] node {$0$} (vn-);
\draw[group, ->] (alphan) to[bend right] node {$a_n$} (vn+);

\draw[group, ->] (tau) to[bend left] node {$0$} (t);
\end{scope}

\end{tikzpicture}

### 2017-06-23 src/latency.tex
foo

--- 2017-04-26 src/latency.tex
@@
-\todo{Are we going to talk about the problem also with latency constraint ?}
+We now consider the \VPN{} problem with latency.
+Recall that in this variant of the problem we are also given a latency function
+$l : E \times \calE \to \R$, and a latency constraint $L$.
+The goal is to find a minimum cost embedding that also respect the latency
+constraint.
+
+Let $L(\sigma-\gamma, s-w, c)$ denote an embedding of a $\sigma\gamma$-path
+into a $sw$-path with the minimum possible latency that cost at most $c$.
+Let $L_{b}(\alpha\beta, v-w)$ be the minimum possible latency on a $\alpha\beta$-path
+w.r.t virtual edge $\alpha\beta$, using only edges with bandwidth capacity at least $b$,
+i.e. if $P$ is the set of edges in this path then $\forall_{e \in P}~b(e) \geq b$,
+and $\sum_{e \in P}l(\alpha\beta, e)$ is minimum.
+Observe that the later can be reduced to a shortest path problem on $G$ by removing
+edged with bandwidth less than $b$ and setting the weight of each edge $e$ to be 
+$l(\alpha\beta, e)$.
+Now $L(\sigma-\gamma, s-w, c)$ can be computed recursively as follow:
+\begin{align*}
+&L(\sigma-\gamma, s-w, c) = 
+\min_{\substack{
+\alpha\beta \in \calE,  
+v \in V:
+\\
+\pi(v) < \pi(w),
+\\
+\pi(\beta ) < \pi(\gamma ), 
+\\
+r_{b(\alpha\beta)}(v,w)
+}}
+L_{b}(\alpha\beta, v-w) + 
+L(\sigma-\alpha, s-v, c - C(\beta-\gamma, w))
+\\
+&L(\sigma-\sigma, s-v, \geq 0) = 0
+\\
+&L(\sigma-\alpha, s-s, \cdot) = \infty
+\\
+&L(\cdot, \cdot, <0) = \infty
+\end{align*}
+
+Now, to compute the optimal embedding with the additional latency constraint,
+$L$, one can simply (binary) search for the minimum value of $c$ such that
+$L(\sigma-\tau, s-t, c) \leq L$.

### 2017-06-23 src/main.tex
foo

--- 2017-06-23 src/main.tex
@@
-%\nonstopmode
+\nonstopmode
 %\documentclass[11pt]{article}
@@
 %\usepackage{lipsum}
-\usepackage{todonotes}
+%\usepackage{todonotes}
 %\usepackage{lineno}
@@
 
-\dror{reduction from partition using latency}
-
-%
+Given a partition instance $a_1, \ldots, a_n$, we construct a virtual path
+$\alpha_1, \ldots, \alpha_n, \tau$ and a physical path 
+$v_1^-, v_1^+, \ldots, v_n^-, v_n^+, t$.
+We set $p \equiv 1$, $b \equiv 1$, 
+$c(\alpha_i, v_i^-) = 0$, $c(\alpha_i, v_i^+) = a_i$, $c(\tau, t) = 0$
+and for any $v \notin \{v_i^-,v_i^+\}$ we set $c(\alpha_i, v) = \infty$.
+We also set $l(\alpha_i\alpha_{i+1}, v_i^-v_i^+) = a_i$, and set $l = 0$
+otherwise.
+Let $s = 1/2\sum_i^n a_i$
+One can verify that there is embedding with cost $s$ and latency $s$ 
+if and only if $a_1, \ldots, a_n$ can be partitioned.
 \qed
 \end{proof}
+Figure~\ref{fig:reduction2} depicts the above reduction.
+\begin{figure}[ht]
+\centering
+\scalebox{.9}{
+\input{fig-reduction2}
+}
+\caption[]{
+\label{fig:reduction2}
+A reduction from a partition instance $a_1, \ldots, a_n$.
+Each $\alpha_i$ can be placed either in $v_i^-$ or in $v_i^+$.
+In the former case this placement incure no cost but additional latency of $a_i$,
+in the later case there will be additional $a_i$ cost with zero latency.
+}
+\end{figure}
 

### 2017-06-24 src/algorithm.tex
latency

@@
 efficiently computed by breaking the problem into the problem of embedding 
-a $\sigma\alpha$-path into a $sv$-path (blue, dashed clouds) 
+a $\sigma\alpha$-path into a $sv$-path (blue, dashed rectangles) 
 and the problem of embedding a $\beta\gamma$-path into $w$ (orange, dotted).

### 2017-06-24 src/latency.tex
latency

@@
 constraint.
+
+We first describe an algorithm that, given a cost constraint $c$, 
+finds an embedding that costs at most $c$ and has the minimum possible latency.
+Once again, the algorithm maintains a pair of physical and virtual nodes,
+$\gamma$ and $w$ respectively.
+In each step it chooses a virtual edge $\alpha\beta$ and a physical node $v$
+that are ascendant of $\gamma$ and $w$ respectively.
+It then finds a $vw$-path that support the bandwidth of $\alpha\beta$ and
+has the minimum possible latency with respect to this edge.
+It also finds $\beta\gamma$-path that can be embedded into $w$ and has the 
+minimum possible cost.
+Finally it finds an embedding of a $\sigma\alpha$-path into a $sv$-path with 
+the minimum possible latency recursively.
 

### 2017-06-25 src/scaling.tex
scaling

We now show that for an arbitrary cost function, $c$,
and for any $\varepsilon > 0$ 
we can defined a scaled, rounded function $c'$ such that:
\begin{enumerate}
\item $OPT_{c'} \leq (1 + \varepsilon)OPT$, where $OPT_{c'}$ is the optimal
value w.r.t $c'$ and $OPT$ is the optimal value w.r.t $c$.
\item $\max_{\alpha, v : c'(\alpha, v) \neq \infty}c'(\alpha, v)$ is polynomial
bounded in the size of the input.
\end{enumerate}
Combining the above with the algorithms described in 
Section~\ref{sec:alg1} and \ref{sec:alg2} we have FPTAS for the \VPN{} problem
for an arbitrary cost function.

Let $\~c$ be the maximum cost incurs by embedding a single virtual node into 
a physical node in an optimal embedding, 
that is $\~c \eqdf \max_{\alpha \in \calV}c(\alpha, f_{opt}(\alpha))$.
Given $\varepsilon$ we define 
$$
c'(\alpha, v) \eqdf
\begin{cases}
\ceil{c(\alpha, v)/\mu} & c(\alpha, v) \leq \~c
\\
\infty & c(\alpha, v) > \~c
\end{cases}
$$
where 
$
\mu \eqdf \frac{\~c\varepsilon}{n}
$.
Let $s$ be an optimal placement w.r.t $c'$ 
and let $o$ be an optimal placement w.r.t $c$, 
let also $S$ and $O$ denotes their values respectively, then.
\begin{lemma}
S \leq (1 + \varepsilon)O
\end{lemma}
\begin{proof}
\begin{align*}
S = & \sum_{\alpha \in \calV}c(\alpha, s(\alpha)) \leq
\\&
\mu\sum_{\alpha \in \calV}c'(\alpha, s(\alpha)) \leq
\\&
\mu\sum_{\alpha \in \calV}c'(\alpha, o(\alpha)) \leq
\\&
\mu\sum_{\alpha \in \calV}c(\alpha, o(\alpha))/\mu + 1 \leq
\\&
\sum_{\alpha \in \calV}c(\alpha, o(\alpha)) + n\mu =
O + \~c\varepsilon \leq (1 + \varepsilon)O
\end{align*}
\end{proof}
Clearly, $\~c$, is not known in advanced, but one can "guess" its value because there are at most
$|\calV| \cdot |V|$ possible values it can get.

### 2017-06-25 src/scaling.tex
scaling

@@
 Combining the above with the algorithms described in 
-Section~\ref{sec:alg1} and \ref{sec:alg2} we have FPTAS for the \VPN{} problem
+Section~\ref{sec:alg1} and \ref{sec:alg2} we present FPTAS for the \VPN{} problem
 for an arbitrary cost function.
@@
 \end{proof}
-Clearly, $\~c$, is not known in advanced, but one can "guess" its value because there are at most
-$|\calV| \cdot |V|$ possible values it can get.
+Clearly, $\~c$, is not known in advanced, but one can "guess" 
+its value as there are at most
+$|\calV| \cdot |V|$ possible values to choose from.

### 2017-06-25 src/algorithm.tex
mv latency & scaling to alg

@@
 we present an efficient algorithm to the \VPN{} problem.
-We then argue that, using a standard scaling and rounding technique, we can use
+We then extend the algorithm to also obey a global latency constraint.
+Finally, we argue that, using a standard scaling and rounding technique, we can use
 the same computation to achieve a solution with a cost only
@@
 We are given an instance of the \VPN{} problem 
-\begin{align*}
-\calG = (\calV, \calE)		\\
-G = (V, E)		\\
-(\sigma , \tau , s, t)	\\
+$
+\calG = (\calV, \calE),
+G = (V, E),
+(\sigma , \tau , s, t),
 (p, b, c)
-\end{align*}
+$.
 The algorithm maintains a pair of physical and virtual nodes,
@@
 $$C(\beta-\gamma, w) = \smashoperator{\min_{c : P_w(\beta-\gamma, c) \leq p(w)}}c$$
+
+We now consider the \VPN{} problem with latency.
+Recall that in this variant of the problem we are also given a latency function
+$l : E \times \calE \to \R$, and a latency constraint $L$.
+The goal is to find a minimum cost embedding that also respect the latency
+constraint.
+
+We first describe an algorithm that, given a cost constraint $c$, 
+finds an embedding that costs at most $c$ and has the minimum possible latency.
+Once again, the algorithm maintains a pair of physical and virtual nodes,
+$\gamma$ and $w$ respectively.
+In each step it chooses a virtual edge $\alpha\beta$ and a physical node $v$
+that are ascendant of $\gamma$ and $w$ respectively.
+It then finds a $vw$-path that support the bandwidth of $\alpha\beta$ and
+has the minimum possible latency with respect to this edge.
+It also finds $\beta\gamma$-path that can be embedded into $w$ and has the 
+minimum possible cost.
+Finally it finds an embedding of a $\sigma\alpha$-path into a $sv$-path with 
+the minimum possible latency recursively.
+
+Let $L(\sigma-\gamma, s-w, c)$ denote an embedding of a $\sigma\gamma$-path
+into a $sw$-path with the minimum possible latency that cost at most $c$.
+Let $L_{b}(\alpha\beta, v-w)$ be the minimum possible latency on a $\alpha\beta$-path
+w.r.t virtual edge $\alpha\beta$, using only edges with bandwidth capacity at least $b$,
+i.e. if $P$ is the set of edges in this path then $\forall_{e \in P}~b(e) \geq b$,
+and $\sum_{e \in P}l(\alpha\beta, e)$ is minimum.
+Observe that the later can be reduced to a shortest path problem on $G$ by removing
+edged with bandwidth less than $b$ and setting the weight of each edge $e$ to be 
+$l(\alpha\beta, e)$.
+Now $L(\sigma-\gamma, s-w, c)$ can be computed recursively as follow:
+\begin{align*}
+&L(\sigma-\gamma, s-w, c) = 
+\min_{\substack{
+\alpha\beta \in \calE,  
+v \in V:
+\\
+\pi(v) < \pi(w),
+\\
+\pi(\beta ) < \pi(\gamma ), 
+\\
+r_{b(\alpha\beta)}(v,w)
+}}
+L_{b}(\alpha\beta, v-w) + 
+L(\sigma-\alpha, s-v, c - C(\beta-\gamma, w))
+\\
+&L(\sigma-\sigma, s-v, \geq 0) = 0
+\\
+&L(\sigma-\alpha, s-s, \cdot) = \infty
+\\
+&L(\cdot, \cdot, <0) = \infty
+\end{align*}
+
+Now, to compute the optimal embedding with the additional latency constraint,
+$L$, one can simply (binary) search for the minimum value of $c$ such that
+$L(\sigma-\tau, s-t, c) \leq L$.
+
+To conclude this section we show that for an arbitrary cost function, $c$,
+and for any $\varepsilon > 0$ 
+we can defined a scaled, rounded function $c'$ such that:
+\begin{enumerate}
+\item $OPT_{c'} \leq (1 + \varepsilon)OPT$, where $OPT_{c'}$ is the optimal
+value w.r.t $c'$ and $OPT$ is the optimal value w.r.t $c$.
+\item $\max_{\alpha, v : c'(\alpha, v) \neq \infty}c'(\alpha, v)$ is polynomial
+bounded in the size of the input.
+\end{enumerate}
+Combining the above with the algorithms described earlier 
+yields FPTAS for the \VPN{} problem for an arbitrary cost function.
+
+Let $\~c$ be the maximum cost incurs by embedding a single virtual node into 
+a physical node in an optimal embedding, 
+that is $\~c \eqdf \max_{\alpha \in \calV}c(\alpha, f_{opt}(\alpha))$.
+Given $\varepsilon$ we define 
+$$
+c'(\alpha, v) \eqdf
+\begin{cases}
+\ceil{c(\alpha, v)/\mu} & c(\alpha, v) \leq \~c
+\\
+\infty & c(\alpha, v) > \~c
+\end{cases}
+$$
+where 
+$
+\mu \eqdf \frac{\~c\varepsilon}{n}
+$.
+Let $s$ be an optimal placement w.r.t $c'$ 
+and let $o$ be an optimal placement w.r.t $c$, 
+let also $S$ and $O$ denotes their values respectively, then.
+\begin{lemma}
+S \leq (1 + \varepsilon)O
+\end{lemma}
+\begin{proof}
+\begin{align*}
+S = & \sum_{\alpha \in \calV}c(\alpha, s(\alpha)) \leq
+\\&
+\mu\sum_{\alpha \in \calV}c'(\alpha, s(\alpha)) \leq
+\\&
+\mu\sum_{\alpha \in \calV}c'(\alpha, o(\alpha)) \leq
+\\&
+\mu\sum_{\alpha \in \calV}c(\alpha, o(\alpha))/\mu + 1 \leq
+\\&
+\sum_{\alpha \in \calV}c(\alpha, o(\alpha)) + n\mu =
+O + \~c\varepsilon \leq (1 + \varepsilon)O
+\end{align*}
+\end{proof}
+Clearly, $\~c$, is not known in advanced, but one can "guess" 
+its value as there are at most
+$|\calV| \cdot |V|$ possible values to choose from.

### 2017-06-25 src/scaling.tex
mv latency & scaling to alg

@@
 Combining the above with the algorithms described in 
-Section~\ref{sec:alg1} and \ref{sec:alg2} we present FPTAS for the \VPN{} problem
+Section~\ref{sec:alg1} and \ref{sec:alg2} yields FPTAS for the \VPN{} problem
 for an arbitrary cost function.

### 2017-06-27 src/algorithm.tex
fix errors

@@
 
-Let $\~c$ be the maximum cost incurs by embedding a single virtual node into 
+Let $\hat{c}$ be the maximum cost incurs by embedding a single virtual node into 
 a physical node in an optimal embedding, 
-that is $\~c \eqdf \max_{\alpha \in \calV}c(\alpha, f_{opt}(\alpha))$.
+that is $\hat{c} \eqdf \max_{\alpha \in \calV}c(\alpha, f_{opt}(\alpha))$.
 Given $\varepsilon$ we define 
@@
 \begin{cases}
-\ceil{c(\alpha, v)/\mu} & c(\alpha, v) \leq \~c
+\ceil{c(\alpha, v)/\mu} & c(\alpha, v) \leq \hat{c}
 \\
-\infty & c(\alpha, v) > \~c
+\infty & c(\alpha, v) > \hat{c}
 \end{cases}
@@
 $
-\mu \eqdf \frac{\~c\varepsilon}{n}
+\mu \eqdf \frac{\hat{c}\varepsilon}{n}
 $.
@@
 \sum_{\alpha \in \calV}c(\alpha, o(\alpha)) + n\mu =
-O + \~c\varepsilon \leq (1 + \varepsilon)O
+O + \hat{c}\varepsilon \leq (1 + \varepsilon)O
 \end{align*}
 \end{proof}
-Clearly, $\~c$, is not known in advanced, but one can "guess" 
+Clearly, $\hat{c}$, is not known in advanced, but one can "guess" 
 its value as there are at most

### 2017-06-28 src/chain.tex
foo

@@
 \input{tikz}
+
+\renewcommand{\floatpagefraction}{0.6}
 
@@
 \newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}
+
+\def\R{\mathbb{R}}
+\def\N{\mathbb{N}}
 
@@
 \begin{abstract}
-We study the allocation problem of a \emph{service chain} in a
-software-defined network that supports network function
+We study the allocation problem of a request for a \emph{service
+chain} in a software-defined network that supports network function
 virtualization.
@@
 %
-Each pair of server and VNF are associated with a cost for placing the
-network function in the server, and given a request, the goal is to
-find a valid service chain of minimum total cost or to identify that
-a valid service chain does not exist.
+In addition, each pair of server and VNF are associated with a cost
+for placing the network function in the server.  Given a request, the
+goal is to find a valid service chain of minimum total cost that
+respects the latency constraint or to identify that such a service
+chain does not exist.
 
 We show that even the feasibility problem is NP-hard in general
-di-graphs.  Hence we first focus on directed acyclic graphs (DAGs).
-We show that the problem is still NP-hard in DAGs and present an
-FPTAS.
+graphs.  Hence we focus on directed acyclic graphs (DAGs).  We show
+that the problem is still NP-hard in DAGs even for a very simple
+network, and even if the specification consists of only one option.
 %
-Based on out PTAS, we also provide a randomized algorithm for
-instances in which the service chain passes through a bounded number
-of servers whose degree is larger than two.
-
-?????
-
-Fault tolerant placement: two service chains?
-
-FPT algorithm where the number of servers whose degree is larger than
-two is a parameter?
+On the other hand, we present an FPTAS for the case where the network
+is a DAG and the specification is also represented as a DAG.  Based on
+our FPTAS, we provide a randomized algorithm for instances in which
+the service chain passes through a bounded number of servers whose
+degree is larger than two.
 \end{abstract}
@@
 network status, required quality of service, and the identity of the
-client.  Hence, a central issue is a central agent that is able to
+client.  Hence, a focal issue is a central agent that is able to
 received reports from network components and client requests, and as a
@@
 
-In this paper we study the allocation problem of a compund request for
-a service chain in a software-defined network that supports NFV.
-Given a (physical) network that contains servers with limited
-processing power and of links with limited bandwidth, a service chain
-is a sequence of virtual network functions (VNFs) that service a
-certain flow request in the network.
-%
-The allocation of a service chain consists of routing and VNF
-placement.  That is, each VNF from the seqeunce is placed in a server
-along a path, and it is feasible if each server can handle the VNFs
-that are assigned to it, and if each link on the path can carry the
-flow that is assigned to it.
-%
-A request for service is composed of a source and a destination in the
-network, an upper bound on the total latency, and a specification of
-all service chains that are considered valid for this request.
-%
-Each pair of server and VNF are associated with a cost for placing the
-network function in the server.  This cost measures compatibility of a
-VNF to a server (infinite costs means ``incompatible'').  Given a
-request, the goal is to find a valid service chain of minimum total
-cost or to identify that a valid service chain does not exist.
-
-\dror{Explain one shot approach}
+%%%%%
 
@@
 %
-It is important to note that in this problem does not consider
+It is important to note that in this problem the authors do not consider
 routing, and also it assumes unordered VNF subsets.
@@
 Even, Medina, and Patt-Shamir~\cite{EMP16} studied online path
-computation and VNF placement.  They considered service chain requests
-that arrive in an online manner.  Each request is a a flow with a
-high-level specification of routing and VNF requirements.  Each VNF
-can be performed by a specified subset of servers in the system.  Upon
+computation and VNF placement.  They considered compound requests that
+arrive in an online manner.  Each request is a flow with a
+specification of routing and VNF requirements.  The specification is
+represented by a DAG whose vertices are VNFs.  Each VNF can be
+performed by a specified subset of servers in the system.  Upon
 arrival of a request, the algorithm either rejects the request or
-accepts it and with a specific routing and VNF assignment, under given
+accepts it with a specific routing and VNF assignment, under given
 server capacity constraints.  Each request has a benefit that is
 gained if it is accepted, and the goal is to maximize the total
-benefit.
+benefit gained by accepted requests.
 %
@@
 performance guarantee holds for the case where the processing of any
-processing request in any possible service chain is never more than
+request in any possible service chain is never more than
 $O(1/(k \log (nk)))$ fraction of the capacity of any network
 component.
+%
+Even, Rost, and Schmid~\cite{ERS16} presented a randomized
+approximation algorithm for the same problem that computes
+$(1-\eps)$-approximate placements if the processing of any processing
+request in any possible service chain is never more than
+$O(\eps^2/\log n)$ fraction of the capacity of any network component.
 
-Even, Rost, and Schmid~\cite{ERS16}
-
-\dror{finish}
+\dror{add references - see [ERS16]}
 
@@
 %
-We show that even the feasibility problem is NP-hard in general
-di-graphs.  Hence we first focus on directed acyclic graphs (DAGs).
-We show that the problem is still NP-hard in DAGs and present an
-FPTAS.
+In this paper we study the allocation problem of a compound flow
+request for a service chain in a software-defined network that
+supports NFV, where the goal is to find an optimal placement with
+respect to the current available resources from the point of view of
+the network (i.e., the ISP).
 %
-Based on out PTAS, we also provide a randomized algorithm for
-instances in which the service chain passes through a bounded number
-of servers whose degree is larger than two.
+More specifically, we consider the case where the network already
+contains previous resource allocations.  Therefore, we are given a
+(physical) network that contains servers with limited (residual)
+processing power and of links with limited (residual) bandwidth.
+%
+A request for service is composed of a source and a destination in the
+network, an upper bound on the total latency, and a specification of
+all service chains that are considered valid for this request.  As
+in~\cite{EMP16}, the specification is represented by a DAG whose
+vertices are VNFs.
+%
+The allocation of a service chain consists of routing and VNF
+placement.  That is, each VNF from the sequence is placed in a server
+along a path, and it is feasible if each server can handle the VNFs
+that are assigned to it, and if each link on the path can carry the
+flow that is assigned to it.  Moreover each link causes a delay, and
+the service chain placement should also comply with a bound on the
+total latency.
+%
+Each pair of server and VNF are associated with a cost for placing the
+network function in the server.  This cost measures compatibility of a
+VNF to a server (e.g., infinite costs means ``incompatible'').  Given
+a request, the goal is to find a feasible service chain of minimum
+total cost or to identify that a valid service chain does not exist.
 
-?????
-
-\bigskip
+We show that the feasibility problem is NP-hard in general graphs
+using a reduction from \textsc{Hamiltonian Path}.  Hence we focus on
+directed acyclic graphs (DAGs).  We show that the problem is still
+NP-hard in DAGs even for a very simple network, and even if the
+specification consists of only one option.  Both reductions are from
+the \textsc{Partition} problem.
+%
+On the positive side, we present an FPTAS for the case where the
+network is a DAG.  Based on our FPTAS, we provide a randomized
+algorithm for instances in which the service chain passes through a
+bounded number of servers whose degree is larger than two.
 
@@
   has a non-negative processing capacity $p(v)$, and each directed
-  edge $e \in A$ has a non-negative bandwidth cap $b(e)$.
+  edge $e \in E$ has a non-negative bandwidth cap $b(e)$.
 
@@
   The DAG $\calG$ has a source node $\sigma \in \calV$ and a
-  destination $\tau \in \calV$ Each node $\alpha \in \calV$ represent
+  destination $\tau \in \calV$. Each node $\alpha \in \calV$ represent
   a VNF that has a processing demand $p(\alpha)$.  Without loss of
@@
 \item[Virtual path:] A path from $\sigma$ to $\tau$ in $\calG$, namely
-  a sequence of vertices $\alpha_0,\ldots,\alpha_\ell$, where
-  $\alpha_0 = \sigma$, $\alpha_\ell = \tau$, and
+  a sequence of vertices $\alpha_0,\ldots,\alpha_q$, where
+  $\alpha_0 = \sigma$, $\alpha_q = \tau$, and
   $(\alpha_j,\alpha_{j+1}) \in \calE$, for every $j \in
-  \set{0,\ldots,\ell-1}$.
+  \set{0,\ldots,q-1}$.
 
@@
   physical path.  Formally, a placement is a function $f:
-  \set{\alpha_0,\ldots,\alpha_\ell} \to \set{v_0,\ldots,v_k}$
+  \set{\alpha_0,\ldots,\alpha_q} \to \set{v_0,\ldots,v_k}$
   such that
@@
 We also consider an extended version of \scp in which each physical
-link causes a delay and there is an upper bound $T$ on the total
+link causes a delay and there is an upper bound $L$ on the total
 delay.  More formally, each pair of a virtual edge $\eps$ and physical
-edge $e$ is associated with a latency $t(\eps,e)$.
+edge $e$ is associated with a latency $\ell(\eps,e)$.
 %
-Given a placement $f: \set{\alpha_0,\ldots,\alpha_\ell} \to
+Given a placement $f: \set{\alpha_0,\ldots,\alpha_q} \to
 \set{v_0,\ldots,v_k}$, the total latency of the solution is given by
 \[
-T(f) = \sum_j \sum_{e \in \bar{f}(\eps)} t(\eps,e)
+L(f) = \sum_j \sum_{e \in \bar{f}(\eps)} \ell(\eps,e)
 ~.
 \]
-In this case there is an additional constraint that $T(f) \leq T$.
+In this case there is an additional constraint that $L(f) \leq L$.
 
@@
 Given a virtual DAG $\calG$, we assume the existence of a topological
-sorting of the vertices and write $\alpha \prec_v \beta$ if $\alpha$
+sorting of the vertices and write $\alpha \prec \beta$ if $\alpha$
 precedes $\beta$ in this ordering.  If the physical network is a DAG,
-then we make a similar assumption and write $v \prec_p u$ if $v$
+then we make a similar assumption and write $v \prec u$ if $v$
 precedes $u$ in this ordering.
@@
 
-\section{Hardness}
+\section{Hardness Results}
 
-In this section we present two hardness results.  First, we show that
-even the feasibility question of \scp is NP-hard, and therefore no
-approximation algorithm exists for \scp.  In addition, we show that
+In this section we present three hardness results.  First, we show
+that even the feasibility question of \scp is NP-hard, and therefore
+no approximation algorithm exists for \scp.  In addition, we show that
 \scp is NP-hard even if $\abs{V \setminus \set{s,t}} = 1$.  We also
@@
 
-We show that finding a feasible solution is NP-hard.
+We start by showing that even finding a feasible solution is NP-hard.
 
@@
 
-Next, we show that \scp is NP-hard even if the physical network is a
-DAG.
+Next, we show that \scp is NP-hard even if the physical network is
+very simple.
 
 \begin{theorem}
+\label{thm:simple}
 \scp is NP-hard, even if $\abs{V \setminus \set{s,t}} = 1$.
@@
 \begin{proof}
-The prove the theorem using a reduction from \textsc{Partition}.
-Given a \textsc{Partition} instance $\set{a_1, \ldots, a_n}$ we
+We prove the theorem using a reduction from \textsc{Partition}.
+Given a \textsc{Partition} instance $a = \set{a_1, \ldots, a_n}$ we
 construct an \scp instance as follows.
@@
 there are two edges $(s,v)$ and $(v,t)$.  The capacity of $v$ is $p(v)
-= \half \sum_i a_i$.  Edge capacities are zero.
+= \half \sum_i a_i$.  Edge bandwidth are zero.
 %
@@
 \]
-The DAG is shown in Figure~\ref{fig:dag}.
+The DAG is shown in Figure~\ref{fig:simple}.
 %
@@
 
-\begin{figure}
+\begin{figure}[t]
 \centering
 \input{fig-reduction}
-\caption{???}
-\label{fig:dag}
+\caption{The specification defined in the proof of Theorem~\ref{thm:simple}.}
+\label{fig:simple}
 \end{figure}
 
-\dror{Figure 2: source and destination should be fixed}
+Next, we show that \scp is NP-hard even if both the physical network
+and the VNF specification are paths.
 
@@
 \begin{proof}
+The prove the theorem using a reduction from \textsc{Partition}.
+Given a \textsc{Partition} instance $\set{a_1, \ldots, a_n}$, we
+construct a virtual path $\sigma, \alpha_1, \ldots, \alpha_n, \tau$
+and a physical path $s, v_1^-, v_1^+, \ldots, v_n^-, v_n^+, t$.  We
+set $p(v) = 1$, for every node $v \neq s,t$, and $p(\alpha_i) = 1$,
+for every $i$.  In addition, we set $b(e) = 1$, for every edge $e \in
+E$, and $b(\eps) = 1$, for every edge $\eps \in \calE$.
+%
+As for the costs, we define $c(\alpha_i, v_i^-) = 0$, $c(\alpha_i,
+v_i^+) = a_i$, and for any $v \notin \{v_i^-,v_i^+\}$ we set
+$c(\alpha_i, v) = \infty$.  We also define $\ell((\alpha_i,\alpha_{i+1}),
+(v_i^-,v_i^+)) = a_i$, and set $\ell(\eps,e) = 0$, otherwise.  Finally,
+we set $L = \half \sum_i^n a_i$.
+%
+Figure~\ref{fig:reduction2} depicts the above reduction.
 
-\dror{reduction from partition using latency}
-
+One can easily verify that $a_i$ is either counted in the latency of in the cost.
+Hence, 
+$\set{a_1, \ldots,
+a_n} \in \textsc{Partition}$ if and only if there is a placement with
+cost $\half \sum_i^n a_i$.
 %
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Algorithm}
+\begin{figure}[t]
+\centering
+\scalebox{.9}{
+\input{fig-reduction2}
+}
+\caption[]{
+\label{fig:reduction2}
+A reduction from a partition instance $a_1, \ldots, a_n$.
+The cost function enforces each $\alpha_i$ to be placed either 
+in $v_i^-$ or in $v_i^+$.
+In the former case this placement incure no cost but additional latency of $a_i$,
+in the later case there will be additional $a_i$ cost with zero latency.
+}
+\end{figure}
 
@@
 
-\section{Latency}
+\section{Algorithms}
+\label{sec:algorithms}
+
+%%%%%
+
+\subsection{???}
+
+In this section, 
+assuming costs are integral and polynomial bounded in the input length,
+we present an efficient algorithm to \scp{}.
+We then extend the algorithm to also obey a global latency constraint.
+Finally we argue that, using a standard scaling and rounding technique, we can use
+the same computation to achieve a solution with a cost only
+$1 + \varepsilon$ times greater that of the optimal solution, for any
+$\varepsilon > 0$, i.e. an FPTAS, for an arbitrary cost function.
+These are recursive algorithms that can be efficiently implemented using
+dynamic programming.
+
+We are given an instance of the \scp{} problem 
+$
+\calG = (\calV, \calE),
+G = (V, E),
+(\sigma , \tau , s, t),
+(p, b, c)
+$.
+The algorithm maintains a pair of physical and virtual nodes,
+$\gamma$ and $w$ respectively.
+In each step it chooses a virtual edge $\alpha\beta$ and a physical node $v$
+that are ascendant of $\gamma$ and $w$ respectively.
+It then embeds a minimum cost $\beta\gamma$-path into $w$ 
+without violating its processing capacity,
+it also compute a $vw$-path to be used in the solution, 
+making sure the path can carry the bandwidth demand of the edge $\beta\gamma$.
+Finally it finds an optimal embedding to a $\sigma\alpha$-path into a $sv$-path 
+recursively.
+This informal description of the algorithm is illustrated in Figure~\ref{fig:dp1}.
+
+\begin{figure}[t]
+\centering
+\input{fig-dp2}
+\caption[]{
+\label{fig:dp1}
+The optimal embedding of a $\sigma \gamma $-path into a $sw$-path can be
+efficiently computed by breaking the problem into the problem of embedding 
+a $\sigma\alpha$-path into a $sv$-path (blue, dashed rectangles) 
+and the problem of embedding a $\beta\gamma$-path into $w$ (orange, dotted).
+The $vw$-path must carry $b(\alpha\beta)$ bandwidth, 
+The $\beta\gamma$-path is a minimum cost $\beta\gamma$-path 
+that can be embedded into $w$.
+}
+\end{figure}
+
+We now give a more formal description of the algorithm.
+Let $C(\sigma-\gamma , s-w)$ denote the
+minimum cost embedding of a $\sigma\gamma $-path into a $sw$-path.
+Also let $C(\beta-\gamma, w)$ be the minimum cost
+embedding of a $\beta\gamma$-path into $w$, 
+and let $r_b(v, w)$ be a predicate that is true if $w$ is reachable from $v$
+using only edges with bandwidth at least $b$. 
+We claim that $C$ can be computed recursively as follow:
+\begin{align*}
+&C(\sigma-\gamma , s-w) = 
+\min_{\substack{
+\alpha\beta \in \calE,  
+v \in V:
+\\
+v \prec w,
+\\
+\beta \prec \gamma, 
+\\
+r_{b(\alpha\beta)}(v,w)
+}}
+C(\sigma-\alpha , s-v)
++
+C(\beta-\gamma, w)
+\\
+&C(\sigma-\sigma , s-v) = 0
+\\
+&C(\sigma-\alpha , s-s) = \infty
+\end{align*}
+Computing $C(\sigma-\tau , s-t)$ gives the optimal embedding. 
+It is clear that $r_b(v,w)$ can be computed efficiently by removing all the edges
+with bandwidth less than $b$ and checking connectivity.
+We now argue that $C(\beta-\gamma, w)$ can be computed efficiently as well.
+Let $P_w(\alpha-\gamma, c)$ 
+be the minimum processing required to embed a virtual, 
+$\alpha\gamma$-path into $w$ with a cost constraint $c$, 
+then $P$ can be computed recursively as follow:
+\begin{align*}
+&P_{w}(\alpha-\gamma, c) = 
+\min_{\beta\gamma  \in \calE} P_{w}(\alpha-\beta, c - c(\gamma, w))
+\\
+&P_w(\alpha-\alpha, c) = 
+\begin{cases}
+p(\alpha) & c(\alpha, w) \leq c
+\\
+\infty & \text{otherwise}
+\end{cases}
+\\
+&P(\cdot, \cdot, <0) = \infty
+\end{align*}
+To complete our argument observe that the following holds:
+$$C(\beta-\gamma, w) = \smashoperator{\min_{c : P_w(\beta-\gamma, c) \leq p(w)}}c$$
+
+%%%%%
+
+\subsection{???}
+
+We now consider the \scp{} problem with latency.
+Recall that in this variant of the problem we are also given a latency function
+$l : E \times \calE \to \R$, and a latency constraint $T$.
+The goal is to find a minimum cost embedding that also respect the latency
+constraint.
+
+We first describe an algorithm that, given a cost constraint $c$, 
+finds an embedding that costs at most $c$ and has the minimum possible latency.
+Once again, the algorithm maintains a pair of physical and virtual nodes,
+$\gamma$ and $w$ respectively.
+In each step it chooses a virtual edge $\alpha\beta$ and a physical node $v$
+that are ascendant of $\gamma$ and $w$ respectively.
+It then finds a $vw$-path that support the bandwidth of $\alpha\beta$ and
+has the minimum possible latency with respect to this edge.
+It also finds $\beta\gamma$-path that can be embedded into $w$ and has the 
+minimum possible cost.
+Finally it finds an embedding of a $\sigma\alpha$-path into a $sv$-path with 
+the minimum possible latency recursively.
+
+Let $L(\sigma-\gamma, s-w, c)$ denote an embedding of a $\sigma\gamma$-path
+into a $sw$-path with the minimum possible latency that cost at most $c$.
+Let $L(\alpha\beta, v-w)$ be the minimum possible latency on a $\alpha\beta$-path
+w.r.t virtual edge $\alpha\beta$, using only edges with bandwidth capacity at
+least $b(\alpha\beta)$, i.e. $\forall_{e \in \bar{f}(\alpha\beta)}~b(e) \geq
+b(\alpha\beta)$, and $\sum_{e \in \bar{f}(\alpha\beta)}l(\alpha\beta, e)$ is
+minimum.
+Observe that the later can be reduced to a shortest path problem on $G$ by removing
+edged with bandwidth less than $b$ and setting the weight of each edge $e$ to be 
+$l(\alpha\beta, e)$.
+Now $L(\sigma-\gamma, s-w, c)$ can be computed recursively as follow:
+\begin{align*}
+&L(\sigma-\gamma, s-w, c) = 
+\min_{\substack{
+\alpha\beta \in \calE,  
+v \in V:
+\\
+v \prec w,
+\\
+\beta \prec \gamma, 
+\\
+r_{b(\alpha\beta)}(v,w)
+}}
+L(\alpha\beta, v-w) + 
+L(\sigma-\alpha, s-v, c - C(\beta-\gamma, w))
+\\
+&L(\sigma-\sigma, s-v, \geq 0) = 0
+\\
+&L(\sigma-\alpha, s-s, \cdot) = \infty
+\\
+&L(\cdot, \cdot, <0) = \infty
+\end{align*}
+
+Now, to compute the optimal embedding with the additional latency constraint,
+$T$, one can simply (binary) search for the minimum value of $c$ such that
+$L(\sigma-\tau, s-t, c) \leq T$.
+
+%%%%%
+
+\subsection{???}
+
+To conclude this section we show that for an arbitrary cost function, $c$,
+and for any $\varepsilon > 0$ 
+we can defined a scaled, rounded function $c'$ such that:
+\begin{enumerate}
+\item $OPT_{c'} \leq (1 + \varepsilon)OPT$, where $OPT_{c'}$ is the optimal
+value w.r.t $c'$ and $OPT$ is the optimal value w.r.t $c$.
+\item $\max_{\alpha, v : c'(\alpha, v) \neq \infty}c'(\alpha, v)$ is polynomial
+bounded in the size of the input.
+\end{enumerate}
+Note that combining the above claim with the algorithms described
+earlier yields FPTAS for the \scp{} problem for an arbitrary cost function.
+
+Let $\hat{c}$ be the maximum cost incurs by embedding a single virtual node into 
+a physical node in an optimal embedding, 
+that is $\hat{c} \eqdf \max_{\alpha \in \calV}c(\alpha, f_{opt}(\alpha))$.
+Given $\varepsilon$ we define 
+$$
+c'(\alpha, v) \eqdf
+\begin{cases}
+\ceil{c(\alpha, v)/\mu} & c(\alpha, v) \leq \hat{c}
+\\
+\infty & c(\alpha, v) > \hat{c}
+\end{cases}
+$$
+where 
+$
+\mu \eqdf \frac{\hat{c}\varepsilon}{n}
+$.
+Let $s$ be an optimal placement w.r.t $c'$ 
+and let $o$ be an optimal placement w.r.t $c$, 
+let also $S$ and $O$ denotes their values respectively, then.
+\begin{lemma}
+S \leq (1 + \varepsilon)O
+\end{lemma}
+\begin{proof}
+\begin{align*}
+S = & \sum_{\alpha \in \calV}c(\alpha, s(\alpha)) \leq
+\\&
+\mu\sum_{\alpha \in \calV}c'(\alpha, s(\alpha)) \leq
+\\&
+\mu\sum_{\alpha \in \calV}c'(\alpha, o(\alpha)) \leq
+\\&
+\mu\sum_{\alpha \in \calV}c(\alpha, o(\alpha))/\mu + 1 \leq
+\\&
+\sum_{\alpha \in \calV}c(\alpha, o(\alpha)) + n\mu =
+O + \hat{c}\varepsilon \leq (1 + \varepsilon)O
+\end{align*}
+\end{proof}
+Clearly, $\hat{c}$, is not known in advanced, but one can "guess" 
+its value as there are at most
+$|\calV| \cdot |V|$ possible values to choose from.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{General Graphs}
+\label{sec:general}
+
+In this section we consider the problem when the physical network is undirected.
+Once again we seek to embed a virtual $\sigma\tau$-path 
+into a simple physical $st$-path.
+Note, that we still assume that the virtual graph is a DAG. 
+We extend our algorithm to work for this case as well.
+
+Recall that the problem on general graphs cannot be approximate at all,
+thus we assume in this section that there exists an optimal embedding that uses
+a physical path with at most $k$ \emph{heavy} vertices, thus are vertices with
+degree greater than two (we do not assume anything about the physical network).
+The modified algorithm includes a preprocessing stage that applies
+random orientation to the physical network, the entire algorithm runs in
+$O(t(n)k!)$, where $t(n)$ is the time it takes to compute the optimal embedding when the
+physical network is a DAG, and finds the optimal embedding with high
+probability.
+
+The preprocessing stage is as follow:
+let $V_h$ be the set of heavy vertices, and let 
+$\pi:V_h \to [|V_h|]$ be a random permutation.
+For every \emph{light path} $w_1, \ldots, w_l$, that is, $w_1, w_l \in
+V_h$, $\pi(w_1) < \pi(w_l)$, and $\forall_{1 < i < l}, w_i \notin V_h$,
+we direct the edges from $w_1$ to $w_l$ i.e. $w_i \to w_{i+1}$ for every $1
+\leq i \leq l - 1$.
+One can verifies that this can be done efficiently and that when this process
+terminates $G$ is a DAG, Figure~\ref{fig:orientation} depicts the preprocessing
+stage.
+
+\begin{figure}[ht]
+\input{fig-orientation}
+\caption{
+\label{fig:orientation}
+The preprocessing stage: on the left is the undirected physical network,
+Only the heavy nodes are drawn.
+The numbers represent the permutation and the blue, dashed path represents a
+path of an optimal embedding.
+On the right side is the orientated physical network, 
+note that it is enough that the internal ordering of the nodes on the blue,
+dashed path is "correct" to ensure that the algorithm finds the optimal
+embedding. }
+\end{figure}
+
+Completing the orientation, we use our previous algorithm to find an optimal
+embedding.
+We repeat this process, each time with a new independent random permutation, and
+keep the best embedding so far.
+Note that if there is an optimal embedding using a physical path with at most
+$k$ heavy vertices then it is sufficient that those vertices are ordered
+"correctly" w.r.t $\pi$, regardless of the order $\pi$ applies to all other
+heavy vertices, to ensure that the algorithm finds the optimal embedding.
+We claim that with high probability, 
+after $O(k!)$ iterations, the above algorithm finds the optimal embedding, formally:
+
+\begin{theorem}
+With probability at least $1 - e^{-x}$ the algorithm finds the optimal embedding
+after $xk!$ iterations.
+\end{theorem}
+
+\begin{proof}
+Consider an optimal embedding and the order it induces on the heavy vertices in
+the physical path (at most $k$ such vertices), if the random permutation orders
+the heavy vertices correctly, i.e. in that order, we are guaranteed to find the
+optimal embedding.
+This happens with probability $1/k!$ and the probability to miss the optimal
+embedding after $xk!$ iterations is $1 - (1 - 1/k!)^{xk!} \leq 1 - e^{-x}$.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Extensions}
+
+Global constraint = security, fault tolerance.
+
+Costs by sets of VNFS
+
+Fault tolerant placement: two service chains?
+
+FPT algorithm where the number of servers whose degree is larger than
+two is a parameter?
 

### 2017-10-29 src/chain.tex
dror

--- 2017-06-21 src/chain.tex
@@
 \usepackage{paralist}
+\usepackage{stmaryrd}
 
@@
 
-\usepackage[final]{microtype}
+%\usepackage[final]{microtype}
 \usepackage[final]{hyperref}
@@
 \newcommand{\calV}{\mathcal{V}}
+
+\newcommand{\opt}{\textsc{opt}\xspace}
+\newcommand{\cost}{\textsc{cost}\xspace}
+\newcommand{\process}{\textsc{prc}\xspace}
+\newcommand{\latency}{\textsc{lat}\xspace}
 
@@
 \begin{abstract}
-We study the allocation problem of a \emph{service chain} in a
-software-defined network that supports network function
-virtualization.
+We study the allocation problem of a compound request for a
+\emph{service chain} in a software defined network that supports
+network function virtualization.
 %
@@
 The allocation of a service chain consists of routing and VNF
-placement.  That is, each VNF from the seqeunce is placed in a server
-along a path, and it is feasible if each server can handle the VNFs
-that are assigned to it, and if each link on the path can carry the
-flow that is assigned to it.
+placement, namely each VNF from the sequence is placed in a server
+along a path.  It is feasible if each server can handle the VNFs that
+are assigned to it, and if each link on the path can carry the flow
+that is assigned to it.
 %
 A request for service is composed of a source and a destination in the
-network, an upper bound on the total latency, and a specification of
-all service chains that are considered valid for this request.
+network, an upper bound on the total latency, and a specification in
+the form of a directed acyclic graph (DAG) of VNFs that provides all
+service chains that are considered valid for this request.
 %
-Each pair of server and VNF are associated with a cost for placing the
-network function in the server, and given a request, the goal is to
-find a valid service chain of minimum total cost or to identify that
-a valid service chain does not exist.
+In addition, each pair of server and VNF is associated with a cost for
+placing the VNF in the server.  Given a request, the goal is to find a
+valid service chain of minimum total cost that respects the latency
+constraint or to identify that such a service chain does not exist.
 
 We show that even the feasibility problem is NP-hard in general
-di-graphs.  Hence we first focus on directed acyclic graphs (DAGs).
-We show that the problem is still NP-hard in DAGs and present an
-FPTAS.
+graphs.  Hence we focus on DAGs.  We show that the problem is still
+NP-hard in DAGs even for a very simple network, and even if the VNF
+specification consists of only one option (i.e., the virtual DAG is a
+path).
 %
-Based on out PTAS, we also provide a randomized algorithm for
-instances in which the service chain passes through a bounded number
-of servers whose degree is larger than two.
+On the other hand, we present an FPTAS for the case where the network
+is a DAG.  In addition, based on our FPTAS, we provide a randomized
+algorithm for instances in which the service chain passes through a
+bounded number of vertices whose degree is larger than two.
+\end{abstract}
 
-?????
-
-Fault tolerant placement: two service chains?
-
-FPT algorithm where the number of servers whose degree is larger than
-two is a parameter?
-\end{abstract}
+% Keywords:
+% approximation algorithms,
+% randomized algorithms,
+% network function virtualization,
+% resource allocation,
+% service chaining,
+% software defined network,
+%
 
@@
 %
-Current developments aim to improve the utilization of network
+Current developments that aim to improve the utilization of network
 resources include the detachment of network applications from network
@@
 
-A complimentary approach is Network Function Virtualization
+A complementary approach is Network Function Virtualization
 (NFV)~\cite{NFV12}.  Instead of relying on special purpose machines,
@@
 %
+In this paper we consider an SDN network that employs
+NVF~\cite{SDN-NFV15}.  Such networks attracted a lot of attention in
+the networking community, especially from a systems point of view
+(see, e.g.,~\cite{GVPGKDA14,HVSBFTF15}).  Several papers also consider
+the algorithmic aspects of such networks but mainly present heuristics
+(see, e.g,~\cite{SBMPKSF14}).  For more details see~\cite{ERS16} and
+references therein.
 
@@
 the input is an undirected graph with a metric distance function on
-the edges.  clients are located in various nodes, and each client is
+the edges.  Clients are located in various nodes, and each client is
 interested in a subset of VNFs.  For each node $v$ and VNF $\alpha$,
@@
 on $v$ for placing a copy of $\alpha$.  Furthermore, each node has a
-limited capacity.  Also, each copy of a VNF can handle a limited
-amount of clients A solution is the assignment of each client to a
-subset of nodes, each corresponding to one of its required VNFs.  The
-cost of a solution is the total setup costs plus the sum of distances
-between the clients and the node from which they get service.
+limited capacity, and each copy of a VNF can handle a limited amount
+of clients.  A solution is the assignment of each client to a subset
+of nodes, each corresponding to one of its required VNFs.  The cost of
+a solution is the total setup costs plus the sum of distances between
+the clients and the node from which they get service.
 %
@@
 %
-It is important to note that in this problem does not consider
-routing, and also it assumes unordered VNF subsets.
+It is important to note that in this problem routing is not considered
+and it is assumed that VNF subsets can be executed in any order.
+
+Lukovszki and Schmid~\cite{LukovszkiSchmid15} studied the problem of
+admission control and placement of service chains, where each chain is
+associated with a source-destination pair and is supposed to be routed
+via an ordered sequence of $\ell$ VNFs.  The VNFs may have multiple
+instantiations, but each node has a limited capacity that bounds the
+number of requests it may service.
+%
+They presented an $O(\log \ell)$-competitive algorithm for the problem
+of maximizing the number of serviced chains, assuming that capacities
+are $\Omega(\log \ell)$.
+%at least logarithmic in $\ell$.
+It is also shown that this ratio is asymptotically optimal even for
+randomized online algorithms.  APX-hardness results for the offline
+version of the problem were also presented.
+%
+Rost and Schmid~\cite{RostSchmid16} considered variant of this
+problem, where each node can host a subset of the VNFs.  In addition,
+each VNF has a demand and each VNF-node pair has a capacity, and in a
+feasible solution the total demand for each pair is bounded by the
+capacity.  They considered two goals: maximum profit and minimum
+resource cost and gave bicriteria approximation algorithms which are
+based on LP-rounding for several special cases.
 
 Even, Medina, and Patt-Shamir~\cite{EMP16} studied online path
-computation and VNF placement.  They considered service chain requests
-that arrive in an online manner.  Each request is a a flow with a
-high-level specification of routing and VNF requirements.  Each VNF
-can be performed by a specified subset of servers in the system.  Upon
+computation and VNF placement.  They considered compound requests that
+arrive in an online manner.  Each request is a flow with a
+specification of routing and VNF requirements which is represented by
+a directed acyclic graph (DAG) whose vertices are VNFs.  Each VNF can
+be performed by a specified subset of servers in the system.  Upon
 arrival of a request, the algorithm either rejects the request or
-accepts it and with a specific routing and VNF assignment, under given
+accepts it with a specific routing and VNF assignment, under given
 server capacity constraints.  Each request has a benefit that is
 gained if it is accepted, and the goal is to maximize the total
-benefit.
+benefit gained by accepted requests.
 %
@@
 a third response, which is refer to as “stand by”, whose competitive
-ratio is $O(\log (knb_{\max})$, where $n$ is the number of nodes,
+ratio is $O(\log (knb_{\max}))$, where $n$ is the number of nodes,
 $b_{\max}$ is an upper bound on a request benefit per time unit, and
@@
 performance guarantee holds for the case where the processing of any
-processing request in any possible service chain is never more than
+request in any possible service chain is never more than
 $O(1/(k \log (nk)))$ fraction of the capacity of any network
 component.
+%
+Even, Rost, and Schmid~\cite{ERS16} presented a randomized
+approximation algorithm for the same problem that computes
+$(1-\eps)$-approximate placements if the demand of any processing
+request in any possible service chain is never more than an
+$O(\eps^2/\log n)$ fraction of the capacity of any network component.
 
-Even, Rost, and Schmid~\cite{ERS16}
-
-\dror{finish}
+%%%%%
 
@@
 %
-We show that even the feasibility problem is NP-hard in general
-di-graphs.  Hence we first focus on directed acyclic graphs (DAGs).
-We show that the problem is still NP-hard in DAGs and present an
-FPTAS.
+We study the allocation problem of a compound flow request for a
+service chain in a software-defined network that supports NFV, where
+the goal is to find an optimal placement with respect to the current
+available resources from the point of view of the network (i.e., the
+ISP).
 %
-Based on out PTAS, we also provide a randomized algorithm for
-instances in which the service chain passes through a bounded number
-of servers whose degree is larger than two.
+More specifically, we consider the case where the network already
+contains previous resource allocations.  Therefore, we are given a
+(physical) network that contains servers with limited (residual)
+processing power and of links with limited (residual) bandwidth.
+%
+A request for service is composed of a source and a destination in the
+network, an upper bound on the total latency, and a specification of
+all service chains that are considered valid for this request.  As
+in~\cite{EMP16}, the specification is represented by a DAG whose
+vertices are VNFs.
+%
+The allocation of a service chain consists of routing and VNF
+placement.  That is, each VNF from the sequence is placed in a server
+along a path, and it is feasible if each server can handle the VNFs
+that are assigned to it, and if each link on the path can carry the
+flow that is assigned to it.  Moreover each link causes a delay, and
+the service chain placement should also comply with a global bound on
+the total latency.
+%
+Each pair of server and VNF is associated with a cost for placing the
+network function in the server.  This cost measures compatibility of a
+VNF to a server (e.g., infinite costs means ``incompatible'').  Given
+a request, the goal is to find a feasible service chain of minimum
+total cost or to identify that a valid service chain does not exist.
 
-?????
-
-\bigskip
+We show that even feasibility is NP-hard in general networks using a
+reduction from \textsc{Hamiltonian Path}.
+%Hence we focus on DAGs.
+We show that the problem is still NP-hard if the network is a DAG even
+for a very simple network, and even if the specification consists of a
+single option.  Both reductions are from \textsc{Partition}.
+%
+On the positive side, we present an FPTAS for the case where the
+network is a DAG which is based on a non-trivial dynamic programming
+algorithm.
+%
+Based on our FPTAS, we provide a randomized algorithm for general
+networks in which there is an optimal placement whose physical path
+consists of at most $k$ vertices whose degree is larger than $2$.  For
+example, this can be assumed if all simple paths from $s$ to $t$
+contain at most $k$ such vertices.  The algorithm computes a
+$(1+\eps)$-approximate placement with probability $(1-e^{-1})$ using
+$k!$ invocation of the FPTAS.
 
@@
 
-\paragraph*{\bf Model.}
+\paragraph*{Model.}
 %
@@
 %
-  The physical network is a digraph $G = (V,E)$.  Each node $v \in V$
+  The physical network is a graph $G = (V,E)$.  Each node $v \in V$
   has a non-negative processing capacity $p(v)$, and each directed
-  edge $e \in A$ has a non-negative bandwidth cap $b(e)$.
+  edge $e \in E$ has a non-negative bandwidth capacity $b(e)$.
 
@@
 \item[Virtual path:] A path from $\sigma$ to $\tau$ in $\calG$, namely
-  a sequence of vertices $\alpha_0,\ldots,\alpha_\ell$, where
-  $\alpha_0 = \sigma$, $\alpha_\ell = \tau$, and
+  a sequence of vertices $\alpha_0,\ldots,\alpha_q$, where
+  $\alpha_0 = \sigma$, $\alpha_q = \tau$, and
   $(\alpha_j,\alpha_{j+1}) \in \calE$, for every $j \in
-  \set{0,\ldots,\ell-1}$.
+  \set{0,\ldots,q-1}$.
 
 \item[Physical path:] A simple path from $s$ to $t$ in $G$, namely a
-  sequence of node $v_0,\ldots,v_k$, where $v_0 = s$, $v_k = t$, and
+  sequence of nodes $v_0,\ldots,v_k$, where $v_0 = s$, $v_k = t$, and
   $(v_i,v_{i+1}) \in E$, for every $i \in \set{0,\ldots,k-1}$.
 
-\item[Placement:] A function $f$ that maps the virtual path to the
+\item[Placement:] A function $f$ that maps a virtual path to a simple
   physical path.  Formally, a placement is a function $f:
-  \set{\alpha_0,\ldots,\alpha_\ell} \to \set{v_0,\ldots,v_k}$
-  such that
+  \set{\alpha_0,\ldots,\alpha_q} \to \set{v_0,\ldots,v_k}$ where 
 \begin{enumerate}
+\item $v_i \neq v_{i'}$ if $i \neq i'$.    
 \item If $f(\alpha_j) = v_i$ and $f(\alpha_{j+1}) = v_{i'}$, then $i
@@
 
-\begin{figure}
+\begin{figure}[t]
 \centering
-\scalebox{1}{
+\scalebox{0.8}{
 \input{fig-embedding}
 }
-\caption{???}
+\caption{An example of an \scp instance and a solution.}
 \label{fig:solution}
@@
 
-The cost of a placement $f$ is:
+The cost of a placement $f$ is defined as:
 \[
-\sum_j c(\alpha_j,f(\alpha_j))
+c(f) \eqdf \sum_j c(\alpha_j,f(\alpha_j))
 ~.
@@
 We also consider an extended version of \scp in which each physical
-link causes a delay and there is an upper bound $T$ on the total
+link causes a delay and there is an upper bound $L$ on the total
 delay.  More formally, each pair of a virtual edge $\eps$ and physical
-edge $e$ is associated with a latency $t(\eps,e)$.
+edge $e$ is associated with a latency $\ell(\eps,e)$.
 %
-Given a placement $f: \set{\alpha_0,\ldots,\alpha_\ell} \to
+Given a placement $f: \set{\alpha_0,\ldots,\alpha_q} \to
 \set{v_0,\ldots,v_k}$, the total latency of the solution is given by
 \[
-T(f) = \sum_j \sum_{e \in \bar{f}(\eps)} t(\eps,e)
+L(f)
+= \sum_{j=0}^{q-1} \sum_{e \in \bar{f}((\alpha_j,\alpha_{j+1}))} \ell((\alpha_j,\alpha_{j+1}),e)
 ~.
 \]
-In this case there is an additional constraint that $T(f) \leq T$.
+In this case there is an additional constraint that $L(f) \leq L$.
+
+%We note that this global bound does not have to represent latency.
+%For example, it can bound the probability of failure along the path.
+%(In this $\ell(\eps,e)$ is the logarithm of the probability.)
 
@@
 
-\paragraph*{\bf Definitions and notation.}
+%\paragraph*{\bf Definitions and notation.}
 %
-Define $n_p \eqdf \abs{V}$ and $m_p \eqdf \abs{E}$.  Similarly, define
-$n_v \eqdf \abs{\calV}$ and $m_v \eqdf \abs{\calE}$.
+%Define $n_p \eqdf \abs{V}$ and $m_p \eqdf \abs{E}$.  Similarly, define
+%$n_v \eqdf \abs{\calV}$ and $m_v \eqdf \abs{\calE}$.
 
+\paragraph*{Notation.}
+%
 Given a virtual DAG $\calG$, we assume the existence of a topological
-sorting of the vertices and write $\alpha \prec_v \beta$ if $\alpha$
+sorting of the vertices and write $\alpha \prec \beta$ if $\alpha$
 precedes $\beta$ in this ordering.  If the physical network is a DAG,
-then we make a similar assumption and write $v \prec_p u$ if $v$
+then we make a similar assumption and write $v \prec u$ if $v$
 precedes $u$ in this ordering.
@@
 %
-One the other hand, since all demands and capacities are $1$, no two
+On the other hand, since all demands and capacities are $1$, no two
 VNFs can share a physical node.  Hence a \scp solution induces an
@@
 \begin{proof}
-The prove the theorem using a reduction from \textsc{Partition}.
-Given a \textsc{Partition} instance $\set{a_1, \ldots, a_n}$ we
+We prove the theorem using a reduction from \textsc{Partition}.
+Given a \textsc{Partition} instance $\set{a_1, \ldots, a_n}$, we
 construct an \scp instance as follows.
@@
 there are two edges $(s,v)$ and $(v,t)$.  The capacity of $v$ is $p(v)
-= \half \sum_i a_i$.  Edge capacities are zero.
+= \half \sum_i a_i$.  Edge bandwidth are zero.
 %
 The virtual DAG is composed of $2n+2$ vertices, namely
-\[
+\(
 \calV
@@
   \cup \set{\beta_1, \ldots, \beta_n}
-~.
-\]
+%~.
+\).
 Also,
@@
 %
-Also, it is not hard to verify that $a \in \textsc{Partition}$ if and
-only if there exists a solution whose cost is $\half \sum_i a_i$.
+Also, it is not hard to verify that $\set{a_1, \ldots, a_n} \in
+\textsc{Partition}$ if and only if there exists a solution whose cost
+is $\half \sum_i a_i$.
 %
@@
 
-\begin{figure}
+\begin{figure}[t]
   \centering
+\scalebox{1}{
   \input{fig-reduction}
-\caption{???}
-\label{fig:dag}
+}
+\caption{The specification defined in the proof of Theorem~\ref{thm:simple}.}
+\label{fig:simple}
 \end{figure}
 
-\dror{Figure 2: source and destination should be fixed}
+Next, we show that \scp is NP-hard even if both the physical network
+and the VNF specification are paths.
 
@@
 \begin{proof}
+We prove the theorem using a reduction from \textsc{Partition}.  Given
+a \textsc{Partition} instance $\set{a_1, \ldots, a_n}$, we construct a
+virtual path $\sigma, \alpha_1, \ldots, \alpha_n, \tau$ and a physical
+path $s, v_1^-, v_1^+, \ldots, v_n^-, v_n^+, t$.  We set $p(v) = 1$,
+for every node $v \neq s,t$, and $p(\alpha_i) = 1$, for every $i$.  In
+addition, we set $b(e) = 1$, for every edge $e \in E$, and $b(\eps) =
+1$, for every edge $\eps \in \calE$.
+%
+As for the costs, we define $c(\alpha_i, v_i^-) = 0$, $c(\alpha_i,
+v_i^+) = a_i$, and for any $v \notin \{v_i^-,v_i^+\}$ we set
+$c(\alpha_i, v) = \infty$.  We also define $\ell((\alpha_i,\alpha_{i+1}),
+(v_i^-,v_i^+)) = a_i$, and set $\ell(\eps,e) = 0$, otherwise.  Finally,
+we set $L = \half \sum_i^n a_i$.
+%
+Figure~\ref{fig:reduction2} depicts the above reduction.
+%
+One can verify that $a_i$ is either counted in the latency of in the
+cost.  Hence, $\set{a_1, \ldots, a_n} \in \textsc{Partition}$ if and
+only if there is a placement with cost $\half \sum_i^n a_i$.
+%
+\qed
+\end{proof}
 
-\dror{reduction from partition using latency}
+\begin{figure}[t]
+\centering
+\scalebox{.75}{
+\input{fig-reduction2}
+}
+\caption{A reduction from a partition instance $a_1, \ldots, a_n$.
+  The cost function enforces each $\alpha_i$ to be placed either in
+  $v_i^-$ or in $v_i^+$.  In the former case this placement incure no
+  cost but additional latency of $a_i$, in the later case there will
+  be additional $a_i$ cost with zero latency.}
+\label{fig:reduction2}
+\end{figure}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Algorithms for Physical Directed Acyclic Graphs}
+\label{sec:algorithms}
+
+In this section we present an FPTAS for \scp in DAGs which is based on
+a dynamic programming algorithm.
+%
+The algorithm is described in a top down manner.  We first assume that
+costs are polynomially bounded and design a dynamic programming
+algorithm that computes a minimum cost placement of a virtual path
+within a single physical node.  Next, we provide a dynamic programming
+algorithm for \scp without the latency constraint.  Then, we give an
+algorithm that copes with a global latency constraint.  At the end of
+the section we drop our assumption on the costs and use standard
+scaling techniques to obtain an FPTAS for \scp in DAGs.
+
+%%%%%
+
+\subsection{Placing a Sub-chain in a Physical Node}
+
+Assume that we want to place a minimum cost virtual path from a VNF
+$\alpha$ to a VNF $\beta$ within a physical node $v$.  A sequence of
+VNFs $\alpha = \alpha_0,\alpha_2,\ldots,\alpha_q = \beta$ is a
+\emph{candidate path} if $(\alpha_i,\alpha_{i+1}) \in \calE$, for
+every $i$, and $\sum_i p(\alpha_i) \leq p(v)$.  We would like to find
+such a path with minimum cost, and we denote the cost of such a path
+by $\cost_v(\alpha \leadsto \beta)$.
+
+We use dynamic programming in order to compute such a path.  Let
+$\process_v(\alpha \leadsto \beta,c)$ be the minimum amount of
+processing required to place a virtual path form $\alpha$ to $\beta$
+into $v$ among paths whose cost is at most $c$.
+%
+The value of $\process_v(\alpha \leadsto \beta,c)$ can be computed
+recursively as follow:
+\[
+\process_v(\alpha \leadsto \beta, c) =
+\begin{cases}
+%\infty    & c < 0, \\
+\infty    & c(\alpha,v) > c, \\
+p(\alpha) & c(\alpha,v) \leq c, \beta = \alpha, \\
+\displaystyle
+\min_{(\gamma,\beta) \in \calE}
+   \set{\process_v(\alpha \leadsto \gamma, c - c(\beta,v)) + p(\beta)}
+          & \text{otherwise}.
+\end{cases}
+\]
+Observe that if $c(\alpha,v) > c$, then a placement is not possible
+with a budget $c$.  Otherwise, if $\alpha = \beta$, then the best path
+is the one containing only $\alpha$.  If $\alpha \neq \beta$, then an
+optimal path ends with an edge $(\gamma,\beta) \in \calE$, which means
+that the processing placed at $v$ consists of $p(\beta)$ plus the
+minimum amount of processing of a path from $\alpha$ to $\gamma$,
+whose cost is at most $c - c(\beta,v)$.
+
+To complete our argument observe that the following holds:
+\[
+\cost_v(\alpha \leadsto \beta)
+= \min \set{c : \process_v(\alpha \leadsto \beta, c) \leq p(v)}
+~.
+\]
+
+Since the costs are assumed to be polynomially bounded, there is a
+polynomial number of states to be computed, and the computation of
+each of them can be done in linear time.  Hence, the total running
+time is polynomial.  Finally, we note that the above algorithm
+computes the minimum amount of processing, but may also be used to
+compute the actual placement that achieves this value using standard
+techniques.
+
+%%%%%
+
+\subsection{Placing a Service Chain}
+
+In this section we describe a dynamic programming algorithm for
+placing a service chain without a global latency bound.
+
+Consider an optimal solution of \scp, i.e., a service chain from
+$\sigma$ to $\tau$ which is placed along a path from $s$ to $t$ in the
+physical DAG.  Suppose $v$ is a node along the path from $s$ to $t$.
+Also, let $\alpha$ be the last VNF in the service chain which is
+placed in the path from $s$ to $v$.  It must be that the placement of
+the VNFs from $\sigma$ to $\alpha$ in the path from $s$ to $v$ is the
+best one among all placements of a virtual path from $\sigma$ to
+$\alpha$ in a path from $s$ to $v$.  In other words, any partial
+placement of an optimal placement is also optimal.  Our algorithm is
+based on this property.
+
+We define a state for each pair of VNF $\alpha$ and physical node $v$.
+Let $\cost(\alpha,v)$ stand for the minimum cost placement of a
+virtual path from $\sigma$ to $\alpha$ in a path from $s$ to $v$,
+where $\alpha$ is the last VNF which is placed along the physical
+path.
+%
+In addition, we write $(u, v) \Mapsto (\gamma,\beta)$ if $v$ is
+reachable from $u$ using only edges with bandwidth at least
+$b(\gamma,\beta)$, namely if there is a path from $u$ to $v$ such that
+the bandwidth of all edges in the path is at least $b(\gamma,\beta)$.
+%
+$\cost(\alpha,v)$ can be computed recursively, as follows:
+\[
+\cost(\alpha,v) =
+\begin{cases}
+0 & \alpha = \sigma, v = s, \\
+\displaystyle
+\min_{
+  \substack{\beta \prec \alpha, (\gamma,\beta) \in \calE, \\
+           u \prec v, \\
+         (u,v) \Mapsto (\gamma,\beta)}
+     }
+  \set{\cost(\gamma,u) + \cost_v(\beta \leadsto \alpha)}
+  & \text{otherwise}.
+\end{cases}
+\]
+The desired value is $\cost(\tau,t)$.
+%
+Consider an optimal placement of a virtual path ending at $\alpha$
+within a path ending at $v$.  Let $\gamma$ be the first VNF along the
+virtual path that is not placed in $v$.  Also, let $u$ be the node in
+which $\gamma$ is placed.  Hence, the optimal placement is composed of
+three segments: an optimal placement of a virtual path that ends in
+$\gamma$ in a physical path ending at $u$, a virtual edge
+$(\gamma,\beta)$ is placed in the path from $u$ to $v$, and a minimum
+cost placement of a virtual path from $\beta$ to $\alpha$ in $v$, that
+does not violate the capacity of $v$.
+%
+Thus, we check all pairs $(\gamma,u)$, where $\gamma \prec \alpha$ and
+$u \prec v$, and for each pair we consider any neighbor
+$(\gamma,\beta) \in \calE$ and $\beta \prec \alpha$ such that $(u, v)
+\Mapsto (\gamma,\beta)$.
+%
+The recursive computation is illustrated in Figure~\ref{fig:dp1}.
+
+\begin{figure}[t]
+\centering
+\scalebox{0.9}{
+\input{fig-dp2}
+}
+%\vspace{-20pt}
+\caption{The optimal placement of a path to $\alpha$ into a path to
+  $v$ can be efficiently computed by breaking the problem into the
+  problem of placing a path to $\gamma$-path into a path to $u$ (blue,
+  dashed rectangles) and the problem of embedding a path from $\beta$
+  to $\alpha$ into $v$ (orange, dotted).  The path from $u$ to $v$
+  must carry at least $b(\gamma,\beta)$ bandwidth.  }
+\label{fig:dp1}
+\end{figure}
+
+As for the running time, observe that checking whether $(u, v) \Mapsto
+(\gamma,\beta)$ can be done using DFS in linear time.
+%
+Since the number of state is polynomial, and each state can be
+computed in polynomial time, the total running time is polynomial.
+Finally, we note that the above algorithm computes the minimum amount
+of cost, but may also be used to compute the actual placement
+that achieves this value using standard techniques.
+
+%%%%%
+
+\subsection{Placing a Service Chain with a Latency Bound}
+\label{sub:DPL}
+
+We now consider the \scp problem with latency.  Recall that in this
+variant of the problem we are also given a latency function $\ell: E
+\times \calE \to \reals_+$, and a latency upper bound $L$.  The goal
+is to find a minimum cost placement that also respect the latency
+constraint.
+
+Let $\latency(\alpha,v,c)$ be the minimum latency created by a
+placement of a virtual path from $\sigma$ to $\alpha$ in a path from
+$s$ to $v$ whose cost is at most $c$.
+%
+Also, let $\latency(\gamma,\beta,w \leadsto v)$ be the minimum
+possible latency of path from $w$ to $v$ such that the bandwidth of
+all edges in the path is at least $b(\gamma,\beta)$.  That is,
+\[ 
+\latency(\gamma,\beta,w \leadsto v)
+= \min_{f: b(\gamma,\beta) \leq \min_{e \in \bar{f}(\gamma,\beta)} b(e)}
+    \sum_{e \in \bar{f}(\gamma,\beta)} \ell((\gamma,\beta),e)
+~.
+\]
+Observe that $\latency(\gamma,\beta,w \leadsto v)$ can be computed
+using a \textsc{Shortest Path} algorithm, were we consider only edges
+whose bandwidth cap is at least $b(\gamma,\beta)$.
+%
+Now we are ready for the computation of $\latency(\alpha,v,c)$:
+\[
+\latency(\alpha,v,c) =
+\begin{cases}
+\infty  &  c < 0 \\
+0       &  \alpha = \sigma, v = s, c \geq 0 \\
+\displaystyle
+\min_{
+  \substack{\beta \prec \alpha, (\gamma,\beta) \in \calE, \\
+           w \prec v, (u,w) \in E, \\
+         (u,v) \Mapsto (\gamma,\beta)}
+     }
+     \set{\begin{array}{l}
+          \latency(\gamma,\beta,w \leadsto v) + \\
+          \latency(\gamma,u,c - \cost_v(\beta \leadsto \alpha))
+          \end{array}
+     }
+  & \text{otherwise}.
+\end{cases}
+\]
+The minimum latency of a placement of a path to $\alpha$ in a path to
+$v$ whose cost is at most $c$ can be divided into two values: the
+latency caused by the placement of a path to $\gamma$, where
+$(\gamma,\beta) \in \calE$, and $\beta \prec \alpha$, with cost $c -
+\cost_v(\beta \leadsto \alpha)$, and the latency caused by placing a
+virtual edge $(\gamma,\beta)$ on a physical path from $w$ to $v$,
+where $w \prec v$ and $(u,w) \in E$.
+%
+The optimal value is $\min \set{c : \latency(\tau,t,c) \leq L}$.
+
+Since the computation of $\latency(\gamma,\beta,w \leadsto v)$ can be
+done efficiently, the computation for a triple $(\alpha,v,c)$ can be
+done in polynomial time.  Hence, the total running time is polynomial.
+Finally, as in the previous algorithms, one may use the algorithm to
+compute a corresponding placement
+%that achieves this value
+using standard techniques.
+
+%%%%%
+
+\subsection{FPTAS for General Costs}
+
+In this section we present an FPTAS for \scp in DAGs for general
+costs, namely without the assumption that costs are polynomially
+bounded.  Our algorithm is similar to the FPTAS for the
+\textsc{Minimum Knapsack} problem.
+
+Let $f$ be an optimal placement, and let $c_{\max}$ be the maximum
+cost of a VNF placement by $f$, i.e., $c_{\max} = \max_{f(\alpha) =
+  u} c(\alpha,v)$.
+%
+Given a constant $\eps>0$, we define
+\[
+c'(\alpha, v) \eqdf
+\begin{cases}
+\ceil{\frac{c(\alpha, v)}{c_{\max}} \cdot \frac{n}{\eps}}
+       & c(\alpha, v) \leq c_{\max}, \\
+\infty & c(\alpha, v) > c_{\max}.
+\end{cases}
+\]
+Let $f'$ be an optimal placement with respect to $c'$.
+
+\begin{lemma}
+\label{lemma:guess}
+$c(f') \leq (1+\eps)c(f)$.
+\end{lemma}
+\begin{proof}
+We have that
+\begin{align*}
+c(f')
+%&
+=    \sum_{\alpha} c(\alpha,f'(\alpha)) %\\
+& \leq \frac{\eps c_{\max}}{n} \cdot \sum_{\alpha} c'(\alpha,f'(\alpha)) \\
+& \leq \frac{\eps c_{\max}}{n} \cdot \sum_{\alpha} c'(\alpha,f(\alpha)) \\
+& \leq \frac{\eps c_{\max}}{n} \cdot
+     \sum_{\alpha}
+       \paren{ c(\alpha,f(\alpha)) \cdot \frac{\eps c_{\max}}{n} + 1} \\
+%& =    c(f) + \frac{\eps c_{\max}}{n} \cdot n \\
+& =    c(f) + \eps c_{\max} \\
+& \leq (1+\eps) c(f)
+~,
+\end{align*}
+where the second inequality is due to the optimality of $f'$ with
+respect to $c'$.
+%
+\qed
+\end{proof}
+
+This leads to the following result:
+
+\begin{theorem}
+\label{thm:fptas}
+There exists an FPTAS for \scp in DAGs.
+\end{theorem}
+\begin{proof}
+Given $\eps>0$, run the dynamic programming algorithm from
+Section~\ref{sub:DPL} $\abs{\calV} \cdot \abs{V}$ times, once for each
+possible value of $c_{\max}$, and choose the best placement.
+According to Lemma~\ref{lemma:guess} the best placement is
+$(1+\eps)$-approximate.  The running time is polynomial in the input
+size and in $1/\eps$.
 %
@@
 
-\section{Algorithm}
+\section{General Networks}
+\label{sec:general}
+
+In this section we consider \scp when the physical network is an
+undirected graph.  Recall that even the feasibility version of \scp is
+NP-hard in general networks, and therefore we focus on a special case.
+%
+A vertex $v \in V$ is called \emph{neighborly} if it has more than two
+neighbors.
+%In this section
+We assume that there exists an optimal placement whose physical path
+consists of at most $k$ neighborly vertices.  For example, this can be
+assumed if all simple paths from $s$ to $t$ contain at most $k$
+neighborly vertices.
+%
+We present a randomized algorithm that consists of $k!$ iterations of
+the following two phases: an orientation phase that applies a random
+orientation to the physical network, and an execution of the FPTAS for
+DAGs given in Theorem~\ref{thm:fptas}.  The algorithm finds a
+$(1-\eps)$-approximate placement with probability $(1-1/e)$, and
+its running time of the algorithm is $O(t(n)k!)$, where $t(n)$ is the
+time it takes to compute a placement when the physical network is a
+DAG.
+%
+As usual, one may amplify the probability of success using repetition.
+
+The orientation phase is done as follows: let $N$ be the set of
+neighborly vertices, and let $\pi:N \to \set{1,\ldots,\abs{N}}$ be a
+random permutation.  We direct the edges according to $\pi$.  Observe
+that each edge $e \in E$ is found on a simple path between two
+neighborly nodes $v_e$ and $v'_e$, in which all internal vertices are
+in $V \subseteq N$.  The edge $e$ is directed towards $v_e$, if
+$\pi(v_e) > \pi(v'_e)$, and otherwise it is directed towards $v'_e$.
+%
+Observe that when this process terminates we get a DAG, denoted by
+$G_\pi$, where there is a topological order than is consistent which
+$\pi$.  Figure~\ref{fig:orientation} depicts the orientation stage.
+%
+A na\"ive implementation of this phase would run in $O(|V||E|)$ time.
+
+\begin{figure}[t]
+\centering
+\scalebox{0.8}{
+  \input{fig-orientation}
+}
+\caption{Orientation phase: on the left is the physical network, where
+  only the heavy nodes are drawn.  The numbers represent the
+  permutation and the dashed path represents a path of an optimal
+  placement.  The orientated physical network is on the right.  It is
+  enough that the internal ordering of the nodes on the dashed path is
+  "correct" to ensure that the survival of the optimal placement. }
+\label{fig:orientation}
+\end{figure}
+
+Upon completing the orientation, we use our previous algorithm to find
+a placement.  We repeat this process $k!$ times, each time with a new
+independent random permutation, and keep the best embedding so far.
+
+\begin{theorem}
+With probability at least $1 - e^{-1}$ the algorithm finds a
+$(1+\eps)$-approximate placement after $k!$ iterations.
+\end{theorem}
+\begin{proof}
+Consider an optimal placement with at most $k$ neighborly vertices,
+and let $\pi'$ be the permutation it induces on the neighborly
+vertices in the physical path.
+%
+If the random permutation $\pi$ orders the neighborly vertices
+correctly, i.e., if $\pi(v) = \pi'(v)$, for every $v \in N$, then the
+optimal placement is feasible with respect to $G_\pi$.  Hence, the
+FPTAS will find a $(1+\eps)$-approximate placement in $G_\pi$.  This
+placement is feasible, and therefore $(1+\eps)$-approximate placement,
+with respect to $G$.
+%
+$\pi$ agrees with $\pi'$ with probability $1/k!$, and the probability
+that $\pi$ does not agree with $\pi'$ in $k!$ iterations is $1 - (1 -
+1/k!)^{k!} \leq 1 - e^{-1}$.
+%
+\qed
+\end{proof}
+
+\section{Fault Tolerance}
 
@@
 
-\section{Latency}
+%\section{Extensions}
+
+%Costs by sets of VNFS
+
+%Fault tolerant placement: two service chains?
+
+%FPT algorithm where the number of servers whose degree is larger than
+%two is a parameter?
 

### 2017-10-29 src/chain.tex
ft introduction

@@
 \section{Fault Tolerance}
+In this section we consider the problem of a service chain placement when there 
+is also demand for fault tolerance.
+Formally, given a physical network, a virtual specification and a parameter 
+$\phi \in \mathbb{N}$, a $\phi$-robust placement is a collection of $\phi$ placements,
+$f_1,\ldots,f_\phi$,
+that correspond to $\phi$ internal vertex disjoint physical paths. 
+We are looking for a $\phi$-robust placement that minimize the total cost:
+$$
+\sum_{i = 1}^\phi \sum_j c(\alpha_j,f_i(\alpha_j))
+$$
 

### 2017-11-02 src/chain.tex
layer

@@
 $$
+In this section we discuss how to efficiently find an optimal 
+(assuming integral polynomial bounded costs) 2-robust placement.
+The algorithm presented here, however, can be generalized to find an optimal $\phi$-robust
+placement for any $\phi$
+
+\subsection{Failure of the Greedy Algorithm}
+Here we give a simple example why the greedy algorithm fails badly.
+By greedy we mean applying the previous algorithm once to find an optimal placement, 
+then removing all the vertices from the resulted path and applying the same algorithm again
+to find the second placement.
+Consider the physical graph as described in Figure~\ref{fig:greedy-bad} and a virtual path of
+two virtual functions $\alpha$ and $\beta$.
+Assume latencies, bandwidth, and processing constraints are all negligible 
+and assume the following cost function 
+$c(1, \alpha) = c(2, \alpha) = 1-\varepsilon, c(1, \beta) = c(2, \alpha) = 1$.
+The greedy algorithm is unable to find a 2-robust placement in this case - after the 
+first iteration there is no path from $s$ to $t$ - while, clearly there is a 2-robust
+placement that costs $4 - 2 \epsilon$.   
+\begin{figure}
+\caption{
+\label{fig:greedy-bad}
+}
+\begin{center}
+\input{fig-alg-bad-example}
+\end{center}
+\end{figure}
+
+\subsection{Fault Tolerance on Layered Graph}
+We first assume that the input graph is a directed layered graph, i.e.
+$G = (\bigcup_{i = 1}^l L_i, A)$ where 
+$A \subseteq \bigcup_{i = 1}^{l - 1} L_i \times L_{i+1}$.
+We assume that the number of vertices in each layer is at least two, or otherwise a 2-robust 
+placement does not exist.
+The algorithm uses dynamic programming.
+We find the optimal 2-robust placement for every  
+combination of two physical vertices from the same layer, 
+and every combination of two virtual functions.
+Formally, given the input $(G = (V, E), \calG = (\calV, \calE), p, b, s, t, c)$
+We define $ft(v_1, v_2, \alpha_1, \alpha_2)$ to be the optimal 2-robust placement of 2 chains
+that start at $\sigma$ and end at $\alpha_1, \alpha_2$ respectively into 
+(internal vertex disjoint) physical paths that start at $s$ and end at $v_1,v_2$ respectively.
+One can verified that the following recursive formula holds:
+$$
+ft(v_1, v_2, \alpha_1, \alpha_2) = 
+\min_{
+\begin{subarray}{c}
+u_1,u_2,(\beta_1,\beta_2:
+\\
+u_1
+\\
+asdf
+\end{subarray}
+}
+$$
+
+\subsection{Layered Graph Transformation}
+Given a directed acyclic graph $G = (V, A)$, 
+and let $\pi:V \to [n]$ be an arbitrary topological sorting of $G$ 
+we transform it into a layered graph $G'$ by replacing every edge $(u, v)$ with a directed path of 
+length (number of arcs) $\pi(v) - \pi(u)$ from $u$ to $v$.
+We set the processing capacity of each internal vertex on this path to be zero,
+and the bandwidth of the arcs along the path to be $b(u,v)$.
+It is easy to see that the resulting graph is indeed a layered graph and that every placement
+on $G$ corresponds to a placement on $G'$ with the same cost.
+Figure~\ref{fig:layer-transform} depicts this process.
+\begin{figure}
+\caption{
+\label{fig:layer-transform}
+}
+\begin{center}
+\input{layer-transform}
+\end{center}
+\end{figure}
 

### 2017-11-06 src/chain.tex
dp
FPT + FT

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{FPT Algorithm for General Networks}
+We now propose an FPT algorithm for general networks that is similar to the randomized 
+algorithm from Section~\ref{sec:general}.
+Our FPT algorithm runs in $O(k! \cdot (A + O))$ where $k$ is the number of neighborly
+vertices in the graph, $A$ is the time required to find a solution on a DAG,
+and $O$ is the time required to orient the graph given a permutation on the neighborly
+vertices, as discussed above.
+The algorithm executes the FPTAS for DAGs given in Theorem~\ref{thm:fptas}
+once for any orientation results from any of the $k!$ possible permutations and
+returns the best solution.
+The following theorem follows immediately.
+
+\begin{theorem}
+There is an FPT algorithm that finds a $(1+\eps)$-approximate placement after $k!$ iterations 
+\end{theorem}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Fault Tolerance}
@@
 $$
-ft(v_1, v_2, \alpha_1, \alpha_2) = 
-\min_{
-\begin{subarray}{c}
-u_1,u_2,(\beta_1,\beta_2:
-\\
-u_1
-\\
-asdf
-\end{subarray}
-}
+ft(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = \min
+\begin{cases}
+nn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
+\\
+ny(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
+\\
+yn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
+\\
+yy(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) 
+\end{cases}
 $$
+
+where
+$$
+\begin{array}{l}
+nn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
+\displaystyle\smashoperator{\min_{\substack{\\ u_1, u_2: \\ b(u_1, v_1) \geq b(\gamma_1, \beta_1) \\ b(u_2, v_2) \geq b(\gamma_2, \beta_2)}}}
+ft(u_1, u_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
+\\
+ny(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
+\displaystyle\smashoperator{\min_{
+	\substack{
+	u_1, u_2: 
+	\\ 
+	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
+	\\ 
+	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
+	\\
+	\gamma'_2\beta'_2 \in \calE:
+	\\
+	\beta'_2 \prec \gamma_2 
+	}}}
+ft(u_1, u_2, \alpha_1, \gamma_2, \gamma_1\beta_1, \gamma'_2\beta'_2)
+\\
+yn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
+\displaystyle\smashoperator{\min_{
+	\substack{
+	u_1, u_2: 
+	\\ 
+	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
+	\\ 
+	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
+	\\
+	\gamma'_1\beta'_1 \in \calE:
+	\\
+	\beta'_1 \prec \gamma_1 
+	}}}
+ft(u_1, u_2, \gamma_1, \alpha_2, \gamma'_1\beta'_1, \gamma_2\beta_2)
+\\
+yy(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
+\displaystyle\smashoperator{\min_{
+	\substack{
+	u_1, u_2: 
+	\\ 
+	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
+	\\ 
+	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
+	\\
+	\gamma'_1\beta'_1, \gamma'_2\beta'_2 \in \calE:
+	\\
+	\beta'_1 \prec \gamma_1, \beta'_2 \prec \gamma_2 
+	}}}
+ft(u_1, u_2, \gamma_1, \gamma_2, \gamma'_1\beta'_1, \gamma'_2\beta'_2)
+\end{array}
+$$
+
+\begin{theorem}
+There is an algorithm that, on a layered graph, finds an optimal 2-robust placement in 
+polynomial time. 
+\end{theorem}
+
+\begin{proof}
+One can verify, that using dynamic programming, the above recursive can be solved in polynomial time,
+using backtracking we can also find the optimal solution.
+\end{proof}
+
+We note that the above algorithm does not take into account the latency constraint.
+It is possible, however, given a latency constraint, $L$, to modify the algorithm to return
+an optimal solution such that the total latency of the two placements is no more than $2L$.
+Such a solution is guaranteed to be optimal in terms of costs.
+It is also easy to see that in such solution at least one of the placements has lower latency 
+than $L$ and the other one has latency that is at most $2L$.
 
@@
 \begin{figure}
-\caption{
+\captionsetup{singlelinecheck=off}
+\caption[layered]{foo
 \label{fig:layer-transform}
-}
+\begin{enumerate}
+\item A directed acyclic graph that is not a layered graph
+  \item A topological sorting of the above graph
+  \item A layered graph obtained by replacing crossing arcs with simple paths 
+\end{enumerate}}
 \begin{center}

### 2017-11-06 src/chain.tex
camera ready ?

--- 2017-10-29 src/chain.tex
@@
 
-\section{Fault Tolerance}
-In this section we consider the problem of a service chain placement when there 
-is also demand for fault tolerance.
-Formally, given a physical network, a virtual specification and a parameter 
-$\phi \in \mathbb{N}$, a $\phi$-robust placement is a collection of $\phi$ placements,
-$f_1,\ldots,f_\phi$,
-that correspond to $\phi$ internal vertex disjoint physical paths. 
-We are looking for a $\phi$-robust placement that minimize the total cost:
-$$
-\sum_{i = 1}^\phi \sum_j c(\alpha_j,f_i(\alpha_j))
-$$
+\paragraph{\textbf{FPT Algorithm}}
+Let $k = |N|$, we present an FPT algorithm that runs in $k!$ iterations and is
+guaranteed to find the optimal placement.
+For each possible permutation of the $k!$ permutations on the $k$ neighborly vertices, 
+the algorithm applies the graph orientation procedure as described above,
+and then executes the FPTAS for DAGs given in Theorem~\ref{thm:fptas}, 
+thus the running time of the algorithm is $O(k!(A + O))$ where $A$ is the running time of the
+FPTAS and $O$ is the time it takes to orient an undirected graph.
+
+\begin{theorem}
+There is an FPT algorithm that finds a $(1+\eps)$-approximate placement 
+in $O(k!(A + O))$ time
+\end{theorem}
+
+\begin{proof}
+The running time of the algorithm follows from the discussion above, the correctness of the 
+algorithm follows directly from the fact that there is a correct orientation among the $k!$
+possible once that corresponds to the optimal placement 
+\qed
+\end{proof}
 

### 2017-11-07 src/chain.tex
dror1

@@
 \renewcommand{\floatpagefraction}{0.6}
+
+\parskip = \smallskipamount
 
@@
 
+\begin{document}
+
 \title{\bf Service Chain Placement in SDNs%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
 \maketitle
@@
 On the other hand, we present an FPTAS for the case where the network
-is a DAG.  In addition, based on our FPTAS, we provide a randomized
-algorithm for instances in which the service chain passes through a
-bounded number of vertices whose degree is larger than two.
+is a DAG.  In addition, based on our FPTAS, we provide algorithms for
+instances in which the service chain passes through a bounded number
+of vertices whose degree is larger than two.
 \end{abstract}
@@
 
-\paragraph*{\bf Related work.}
-%
+\subsection{Related Work}
+%\paragraph*{\bf Related work.}
+
 In this paper we consider an SDN network that employs
@@
 
-\paragraph*{\bf Our results.}
-%
+\subsection{Our Results}
+%\paragraph*{\bf Our results.}
+
 We study the allocation problem of a compound flow request for a
@@
 single option.  Both reductions are from \textsc{Partition}.
-%
+
 On the positive side, we present an FPTAS for the case where the
@@
 contain at most $k$ such vertices.  The algorithm computes a
-$(1+\eps)$-approximate placement with probability $(1-e^{-1})$ using
-$k!$ invocation of the FPTAS.
+$(1+\eps)$-approximate placement with high probability using $k! \log
+n$ invocations of the FPTAS.
+%
+We also present a (deterministic) parameterized algorithm that
+computes a $(1+\eps)$-approximate placement in time $O(k! \cdot
+\text{poly}(n))$, where $k$ is the number of vertices in the network
+whose degree is larger than $2$.
 
@@
 %
-The \scplong (\scp) input is composed of three components, a physical
-network, a virtual specification, and placement costs:
+An instance of the \scplong (\scp) problem is composed of three
+components, a physical network, a virtual specification, and placement
+costs:
 \begin{description}
@@
   edge $e \in E$ has a non-negative bandwidth capacity $b(e)$.
+%
+  Without loss of generality, we assume that $p(s) = p(t) = 0$.
+
+\medskip
 
@@
 %
-  Without loss of generality, we assume that $p(s) = p(t) = 0$.  
-%
   The DAG $\calG$ has a source node $\sigma \in \calV$ and a
   destination $\tau \in \calV$. Each node $\alpha \in \calV$ represent
-  a VNF that has a processing demand $p(\alpha)$.  Without loss of
-  generality, we assume that $p(\sigma) = p(\tau) = 0$.  Each edge
-  $\eps \in \calE$ has a bandwidth demand $b(\eps)$.
+  a VNF that has a processing demand $p(\alpha)$.
+%
+  Without loss of generality, we assume that $p(\sigma) = p(\tau) =
+  0$.  Each edge $\eps \in \calE$ has a bandwidth demand $b(\eps)$.
+
+\medskip
 
@@
 
+\medskip
+
 \item[Physical path:] A simple path from $s$ to $t$ in $G$, namely a
@@
   $(v_i,v_{i+1}) \in E$, for every $i \in \set{0,\ldots,k-1}$.
+
+\medskip
 
@@
 \centering
-\scalebox{0.8}{
+\scalebox{0.85}{
 \input{fig-embedding}
@@
 The virtual DAG is composed of $2n+2$ vertices, namely
-\(
+\[
 \calV
@@
   \cup \set{\beta_1, \ldots, \beta_n}
-%~.
-\).
+~.
+\]
 Also,
@@
 \infty    & c(\alpha,v) > c, \\
-p(\alpha) & c(\alpha,v) \leq c, \beta = \alpha, \\
+p(\alpha) &
+\begin{array}{c}
+c(\alpha,v) \leq c, \\
+\beta = \alpha,
+\end{array}
+\\
 \displaystyle
@@
 \begin{cases}
-\infty  &  c < 0 \\
-0       &  \alpha = \sigma, v = s, c \geq 0 \\
+\infty  &  c < 0,\\
+0       &
+\begin{array}{c}
+\alpha = \sigma, v = s, \\
+\text{and } c \geq 0,
+\end{array} \\
 \displaystyle
@@
 \subsection{FPTAS for General Costs}
+\label{sub:fptas}
 
@@
 neighbors.
-%In this section
-We assume that there exists an optimal placement whose physical path
-consists of at most $k$ neighborly vertices.  For example, this can be
-assumed if all simple paths from $s$ to $t$ contain at most $k$
-neighborly vertices.
-%
-We present a randomized algorithm that consists of $k!$ iterations of
-the following two phases: an orientation phase that applies a random
+%
+First, we assume that there exists an optimal placement whose physical
+path consists of at most $k$ neighborly vertices.  For example, this
+can be assumed if all simple paths from $s$ to $t$ contain at most $k$
+neighborly vertices.  In this case we present a randomized algorithm
+that computes an $(1+\eps)$-approximate placement with high
+probability whose running time is $O(k! \cdot \text{poly}(n))$.
+%
+Our second algorithm works under the stronger assumption that there
+are $k$ neighborly vertices in the network.  In this case, we present
+a deterministic algorithm whose running time is $O(k! \cdot
+\text{poly}(n))$.
+
+%%%%%
+
+Our randomized algorithm that consists of $k!$ iterations of the
+following two phases: an orientation phase that applies a random
 orientation to the physical network, and an execution of the FPTAS for
 DAGs given in Theorem~\ref{thm:fptas}.  The algorithm finds a
-$(1-\eps)$-approximate placement with probability $(1-1/e)$, and
-its running time of the algorithm is $O(t(n)k!)$, where $t(n)$ is the
+$(1-\eps)$-approximate placement with probability $(1-1/e)$, and the
+running time of the algorithm is $O((n+t(n))k!)$, where $t(n)$ is the
 time it takes to compute a placement when the physical network is a
@@
 \centering
-\scalebox{0.8}{
+\scalebox{0.9}{
   \input{fig-orientation}
@@
 \begin{theorem}
-With probability at least $1 - e^{-1}$ the algorithm finds a
-$(1+\eps)$-approximate placement after $k!$ iterations.
+There exists an algorithm, that given an \scp instance with an optimal
+solution that contains at most $k$ neighborly vertices, finds a
+$(1+\eps)$-approximate placement with probability $1 - e^{-1}$, whose
+running time is $O(k! \cdot \text{\rm poly}(n))$.
 \end{theorem}
@@
 %
-$\pi$ agrees with $\pi'$ with probability $1/k!$, and the probability
-that $\pi$ does not agree with $\pi'$ in $k!$ iterations is $1 - (1 -
-1/k!)^{k!} \leq 1 - e^{-1}$.
+The permutation $\pi$ agrees with $\pi'$ with probability $1/k!$, and
+the probability that $\pi$ agrees with $\pi'$ in $k!$ iterations is $1
+- (1 - 1/k!)^{k!} \geq 1 - e^{-1}$.  One may amplify the success
+probability to $1 - \inv{n}$ using $\log n$ repetitions.
 %
@@
 
-\paragraph{\textbf{FPT Algorithm}}
-Let $k = |N|$, we present an FPT algorithm that runs in $k!$ iterations and is
-guaranteed to find the optimal placement.
-For each possible permutation of the $k!$ permutations on the $k$ neighborly vertices, 
-the algorithm applies the graph orientation procedure as described above,
-and then executes the FPTAS for DAGs given in Theorem~\ref{thm:fptas}, 
-thus the running time of the algorithm is $O(k!(A + O))$ where $A$ is the running time of the
-FPTAS and $O$ is the time it takes to orient an undirected graph.
+%%%%%
+
+In the case where $\abs{N} = k$ we can simply examine the $k!$
+permutations of the neighborly vertices.  For each possible
+permutation the algorithm applies the graph orientation procedure as
+described above, and then executes the FPTAS for DAGs given in
+Section~\ref{sub:fptas}.  Thus the running time of the algorithm is
+$O((n+t(n)k!)$, where $t(n)$ is the running time of the FPTAS for
+DAGs.
+%
+We note that permutation enumeration for $k$ numbers takes $O(k!)$
+time (see e.g.,~\cite{Even73,Sedgewick77})
 
 \begin{theorem}
-There is an FPT algorithm that finds a $(1+\eps)$-approximate placement 
-in $O(k!(A + O))$ time
+There exists an $O(k! \cdot \text{\rm poly}(n))$-time algorithm, that
+given an \scp instance with $k$ neighborly vertices, finds a
+$(1+\eps)$-approximate placement.
 \end{theorem}
-
-\begin{proof}
-The running time of the algorithm follows from the discussion above, the correctness of the 
-algorithm follows directly from the fact that there is a correct orientation among the $k!$
-possible once that corresponds to the optimal placement 
-\qed
-\end{proof}
+%\begin{proof}
+%The running time of the algorithm follows from the discussion above,
+%the correctness of the algorithm follows directly from the fact that
+%there is a correct orientation among the $k!$ possible once that
+%corresponds to the optimal placement
+%
+%\qed
+%\end{proof}
 
@@
 
+\subsection*{Acknowledgement}
+
+We thank Reuven Bar-Yehuda for helpful discussions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \bibliographystyle{abbrv}

### 2017-11-09 src/chain.tex
fix

@@
 
-Our randomized algorithm that consists of $k!$ iterations of the
+Our randomized algorithm consists of $k!$ iterations of the
 following two phases: an orientation phase that applies a random
@@
 solution that contains at most $k$ neighborly vertices, finds a
-$(1+\eps)$-approximate placement with probability $1 - e^{-1}$, whose
+$(1+\eps)$-approximate placement with high probability, whose
 running time is $O(k! \cdot \text{\rm poly}(n))$.
@@
 described above, and then executes the FPTAS for DAGs given in
-Section~\ref{sub:fptas}.  Thus the running time of the algorithm is
-$O((n+t(n)k!)$, where $t(n)$ is the running time of the FPTAS for
-DAGs.
+Section~\ref{sub:fptas}.  
+Thus the running time of the algorithm is $O(k! \cdot \text{\rm poly}(n))$.
 %

### 2017-11-12 src/chain.tex
camera ready

@@
 neighborly nodes $v_e$ and $v'_e$, in which all internal vertices are
-in $V \subseteq N$.  The edge $e$ is directed towards $v_e$, if
+in $V \setminus N$.  The edge $e$ is directed towards $v_e$, if
 $\pi(v_e) > \pi(v'_e)$, and otherwise it is directed towards $v'_e$.

### 2017-11-27 src/chain.tex

--- 2017-11-09 src/chain.tex
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{document}
 \maketitle
@@
 On the other hand, we present an FPTAS for the case where the network
-is a DAG.  In addition, based on our FPTAS, we provide algorithms for
-instances in which the service chain passes through a bounded number
-of vertices whose degree is larger than two.
+is a DAG.  In addition, based on our FPTAS, we provide a randomized
+algorithm for instances in which the service chain passes through a
+bounded number of vertices whose degree is larger than two.
 \end{abstract}
@@
 single option.  Both reductions are from \textsc{Partition}.
-
+%
 On the positive side, we present an FPTAS for the case where the
@@
   directed acyclic graph (DAG) $\calG = (\calV,\calE)$.
+%
+  Without loss of generality, we assume that $p(s) = p(t) = 0$.  
 %
@@
 neighbors.
-%
-First, we assume that there exists an optimal placement whose physical
-path consists of at most $k$ neighborly vertices.  For example, this
-can be assumed if all simple paths from $s$ to $t$ contain at most $k$
-neighborly vertices.  In this case we present a randomized algorithm
-that computes an $(1+\eps)$-approximate placement with high
-probability whose running time is $O(k! \cdot \text{poly}(n))$.
-%
-Our second algorithm works under the stronger assumption that there
-are $k$ neighborly vertices in the network.  In this case, we present
-a deterministic algorithm whose running time is $O(k! \cdot
-\text{poly}(n))$.
-
-%%%%%
-
-Our randomized algorithm consists of $k!$ iterations of the
-following two phases: an orientation phase that applies a random
+%In this section
+We assume that there exists an optimal placement whose physical path
+consists of at most $k$ neighborly vertices.  For example, this can be
+assumed if all simple paths from $s$ to $t$ contain at most $k$
+neighborly vertices.
+%
+We present a randomized algorithm that consists of $k!$ iterations of
+the following two phases: an orientation phase that applies a random
 orientation to the physical network, and an execution of the FPTAS for
 DAGs given in Theorem~\ref{thm:fptas}.  The algorithm finds a
-$(1-\eps)$-approximate placement with probability $(1-1/e)$, and the
-running time of the algorithm is $O((n+t(n))k!)$, where $t(n)$ is the
+$(1-\eps)$-approximate placement with probability $(1-1/e)$, and
+its running time of the algorithm is $O(t(n)k!)$, where $t(n)$ is the
 time it takes to compute a placement when the physical network is a
@@
 \centering
-\scalebox{0.9}{
+\scalebox{0.8}{
   \input{fig-orientation}
@@
 \begin{theorem}
-There exists an algorithm, that given an \scp instance with an optimal
-solution that contains at most $k$ neighborly vertices, finds a
-$(1+\eps)$-approximate placement with high probability, whose
-running time is $O(k! \cdot \text{\rm poly}(n))$.
+With probability at least $1 - e^{-1}$ the algorithm finds a
+$(1+\eps)$-approximate placement after $k!$ iterations.
 \end{theorem}
@@
 %
-The permutation $\pi$ agrees with $\pi'$ with probability $1/k!$, and
-the probability that $\pi$ agrees with $\pi'$ in $k!$ iterations is $1
-- (1 - 1/k!)^{k!} \geq 1 - e^{-1}$.  One may amplify the success
-probability to $1 - \inv{n}$ using $\log n$ repetitions.
+$\pi$ agrees with $\pi'$ with probability $1/k!$, and the probability
+that $\pi$ does not agree with $\pi'$ in $k!$ iterations is $1 - (1 -
+1/k!)^{k!} \leq 1 - e^{-1}$.
 %
@@
 
-%%%%%
-
-In the case where $\abs{N} = k$ we can simply examine the $k!$
-permutations of the neighborly vertices.  For each possible
-permutation the algorithm applies the graph orientation procedure as
-described above, and then executes the FPTAS for DAGs given in
-Section~\ref{sub:fptas}.  
-Thus the running time of the algorithm is $O(k! \cdot \text{\rm poly}(n))$.
-%
-We note that permutation enumeration for $k$ numbers takes $O(k!)$
-time (see e.g.,~\cite{Even73,Sedgewick77})
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{FPT Algorithm for General Networks}
+We now propose an FPT algorithm for general networks that is similar to the randomized 
+algorithm from Section~\ref{sec:general}.
+Our FPT algorithm runs in $O(k! \cdot (A + O))$ where $k$ is the number of neighborly
+vertices in the graph, $A$ is the time required to find a solution on a DAG,
+and $O$ is the time required to orient the graph given a permutation on the neighborly
+vertices, as discussed above.
+The algorithm executes the FPTAS for DAGs given in Theorem~\ref{thm:fptas}
+once for any orientation results from any of the $k!$ possible permutations and
+returns the best solution.
+The following theorem follows immediately.
 
 \begin{theorem}
-There exists an $O(k! \cdot \text{\rm poly}(n))$-time algorithm, that
-given an \scp instance with $k$ neighborly vertices, finds a
-$(1+\eps)$-approximate placement.
+There is an FPT algorithm that finds a $(1+\eps)$-approximate placement after $k!$ iterations 
 \end{theorem}
-%\begin{proof}
-%The running time of the algorithm follows from the discussion above,
-%the correctness of the algorithm follows directly from the fact that
-%there is a correct orientation among the $k!$ possible once that
-%corresponds to the optimal placement
-%
-%\qed
-%\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Fault Tolerance}
+In this section we consider the problem of a service chain placement when there 
+is also demand for fault tolerance.
+Formally, given a physical network, a virtual specification and a parameter 
+$\phi \in \mathbb{N}$, a $\phi$-robust placement is a collection of $\phi$ placements,
+$f_1,\ldots,f_\phi$,
+that correspond to $\phi$ internal vertex disjoint physical paths. 
+We are looking for a $\phi$-robust placement that minimize the total cost:
+$$
+\sum_{i = 1}^\phi \sum_j c(\alpha_j,f_i(\alpha_j))
+$$
+In this section we discuss how to efficiently find an optimal 
+(assuming integral polynomial bounded costs) 2-robust placement.
+The algorithm presented here, however, can be generalized to find an optimal $\phi$-robust
+placement for any $\phi$
+
+\subsection{Failure of the Greedy Algorithm}
+Here we give a simple example why the greedy algorithm fails badly.
+By greedy we mean applying the previous algorithm once to find an optimal placement, 
+then removing all the vertices from the resulted path and applying the same algorithm again
+to find the second placement.
+Consider the physical graph as described in Figure~\ref{fig:greedy-bad} and a virtual path of
+two virtual functions $\alpha$ and $\beta$.
+Assume latencies, bandwidth, and processing constraints are all negligible 
+and assume the following cost function 
+$c(1, \alpha) = c(2, \alpha) = 1-\varepsilon, c(1, \beta) = c(2, \alpha) = 1$.
+The greedy algorithm is unable to find a 2-robust placement in this case - after the 
+first iteration there is no path from $s$ to $t$ - while, clearly there is a 2-robust
+placement that costs $4 - 2 \epsilon$.   
+\begin{figure}
+\caption{
+\label{fig:greedy-bad}
+}
+\begin{center}
+\input{fig-alg-bad-example}
+\end{center}
+\end{figure}
+
+\subsection{Fault Tolerance on Layered Graph}
+We first assume that the input graph is a directed layered graph, i.e.
+$G = (\bigcup_{i = 1}^l L_i, A)$ where 
+$A \subseteq \bigcup_{i = 1}^{l - 1} L_i \times L_{i+1}$.
+We assume that the number of vertices in each layer is at least two, or otherwise a 2-robust 
+placement does not exist.
+The algorithm uses dynamic programming.
+We find the optimal 2-robust placement for every  
+combination of two physical vertices from the same layer, 
+and every combination of two virtual functions.
+Formally, given the input $(G = (V, E), \calG = (\calV, \calE), p, b, s, t, c)$
+We define $ft(v_1, v_2, \alpha_1, \alpha_2)$ to be the optimal 2-robust placement of 2 chains
+that start at $\sigma$ and end at $\alpha_1, \alpha_2$ respectively into 
+(internal vertex disjoint) physical paths that start at $s$ and end at $v_1,v_2$ respectively.
+One can verified that the following recursive formula holds:
+$$
+ft(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = \min
+\begin{cases}
+nn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
+\\
+ny(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
+\\
+yn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
+\\
+yy(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) 
+\end{cases}
+$$
+
+where
+$$
+\begin{array}{l}
+nn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
+\displaystyle\smashoperator{\min_{\substack{\\ u_1, u_2: \\ b(u_1, v_1) \geq b(\gamma_1, \beta_1) \\ b(u_2, v_2) \geq b(\gamma_2, \beta_2)}}}
+ft(u_1, u_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
+\\
+ny(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
+\displaystyle\smashoperator{\min_{
+	\substack{
+	u_1, u_2: 
+	\\ 
+	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
+	\\ 
+	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
+	\\
+	\gamma'_2\beta'_2 \in \calE:
+	\\
+	\beta'_2 \prec \gamma_2 
+	}}}
+ft(u_1, u_2, \alpha_1, \gamma_2, \gamma_1\beta_1, \gamma'_2\beta'_2)
+\\
+yn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
+\displaystyle\smashoperator{\min_{
+	\substack{
+	u_1, u_2: 
+	\\ 
+	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
+	\\ 
+	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
+	\\
+	\gamma'_1\beta'_1 \in \calE:
+	\\
+	\beta'_1 \prec \gamma_1 
+	}}}
+ft(u_1, u_2, \gamma_1, \alpha_2, \gamma'_1\beta'_1, \gamma_2\beta_2)
+\\
+yy(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
+\displaystyle\smashoperator{\min_{
+	\substack{
+	u_1, u_2: 
+	\\ 
+	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
+	\\ 
+	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
+	\\
+	\gamma'_1\beta'_1, \gamma'_2\beta'_2 \in \calE:
+	\\
+	\beta'_1 \prec \gamma_1, \beta'_2 \prec \gamma_2 
+	}}}
+ft(u_1, u_2, \gamma_1, \gamma_2, \gamma'_1\beta'_1, \gamma'_2\beta'_2)
+\end{array}
+$$
+
+\begin{theorem}
+There is an algorithm that, on a layered graph, finds an optimal 2-robust placement in 
+polynomial time. 
+\end{theorem}
+
+\begin{proof}
+One can verify, that using dynamic programming, the above recursive can be solved in polynomial time,
+using backtracking we can also find the optimal solution.
+\end{proof}
+
+We note that the above algorithm does not take into account the latency constraint.
+It is possible, however, given a latency constraint, $L$, to modify the algorithm to return
+an optimal solution such that the total latency of the two placements is no more than $2L$.
+Such a solution is guaranteed to be optimal in terms of costs.
+It is also easy to see that in such solution at least one of the placements has lower latency 
+than $L$ and the other one has latency that is at most $2L$.
+
+\subsection{Layered Graph Transformation}
+Given a directed acyclic graph $G = (V, A)$, 
+and let $\pi:V \to [n]$ be an arbitrary topological sorting of $G$ 
+we transform it into a layered graph $G'$ by replacing every edge $(u, v)$ with a directed path of 
+length (number of arcs) $\pi(v) - \pi(u)$ from $u$ to $v$.
+We set the processing capacity of each internal vertex on this path to be zero,
+and the bandwidth of the arcs along the path to be $b(u,v)$.
+It is easy to see that the resulting graph is indeed a layered graph and that every placement
+on $G$ corresponds to a placement on $G'$ with the same cost.
+Figure~\ref{fig:layer-transform} depicts this process.
+\begin{figure}
+\captionsetup{singlelinecheck=off}
+\caption[layered]{foo
+\label{fig:layer-transform}
+\begin{enumerate}
+\item A directed acyclic graph that is not a layered graph
+  \item A topological sorting of the above graph
+  \item A layered graph obtained by replacing crossing arcs with simple paths 
+\end{enumerate}}
+\begin{center}
+\input{layer-transform}
+\end{center}
+\end{figure}
 

### 2017-11-27 src/chain.tex
cactus

@@
 
-\begin{document}
 \maketitle
@@
 
-\paragraph*{Model.}
+\subsection*{Model.}
 %
@@
 
-\paragraph*{Notation.}
+\subsection*{Notation.}
 %
@@
 In this section we consider \scp when the physical network is an
-undirected graph.  Recall that even the feasibility version of \scp is
-NP-hard in general networks, and therefore we focus on a special case.
+undirected graph.  
+Recall that even the feasibility version of \scp is NP-hard in general networks,
+and therefore we focus on a special case.
 %
@@
 We assume that there exists an optimal placement whose physical path
-consists of at most $k$ neighborly vertices.  For example, this can be
-assumed if all simple paths from $s$ to $t$ contain at most $k$
+consists of at most $k$ neighborly vertices.  
+For example, this can be assumed if all simple paths from $s$ to $t$ contain at most $k$
 neighborly vertices.
@@
 orientation to the physical network, and an execution of the FPTAS for
-DAGs given in Theorem~\ref{thm:fptas}.  The algorithm finds a
-$(1-\eps)$-approximate placement with probability $(1-1/e)$, and
-its running time of the algorithm is $O(t(n)k!)$, where $t(n)$ is the
-time it takes to compute a placement when the physical network is a
-DAG.
+DAGs given in Theorem~\ref{thm:fptas}.  
+The algorithm finds a $(1-\eps)$-approximate placement with probability $(1-1/e)$, 
+and its running time of the algorithm is $O(t(n)k!)$, 
+where $t(n)$ is the time it takes to compute a placement when 
+the physical network is a DAG.
 %
@@
 
-The orientation phase is done as follows: let $N$ be the set of
-neighborly vertices, and let $\pi:N \to \set{1,\ldots,\abs{N}}$ be a
-random permutation.  We direct the edges according to $\pi$.  Observe
-that each edge $e \in E$ is found on a simple path between two
+The orientation phase is done as follows: 
+let $N$ be the set of neighborly vertices, 
+and let $\pi:N \to \set{1,\ldots,\abs{N}}$ be a random permutation.  
+We direct the edges according to $\pi$.  
+Observe that each edge $e \in E$ is found on a simple path between two
 neighborly nodes $v_e$ and $v'_e$, in which all internal vertices are
-in $V \subseteq N$.  The edge $e$ is directed towards $v_e$, if
-$\pi(v_e) > \pi(v'_e)$, and otherwise it is directed towards $v'_e$.
+in $V \subseteq N$.  
+The edge $e$ is directed towards $v_e$, if $\pi(v_e) > \pi(v'_e)$, 
+and otherwise it is directed towards $v'_e$.
 %
@@
 
+\subsection*{Discussion About the Orientation Phase}
+We now discuss the orientation phase and propose a different method to apply 
+an orientation to an undirected graph.
+While the proposed method does not surpass the trivial orientation in the worse case, 
+in certain cases, the new method yields an exponential improvement over the trivial one.
+
+The orientation works as follow:
+given an undirected graph $G = (V, E)$ we first find its block tree 
+(where every vertex in the tree is a maximal subgraph of $G$ without a cut-vertex),
+then, on the unique  path from $s$ to $t$ we internally orient each block arbitrarily to
+produce a DAG.
+Note that if $B_1, \ldots, B_k$ are the blocks of $G$ on the path from $s$ to $t$ then
+the first and last vertices w.r.t to each block are known and only the order
+of the internal neighborly vertices in each block is needed to be determined,
+thus, we can find all relevant orientations by repeating the process above
+$\Pi_{i = 1}^k n(B_i)$ times, where $n(B_i)$ is the number of internal neighborly vertices
+in $B_i$.
+
+\begin{theorem}
+There is an FPT algorithm that finds a $(1+\eps)$-approximate placement after
+$\Pi_{i = 1}^k n(B_i)$ iterations.
+\end{theorem}
+
+Figure~\ref{fig:or2} shows that in some cases this approach is faster than the trivial one.
+We also note that if the given graph is a cactus graph then using this approach result in 
+a polynomial algorithm.
+This special case of cactus graph was already considered in \cite{Stefan} and was also found
+as a special case for which a hard problem becomes tractable.
+
+\begin{theorem}
+There is a polynomial algorithm that finds a $(1+\eps)$-approximate placement 
+for cactus graph.
+\end{theorem}
+
+\begin{figure}
+\begin{center}
+\input{fig-or2}
+\end{center}
+\caption{
+A undirected graph with its block marked in a dashed, green lines.
+In this instance, using the trivial approach the orientation phase takes 16! iterations,
+while using the second approach we only need 3! iterations.
+\label{fig:or2}
+}
+\end{figure}   
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-01-07 src/chain.tex
merge camera ready

@@
 On the other hand, we present an FPTAS for the case where the network
-is a DAG.  In addition, based on our FPTAS, we provide a randomized
-algorithm for instances in which the service chain passes through a
+is a DAG.  In addition, based on our FPTAS, we provide randomized
+algorithms for instances in which the service chain passes through a
 bounded number of vertices whose degree is larger than two.
@@
 neighbors.
-%In this section
-We assume that there exists an optimal placement whose physical path
-consists of at most $k$ neighborly vertices.  
-For example, this can be assumed if all simple paths from $s$ to $t$ contain at most $k$
-neighborly vertices.
-%
-We present a randomized algorithm that consists of $k!$ iterations of
-the following two phases: an orientation phase that applies a random
+%
+First, we assume that there exists an optimal placement whose physical
+path consists of at most $k$ neighborly vertices.  For example, this
+can be assumed if all simple paths from $s$ to $t$ contain at most $k$
+neighborly vertices.  In this case we present a randomized algorithm
+that computes an $(1+\eps)$-approximate placement with high
+probability whose running time is $O(k! \cdot \text{poly}(n))$.
+%
+Our second algorithm works under the stronger assumption that there
+are $k$ neighborly vertices in the network.  In this case, we present
+a deterministic algorithm whose running time is $O(k! \cdot
+\text{poly}(n))$.
+
+%%%%%
+
+Our randomized algorithm consists of $k!$ iterations of the
+following two phases: an orientation phase that applies a random
 orientation to the physical network, and an execution of the FPTAS for
-DAGs given in Theorem~\ref{thm:fptas}.  
-The algorithm finds a $(1-\eps)$-approximate placement with probability $(1-1/e)$, 
-and its running time of the algorithm is $O(t(n)k!)$, 
-where $t(n)$ is the time it takes to compute a placement when 
-the physical network is a DAG.
+DAGs given in Theorem~\ref{thm:fptas}.  The algorithm finds a
+$(1-\eps)$-approximate placement with probability $(1-1/e)$, and the
+running time of the algorithm is $O((n+t(n))k!)$, where $t(n)$ is the
+time it takes to compute a placement when the physical network is a
+DAG.
 %
@@
 \begin{theorem}
-With probability at least $1 - e^{-1}$ the algorithm finds a
-$(1+\eps)$-approximate placement after $k!$ iterations.
+There exists an algorithm, that given an \scp instance with an optimal
+solution that contains at most $k$ neighborly vertices, finds a
+$(1+\eps)$-approximate placement with high probability, whose
+running time is $O(k! \cdot \text{\rm poly}(n))$.
 \end{theorem}
@@
 \end{proof}
+
+In the case where $\abs{N} = k$ we can simply examine the $k!$
+permutations of the neighborly vertices.  For each possible
+permutation the algorithm applies the graph orientation procedure as
+described above, and then executes the FPTAS for DAGs given in
+Section~\ref{sub:fptas}.  
+Thus the running time of the algorithm is $O(k! \cdot \text{\rm poly}(n))$.
+%
+We note that permutation enumeration for $k$ numbers takes $O(k!)$
+time (see e.g.,~\cite{Even73,Sedgewick77})
+
+\begin{theorem}
+There exists an $O(k! \cdot \text{\rm poly}(n))$-time algorithm, that
+given an \scp instance with $k$ neighborly vertices, finds a
+$(1+\eps)$-approximate placement.
+\end{theorem}
 

### 2018-01-07 src/chain.tex
fix

@@
 Given a network that contains servers with limited processing power
-and of links with limited bandwidth, a service chain is a sequence of
-virtual network functions (VNFs) that service a certain flow request
+and links with limited bandwidth, a service chain is a sequence of
+virtual network functions (VNFs) that serve a certain flow request
 in the network.
@@
 the algorithmic aspects of such networks but mainly present heuristics
-(see, e.g,~\cite{SBMPKSF14}).  For more details see~\cite{ERS16} and
-references therein.
+(see, e.g,~\cite{soule2014merlin}).  
+For more details see~\cite{ERS16} and references therein.
 
@@
 (physical) network that contains servers with limited (residual)
-processing power and of links with limited (residual) bandwidth.
+processing power and links with limited (residual) bandwidth.
 %
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{FPT Algorithms for General Networks}
+We now propose an FPT algorithm for general networks that is similar to the randomized 
+algorithm from Section~\ref{sec:general}.
+Our FPT algorithm runs in $O(k! \cdot (A + O))$ where $k$ is the number of neighborly
+vertices in the graph, $A$ is the time required to find a solution on a DAG,
+and $O$ is the time required to orient the graph given a permutation on the neighborly
+vertices, as discussed above.
+The algorithm executes the FPTAS for DAGs given in Theorem~\ref{thm:fptas}
+once for any orientation results from any of the $k!$ possible permutations and
+returns the best solution.
+The following theorem follows immediately.
+
+\begin{theorem}
+There is an FPT algorithm that finds a $(1+\eps)$-approximate placement after $k!$ iterations 
+\end{theorem}
+
 \subsection*{Discussion About the Orientation Phase}
@@
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{FPT Algorithm for General Networks}
-We now propose an FPT algorithm for general networks that is similar to the randomized 
-algorithm from Section~\ref{sec:general}.
-Our FPT algorithm runs in $O(k! \cdot (A + O))$ where $k$ is the number of neighborly
-vertices in the graph, $A$ is the time required to find a solution on a DAG,
-and $O$ is the time required to orient the graph given a permutation on the neighborly
-vertices, as discussed above.
-The algorithm executes the FPTAS for DAGs given in Theorem~\ref{thm:fptas}
-once for any orientation results from any of the $k!$ possible permutations and
-returns the best solution.
-The following theorem follows immediately.
-
-\begin{theorem}
-There is an FPT algorithm that finds a $(1+\eps)$-approximate placement after $k!$ iterations 
-\end{theorem}
 

### 2018-01-07 src/chain.tex
fix dp for fault

@@
 Formally, given the input $(G = (V, E), \calG = (\calV, \calE), p, b, s, t, c)$
-We define $ft(v_1, v_2, \alpha_1, \alpha_2)$ to be the optimal 2-robust placement of 2 chains
+We define $ft(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)$ 
+to be the minimum cost of a 2-robust placement of 2 chains
 that start at $\sigma$ and end at $\alpha_1, \alpha_2$ respectively into 
 (internal vertex disjoint) physical paths that start at $s$ and end at $v_1,v_2$ respectively.
+the placement is restricted to place a path of virtual functions from $\beta_1$ to
+$\alpha_1$ and from $\beta_2$ to $\alpha_2$ into a single physical node respectively.
 One can verified that the following recursive formula holds:
@@
 $$
-\begin{array}{l}
+\begin{array}{ll}
 nn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
-\displaystyle\smashoperator{\min_{\substack{\\ u_1, u_2: \\ b(u_1, v_1) \geq b(\gamma_1, \beta_1) \\ b(u_2, v_2) \geq b(\gamma_2, \beta_2)}}}
+\\ &
+\displaystyle\smashoperator{\min_{\substack{\\ u_1, u_2: \\ b(u_1, v_1) \geq 
+b(\gamma_1, \beta_1) \\ b(u_2, v_2) \geq b(\gamma_2, \beta_2)}}}
 ft(u_1, u_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
+%
 \\
 ny(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
+\\ &
 \displaystyle\smashoperator{\min_{
@@
 	}}}
-ft(u_1, u_2, \alpha_1, \gamma_2, \gamma_1\beta_1, \gamma'_2\beta'_2)
+ft(u_1, u_2, \alpha_1, \gamma_2, \gamma_1\beta_1, \gamma'_2\beta'_2) +
+\\ & 
+\cost_{v_2}(\beta_2 \leadsto \alpha_2) 
+%
 \\
 yn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) =
+\\ & 
 \displaystyle\smashoperator{\min_{
@@
 	}}}
-ft(u_1, u_2, \gamma_1, \alpha_2, \gamma'_1\beta'_1, \gamma_2\beta_2)
+ft(u_1, u_2, \gamma_1, \alpha_2, \gamma'_1\beta'_1, \gamma_2\beta_2) + 
+\\ & 
+\cost_{v_1}(\beta_1 \leadsto \alpha_1) 
+%
 \\
 yy(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) =
+\\ & 
 \displaystyle\smashoperator{\min_{
@@
 	}}}
-ft(u_1, u_2, \gamma_1, \gamma_2, \gamma'_1\beta'_1, \gamma'_2\beta'_2)
+ft(u_1, u_2, \gamma_1, \gamma_2, \gamma'_1\beta'_1, \gamma'_2\beta'_2) + 
+\\
+& \cost_{v_1}(\beta_1 \leadsto \alpha_1) + \cost_{v_2}(\beta_2 \leadsto \alpha_2) 
 \end{array}

### 2018-07-22 src/chain.tex
dror

--- 2018-01-07 src/chain.tex
@@
 %\nonstopmode
-%\documentclass[11pt]{article}
-\documentclass[runningheads]{llncs}
+\documentclass[11pt]{article}
+%\documentclass[runningheads]{llncs}
 
 \usepackage{amsmath,amssymb,mathtools}
-%\usepackage{amsthm}
-%\usepackage{fullpage}
+\usepackage{amsthm}
+\usepackage{fullpage}
 \usepackage{xspace}
@@
 \usepackage[final]{hyperref}
-\usepackage{subcaption}
+\usepackage{subfig}
+%\usepackage{subcaption}
 
@@
 \sloppy
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% handy theorems
+
+\newtheorem{lemma}{Lemma}
+\newtheorem{observation}[lemma]{Observation}
+\newtheorem{theorem}{Theorem}
+\newtheorem{definition}{Definition}
+\newtheorem{property}{Property}
+\newtheorem{corollary}{Corollary}
+\newtheorem{proposition}{Proposition}
+
+%\spnewtheorem{observation}{Observation}{\bfseries}{\itshape}
 
@@
 \newcommand{\latency}{\textsc{lat}\xspace}
+\newcommand{\ft}{\textsc{ft}\xspace}
 
@@
 \title{\bf Service Chain Placement in SDNs%
-\thanks{Research supported in part by Network Programming (Neptune)
+\thanks{%
+%
+A preliminary version appeared in the 3rd International Workshop on
+Algorithmic Aspects of Cloud Computing (ALGOCLOUD), 2017.
+%
+Research supported in part by Network Programming (Neptune)
 Consortium, Israel.}
+%
 }
 
-\titlerunning{Service Chain Placement in SDNs}
+%\titlerunning{Service Chain Placement in SDNs}
 
@@
 \author{%
-Gilad Kutiel
+Gilad Kutiel%
+\thanks{Department of Computer Science, Technion, Haifa 32000, Israel.} \\
+{\tt\small gkutiel@cs.technion.ac.il}
 \and
 Dror Rawitz%
-\thanks{Partially supported by the Israel Science Foundation
-  (grant no.~497/14).  }
+\thanks{Faculty of Engineering, Bar Ilan University, Ramt-Gan 52900, Israel. Partially supported by the Israel Science Foundation
+  (grant no.~497/14). } \\
+{\tt\small dror.rawitz@biu.ac.il}
 }
 
-\institute{%
-Department of Computer Science, Technion, Haifa 32000, Israel. \\
-\email{gkutiel@cs.technion.ac.il}
-\and
-Faculty of Engineering, Bar Ilan University, Ramt-Gan 52900, Israel.\\
-\email{dror.rawitz@biu.ac.il}
-}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{titlepage}
 
@@
 On the other hand, we present an FPTAS for the case where the network
-is a DAG.  In addition, based on our FPTAS, we provide randomized
-algorithms for instances in which the service chain passes through a
-bounded number of vertices whose degree is larger than two.
+is a DAG.  In addition, based on our FPTAS, we provide algorithms for
+general instances in which the service chain passes through a bounded
+number of vertices whose degree is larger than two.
+%
+Finally, we provide an FPTAS for a fault-tolerant version of the
+problem.
 \end{abstract}
 
-% Keywords:
-% approximation algorithms,
-% randomized algorithms,
-% network function virtualization,
-% resource allocation,
-% service chaining,
-% software defined network,
-%
+\bigskip
+
+\noindent
+\textbf{Keyworks}:
+approximation algorithms,
+randomized algorithms,
+network function virtualization,
+resource allocation,
+service chaining,
+software defined network.
+
+\renewcommand{\thepage}{}
+\end{titlepage}
+\pagenumbering{arabic}
 
@@
 compound service that consists of a sequence of VNFs.  Furthermore,
-one may offer a compound service a service that may be obtained using
-one of several sequences of VNFs.
+one may offer a compound service that may be obtained using one of
+several sequences of VNFs.
 
@@
 the networking community, especially from a systems point of view
-(see, e.g.,~\cite{GVPGKDA14,HVSBFTF15}).  Several papers also consider
-the algorithmic aspects of such networks but mainly present heuristics
-(see, e.g,~\cite{soule2014merlin}).  
-For more details see~\cite{ERS16} and references therein.
+(see, e.g.,~\cite{GVPGKDA14,HVSBFTF15}).  Several papers also
+considered the algorithmic aspects of such networks but mainly
+presented heuristics (see, e.g,~\cite{soule2014merlin}).  For more
+details see~\cite{ERS16} and references therein.
 
@@
 
+Foerster, Parham abd Schmid~\cite{FPS17} considered the
+\textsc{Bidirectional Waypoint Routing} problem, where the input
+consists of a graph $G = (V,E)$ with edge weights and capacities, a
+source $s$, a destination $t$, and a subset of the vertices $W$.  A
+feasible solution is a route from $s$ to $t$ that visits the vertices
+in $W$.  If $W$ is ordered, the route should visit the vertices of $W$
+according to the given order.  The goal is to find a minimum weight
+solution.
+%
+Foerster et al.~\cite{FPS17} showed that the unordered
+problem has no PTAS, assuming P$\neq$NP and gave a
+$1.53$-approximation algorithm.  They also presented polynomial time
+algorithms for special cases.
+%
+As for the ordered variant, they showed that feasible routes can be
+computed efficiently if $\abs{W} = O(1)$.  In addition, they showed
+that the problem is NP-hard and gave a polynomial time algorithm for
+cactus graphs with constant link capacities.
+
 %%%%%
@@
 computes a $(1+\eps)$-approximate placement in time $O(k! \cdot
-\text{poly}(n))$, where $k$ is the number of vertices in the network
-whose degree is larger than $2$.
+\text{poly}(n))$, where the parameter $k$ is the number of vertices in
+the network whose degree is larger than $2$.
+%
+We note that there are special cases (e.g., cactus graphs) in which
+the running time of the algorithm becomes polynomial.
+%
+Finally, we provide an FPTAS for a fault-tolerant version of the
+service chain placement problem (without latency) in which two
+virtuals paths are placed in two vertex joint paths.
 
@@
 
-\subsection*{Model.}
+We foramlly define the problem in this section.
+
+%%%%
+
+\subsection{Model}
 %
@@
 \centering
-\scalebox{0.85}{
+\scalebox{0.9}{
 \input{fig-embedding}
@@
 
-\subsection*{Notation.}
+\subsection{Notation}
 %
@@
 Hamiltonian path.
-%
-\qed
 \end{proof}
@@
 is $\half \sum_i a_i$.
-%
-\qed
 \end{proof}
@@
 only if there is a placement with cost $\half \sum_i^n a_i$.
-%
-\qed
 \end{proof}
@@
 \subsection{Placing a Service Chain}
+\label{sec:chain-placement}
 
@@
 \infty  &  c < 0,\\
-0       &
-\begin{array}{c}
-\alpha = \sigma, v = s, \\
-\text{and } c \geq 0,
-\end{array} \\
+0       & \alpha = \sigma, v = s, \text{and } c \geq 0, \\
 \displaystyle
@@
 respect to $c'$.
-%
-\qed
 \end{proof}
@@
 size and in $1/\eps$.
-%
-\qed
 \end{proof}
@@
 In this section we consider \scp when the physical network is an
-undirected graph.  
-Recall that even the feasibility version of \scp is NP-hard in general networks,
-and therefore we focus on a special case.
+undirected graph.  Recall that even the feasibility version of \scp is
+NP-hard in general networks, and therefore we focus on a special case.
 %
@@
 
-Our randomized algorithm consists of $k!$ iterations of the
-following two phases: an orientation phase that applies a random
-orientation to the physical network, and an execution of the FPTAS for
-DAGs given in Theorem~\ref{thm:fptas}.  The algorithm finds a
-$(1-\eps)$-approximate placement with probability $(1-1/e)$, and the
-running time of the algorithm is $O((n+t(n))k!)$, where $t(n)$ is the
-time it takes to compute a placement when the physical network is a
-DAG.
+\subsection{Randomized Algorithm}
+
+Our randomized algorithm consists of $k!$ iterations of the following
+two phases: an orientation phase that applies a random orientation to
+the physical network, and an execution of the FPTAS for DAGs given in
+Theorem~\ref{thm:fptas}.  The algorithm finds a $(1+\eps)$-approximate
+placement with probability $(1-1/e)$, and the running time of the
+algorithm is $O((n+t(n))k!)$, where $t(n)$ is the time it takes to
+compute a placement when the physical network is a DAG.
 %
@@
 
-The orientation phase is done as follows: 
-let $N$ be the set of neighborly vertices, 
-and let $\pi:N \to \set{1,\ldots,\abs{N}}$ be a random permutation.  
-We direct the edges according to $\pi$.  
-Observe that each edge $e \in E$ is found on a simple path between two
-neighborly nodes $v_e$ and $v'_e$, in which all internal vertices are
-in $V \subseteq N$.  
-The edge $e$ is directed towards $v_e$, if $\pi(v_e) > \pi(v'_e)$, 
-and otherwise it is directed towards $v'_e$.
+The orientation phase is done as follows.  Let $N$ be the set of
+neighborly vertices.  We assume without loss of generality that $N =
+\set{1,\ldots,\abs{N}}$.
+%
+Let $\pi:N \to N$ be a random permutation.  We direct the edges
+according to $\pi$.  Observe that each edge $e \in E$ is found on a
+simple path between two neighborly nodes $v_e$ and $v'_e$, in which
+all internal vertices are in $V \setminus N$.  The edge $e$ is
+directed towards $v_e$, if $\pi(v_e) > \pi(v'_e)$, and otherwise it is
+directed towards $v'_e$.
 %
@@
 $G_\pi$, where there is a topological order than is consistent which
-$\pi$.  Figure~\ref{fig:orientation} depicts the orientation stage.
+$\pi$.  Figure~\ref{fig:orientation} depicts the orientation phase.
 %
@@
 \caption{Orientation phase: on the left is the physical network, where
-  only the heavy nodes are drawn.  The numbers represent the
+  only the neighborly nodes are drawn.  The numbers represent the
   permutation and the dashed path represents a path of an optimal
@@
   enough that the internal ordering of the nodes on the dashed path is
-  "correct" to ensure that the survival of the optimal placement. }
+  "correct" to ensure the survival of an optimal placement. }
 \label{fig:orientation}
@@
 probability to $1 - \inv{n}$ using $\log n$ repetitions.
-%
-\qed
 \end{proof}
+
+%%%%%
+
+\subsection{Fixed Parameter Algorithm}
 
@@
 We note that permutation enumeration for $k$ numbers takes $O(k!)$
-time (see e.g.,~\cite{Even73,Sedgewick77})
+time (see e.g.,~\cite{Even73,Sedgewick77}).
+%
+The result is a fixed parameter approximation algorithm, where the
+parameter is the number of neighborly vertices.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{FPT Algorithms for General Networks}
-We now propose an FPT algorithm for general networks that is similar to the randomized 
-algorithm from Section~\ref{sec:general}.
-Our FPT algorithm runs in $O(k! \cdot (A + O))$ where $k$ is the number of neighborly
-vertices in the graph, $A$ is the time required to find a solution on a DAG,
-and $O$ is the time required to orient the graph given a permutation on the neighborly
-vertices, as discussed above.
-The algorithm executes the FPTAS for DAGs given in Theorem~\ref{thm:fptas}
-once for any orientation results from any of the $k!$ possible permutations and
-returns the best solution.
-The following theorem follows immediately.
-
-\begin{theorem}
-There is an FPT algorithm that finds a $(1+\eps)$-approximate placement after $k!$ iterations 
-\end{theorem}
-
-\subsection*{Discussion About the Orientation Phase}
-We now discuss the orientation phase and propose a different method to apply 
-an orientation to an undirected graph.
-While the proposed method does not surpass the trivial orientation in the worse case, 
-in certain cases, the new method yields an exponential improvement over the trivial one.
-
-The orientation works as follow:
-given an undirected graph $G = (V, E)$ we first find its block tree 
-(where every vertex in the tree is a maximal subgraph of $G$ without a cut-vertex),
-then, on the unique  path from $s$ to $t$ we internally orient each block arbitrarily to
-produce a DAG.
-Note that if $B_1, \ldots, B_k$ are the blocks of $G$ on the path from $s$ to $t$ then
-the first and last vertices w.r.t to each block are known and only the order
-of the internal neighborly vertices in each block is needed to be determined,
-thus, we can find all relevant orientations by repeating the process above
-$\Pi_{i = 1}^k n(B_i)$ times, where $n(B_i)$ is the number of internal neighborly vertices
-in $B_i$.
-
-\begin{theorem}
-There is an FPT algorithm that finds a $(1+\eps)$-approximate placement after
-$\Pi_{i = 1}^k n(B_i)$ iterations.
-\end{theorem}
-
-Figure~\ref{fig:or2} shows that in some cases this approach is faster than the trivial one.
-We also note that if the given graph is a cactus graph then using this approach result in 
-a polynomial algorithm.
-This special case of cactus graph was already considered in \cite{Stefan} and was also found
-as a special case for which a hard problem becomes tractable.
-
-\begin{theorem}
-There is a polynomial algorithm that finds a $(1+\eps)$-approximate placement 
-for cactus graph.
-\end{theorem}
-
-\begin{figure}
+Next we show that there are graphs for which the running time can be
+decreased.  More specifically, we propose a different method to apply
+an orientation to an undirected graph.  While the proposed method does
+not surpass the above mentioned orientation in the worse case, in
+certain cases, the new method yields an exponential improvement.
+
+The orientation works as follow.  Given an undirected graph $G =
+(V,E)$, we first compute its \emph{block-cut} tree.  (Recall that
+every vertex in the block tree is a maximal subgraph of $G$ without a
+cut-vertex.)  Computing such a tree can be done in linear
+time~\cite{HopcroftTarjan73}.
+%
+Then on the unique path from $s$ to $t$ in the block-cut tree we
+internally orient each block arbitrarily to produce a DAG.  Note that
+if $B_1, \ldots, B_\ell$ are the blocks of $G$ on the path from $s$ to
+$t$ then the first and last vertices with respect to each block are
+known and only the order of the internal neighborly vertices in each
+block is needed to be determined, thus, we can find all relevant
+orientations by repeating the process above $\Pi_{i = 1}^\ell
+\abs{N_i}$ times, where $N_i$ is the set of internal neighborly
+vertices in $B_i$.  See example in Figure~\ref{fig:or2}.
+
+\begin{figure}[t]
 \begin{center}
@@
 \end{center}
-\caption{
-A undirected graph with its block marked in a dashed, green lines.
-In this instance, using the trivial approach the orientation phase takes 16! iterations,
-while using the second approach we only need 3! iterations.
+\caption{An undirected graph whose blocks on the way from $s$ to $t$
+  marked in a dashed, green lines.
 \label{fig:or2}
@@
 
+This leads to the following result.
+
+\begin{theorem}
+There exists an $O(\Pi_{i = 1}^k \abs{N_i} \cdot \text{\rm
+  poly}(n))$-time algorithm, that given an \scp instance, computes a
+$(1+\eps)$-approximate placement.
+\end{theorem}
+
+We also note that if the given graph is a cactus graph then there is
+only one possible orientation, and thus this approach results in a
+polynomial time algorithm.
+
+\begin{theorem}
+There exists a polynomial-time algorithm, that given an \scp instance
+where the network is a cactus graph, computes a $(1+\eps)$-approximate
+placement.
+\end{theorem}
+
+We note that cactus graphs were also considered in~\cite{FPS17}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Fault Tolerance}
-In this section we consider the problem of a service chain placement when there 
-is also demand for fault tolerance.
-Formally, given a physical network, a virtual specification and a parameter 
-$\phi \in \mathbb{N}$, a $\phi$-robust placement is a collection of $\phi$ placements,
-$f_1,\ldots,f_\phi$,
-that correspond to $\phi$ internal vertex disjoint physical paths. 
-We are looking for a $\phi$-robust placement that minimize the total cost:
-$$
-\sum_{i = 1}^\phi \sum_j c(\alpha_j,f_i(\alpha_j))
-$$
-In this section we discuss how to efficiently find an optimal 
-(assuming integral polynomial bounded costs) 2-robust placement.
-The algorithm presented here, however, can be generalized to find an optimal $\phi$-robust
-placement for any $\phi$
-
-\subsection{Failure of the Greedy Algorithm}
-Here we give a simple example why the greedy algorithm fails badly.
-By greedy we mean applying the previous algorithm once to find an optimal placement, 
-then removing all the vertices from the resulted path and applying the same algorithm again
-to find the second placement.
-Consider the physical graph as described in Figure~\ref{fig:greedy-bad} and a virtual path of
-two virtual functions $\alpha$ and $\beta$.
-Assume latencies, bandwidth, and processing constraints are all negligible 
-and assume the following cost function 
-$c(1, \alpha) = c(2, \alpha) = 1-\varepsilon, c(1, \beta) = c(2, \alpha) = 1$.
-The greedy algorithm is unable to find a 2-robust placement in this case - after the 
-first iteration there is no path from $s$ to $t$ - while, clearly there is a 2-robust
-placement that costs $4 - 2 \epsilon$.   
-\begin{figure}
-\caption{
-\label{fig:greedy-bad}
-}
+
+In this section we consider the problem of a \textsc{Service Chain
+  Placement} when there is also a demand for fault tolerance.  Note
+that we consider the problem without latency.
+
+Formally, given a physical network, a virtual specification, and a
+parameter $r \in \naturals$, an \emph{$r$-robust} placement is a
+collection of $r$ placements, $f_1,\ldots,f_r$, that correspond to $r$
+internal vertex disjoint physical paths.  In the fault tolerant
+version of \scp we are given $r$ costs functions $c_1,\ldots,c_r$, and
+we are looking for an $r$-robust placement that minimize the total
+cost:
+\[
+\sum_{i=1}^r c_i(f_i) = \sum_{i = 1}^r \sum_j c_i(\alpha_j,f_i(\alpha_j))
+~.
+\]
+We refer to this problem as $r$-robust \scp.
+%
+The motivation for using different costs functions is that it may be
+the case that the first placement is the primal placement that may be
+replaced by one of the other placements in case of a malfunction along
+the physical path that is used by $f_1$.  Hence, the cost function
+$c_2$ may take into account the probability of using the placement
+$f_2$.
+
+In this section we study the problem of efficiently finding an optimal
+2-robust placement.  As in Section~\ref{sec:algorithms} we obtain an
+FPTAS by first assuming that costs are polynomially bounded.  We note
+that the algorithm presented here can be generalized to find an
+optimal $r$-robust placement for any constant $r$.
+
+Before presenting our algorithm, we show that using the algorithm from
+Section~\ref{sec:algorithms} repeatedly, $r$ times, may result in
+failure.  In this approach, we find an optimal placement with respect
+to $c_i$ and then remove all the vertices that are used by the
+computed placement, before computing an optimal placement with respect
+to $c_{i+1}$.
+%
+Consider the following example.  The network, source, and destination
+are depicted in Figure~\ref{fig:greedy-bad}.  The virtual DAG is a
+path consisting of two virtual functions $\alpha$ and $\beta$.  Assume
+that the latencies, bandwidths, and processing time of the request are
+negligible.  Also, assume that $c_1(1, \alpha) = c_1(2,\beta) =
+1-\eps$ and $c_1(1, \beta) = c_1(2, \alpha) = 1$.
+%
+The above algorithm is unable to find a 2-robust placement in this
+case.  After the first iteration there is no path from $s$ to $t$,
+although there is a 2-robust placement that costs $4 - 2 \eps$.
+
+\begin{figure}[t]
 \begin{center}
@@
 \end{center}
+\caption{An example of a network, source, and destination.}
+\label{fig:greedy-bad}
 \end{figure}
 
-\subsection{Fault Tolerance on Layered Graph}
-We first assume that the input graph is a directed layered graph, i.e.
-$G = (\bigcup_{i = 1}^l L_i, A)$ where 
-$A \subseteq \bigcup_{i = 1}^{l - 1} L_i \times L_{i+1}$.
-We assume that the number of vertices in each layer is at least two, or otherwise a 2-robust 
-placement does not exist.
-The algorithm uses dynamic programming.
-We find the optimal 2-robust placement for every  
-combination of two physical vertices from the same layer, 
-and every combination of two virtual functions.
-Formally, given the input $(G = (V, E), \calG = (\calV, \calE), p, b, s, t, c)$
-We define $ft(v_1, v_2, \alpha_1, \alpha_2)$ to be the optimal 2-robust placement of 2 chains
-that start at $\sigma$ and end at $\alpha_1, \alpha_2$ respectively into 
-(internal vertex disjoint) physical paths that start at $s$ and end at $v_1,v_2$ respectively.
-One can verified that the following recursive formula holds:
-$$
-ft(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = \min
-\begin{cases}
-nn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
-\\
-ny(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
-\\
-yn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
-\\
-yy(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) 
-\end{cases}
-$$
-
-where
-$$
-\begin{array}{l}
-nn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
-\displaystyle\smashoperator{\min_{\substack{\\ u_1, u_2: \\ b(u_1, v_1) \geq b(\gamma_1, \beta_1) \\ b(u_2, v_2) \geq b(\gamma_2, \beta_2)}}}
-ft(u_1, u_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
-\\
-ny(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
-\displaystyle\smashoperator{\min_{
-	\substack{
-	u_1, u_2: 
-	\\ 
-	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
-	\\ 
-	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
-	\\
-	\gamma'_2\beta'_2 \in \calE:
-	\\
-	\beta'_2 \prec \gamma_2 
-	}}}
-ft(u_1, u_2, \alpha_1, \gamma_2, \gamma_1\beta_1, \gamma'_2\beta'_2)
-\\
-yn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
-\displaystyle\smashoperator{\min_{
-	\substack{
-	u_1, u_2: 
-	\\ 
-	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
-	\\ 
-	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
-	\\
-	\gamma'_1\beta'_1 \in \calE:
-	\\
-	\beta'_1 \prec \gamma_1 
-	}}}
-ft(u_1, u_2, \gamma_1, \alpha_2, \gamma'_1\beta'_1, \gamma_2\beta_2)
-\\
-yy(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
-\displaystyle\smashoperator{\min_{
-	\substack{
-	u_1, u_2: 
-	\\ 
-	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
-	\\ 
-	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
-	\\
-	\gamma'_1\beta'_1, \gamma'_2\beta'_2 \in \calE:
-	\\
-	\beta'_1 \prec \gamma_1, \beta'_2 \prec \gamma_2 
-	}}}
-ft(u_1, u_2, \gamma_1, \gamma_2, \gamma'_1\beta'_1, \gamma'_2\beta'_2)
-\end{array}
-$$
-
-\begin{theorem}
-There is an algorithm that, on a layered graph, finds an optimal 2-robust placement in 
-polynomial time. 
-\end{theorem}
-
-\begin{proof}
-One can verify, that using dynamic programming, the above recursive can be solved in polynomial time,
-using backtracking we can also find the optimal solution.
-\end{proof}
-
-We note that the above algorithm does not take into account the latency constraint.
-It is possible, however, given a latency constraint, $L$, to modify the algorithm to return
-an optimal solution such that the total latency of the two placements is no more than $2L$.
-Such a solution is guaranteed to be optimal in terms of costs.
-It is also easy to see that in such solution at least one of the placements has lower latency 
-than $L$ and the other one has latency that is at most $2L$.
+%%%%%
 
 \subsection{Layered Graph Transformation}
-Given a directed acyclic graph $G = (V, A)$, 
-and let $\pi:V \to [n]$ be an arbitrary topological sorting of $G$ 
-we transform it into a layered graph $G'$ by replacing every edge $(u, v)$ with a directed path of 
-length (number of arcs) $\pi(v) - \pi(u)$ from $u$ to $v$.
-We set the processing capacity of each internal vertex on this path to be zero,
-and the bandwidth of the arcs along the path to be $b(u,v)$.
-It is easy to see that the resulting graph is indeed a layered graph and that every placement
-on $G$ corresponds to a placement on $G'$ with the same cost.
-Figure~\ref{fig:layer-transform} depicts this process.
-\begin{figure}
-\captionsetup{singlelinecheck=off}
-\caption[layered]{foo
-\label{fig:layer-transform}
-\begin{enumerate}
-\item A directed acyclic graph that is not a layered graph
-  \item A topological sorting of the above graph
-  \item A layered graph obtained by replacing crossing arcs with simple paths 
-\end{enumerate}}
+
+As a first step the input DAG is transformed into a \emph{layered
+  graph}.
+%
+A directed acyclic graph $G = (V,E)$ is called \emph{layered} if there
+is a mapping $h:V \to \naturals$, such that if $(v,u) \in E$ then
+$h(u) = h(v) + 1$.  That is, each vertex $v$ belongs to the layer
+$h(v)$, and each edge goes from one layer to the next.
+%
+We denote the $i$th layer by $L_i$, i.e., $L_i = \set{v : h(v) = i}$.
+In a layer DAG we have that $E \subseteq \bigcup_i (L_i \times
+L_{i+1})$.
+
+Given a directed acyclic graph $G = (V,E)$, let $\pi:V \to [n]$ be an
+arbitrary topological ordering of the vertices in $G$.  We transform
+$G$ into a layered DAG $G'$ by replacing every edge $(v,u) \in E$ with
+a directed path of length (number of edges) $\pi(u) - \pi(v)$ from $u$
+to $v$.
+%
+Figure~\ref{fig:layer-transform}.  depicts this process.  It is
+straightforward to see that the resulting graph $G'$ is indeed a
+layered DAG.
+
+\begin{figure}[t]
 \begin{center}
@@
 \end{center}
+\caption{A layered graph, a topological ordering, and the resulting
+  layered graph.}
+\label{fig:layer-transform}
 \end{figure}
 
+We set the processing capacity of each internal vertex along a path
+that was added to be zero, and the bandwidth of the arcs along the
+path to be $b(v,u)$.  Observe that the transformation can be done in
+polynomial time and that every placement on $G$ corresponds to a
+placement on $G'$ with the same cost, and vice versa.
+
+%%%%%
+
+\subsection{Fault Tolerance on Layered Graphs}
+
+In this section we assume that the input graph is a layered graph,
+i.e., $G = (\bigcup_{i = 1}^\ell L_i, E)$, where $E \subseteq
+\bigcup_{i = 1}^{\ell - 1} (L_i \times L_{i+1})$.  We assume that the
+number of vertices in each layer is at least two, or otherwise a
+$2$-robust placement does not exist.
+%
+Also, we add a dummy virtual edge $(\tau,\tau')$ to the virtual graph
+$\calG$, where $p(\tau')=0$ and $c(\tau',v) = \infty$ for every $v
+\neq t$.
+
+The algorithm uses dynamic programming.  We find the optimal 2-robust
+placement for every combination of two physical vertices from the same
+layer, and every combination of two virtual edges.
+%
+Formally, we define $\ft((\alpha_1,\zeta_1), (\alpha_2,\zeta_2), v_1,
+v_2)$ to be the minimum cost 2-robust placement of two service chains
+that start at $\sigma$ and end with the edges $(\alpha_1,\zeta_1)$ and
+$(\alpha_2,\zeta_2)$, respectively, such that a virtual paths from
+$\sigma$ to $\alpha_1$ and $\alpha_2$ are placed into internal vertex
+disjoint physical paths that start at $s$ and end at $v_1$ and $v_2$,
+respectively.
+%
+We remaind that $\cost^i_{v_i}(\gamma_i,\beta_i)$ is the cost, with respect to
+$c_i$, of a minimum cost path from $\gamma_i$ to $\beta_i$ whose total
+processing requirement can be handled by $v_i$.  
+Consider the following recursive definition:
+\[
+\ft((\alpha_1,\zeta_1),(\alpha_2,\zeta_2),s,s)
+= \cost^1_{s}(\sigma \leadsto \alpha_1) + \cost^2_{s}(\sigma \leadsto \alpha_2) 
+\]
+otherwise, for $v_1 \neq v_2$, where $v_1$ and
+$v_2$ in the same layer, we have
+\[
+\ft((\alpha_1,\zeta_1),(\alpha_2,\zeta_2),v_1,v_2)
+=
+\min\set{
+%
+\begin{array}{l}
+\ft((\gamma_1,\beta_1),(\gamma_2,\beta_2),u_1,u_2) \\ 
++ \cost^1_{v_1}(\beta_1 \leadsto \alpha_1) \\
++ \cost^2_{v_2}(\beta_2 \leadsto \alpha_2)
+\end{array}
+}
+\]
+
+Where we take the minimum over all the possible virtual functions and
+physical nodes such that:
+
+\begin{itemize}
+  \item $\gamma_i \preceq \alpha_i$
+  \item $\beta_i \preceq \alpha_i \lor \beta_i = \zeta_i$ 
+  \item $(\gamma_i,\beta_i) \in \calE$
+  \item $u_1 \neq u_2 \lor u_1 = u_2 = s$
+  \item $(u_i,v_i) \in E$
+  \item $b(\gamma_i,\beta_i) \leq b(u_i,v_i)$
+\end{itemize}
+
+The optimal $2$-robust placement is obtained by the call
+$\ft((\tau,\tau'),(\tau,\tau'),t,t)$
+
+The running time is polynomial, since there is a polynomial number of
+states and the computation of $\cost^i_{v_i}(\gamma_i,\beta_i)$ can be
+done in polynomial time, as shown in
+Section~\ref{sec:chain-placement}.  The above algorithm computes the
+cost of an optimal $2$-robust placement, and as usual, one may compute
+an optimal $2$-robust placement using stanard techniques.
+
+sing the same approach as was used in Section~\ref{sub:fptas} we
+obtain the following result.
+
+\begin{theorem}
+There exists an FPTAS for $2$-robust \scp (without latency) in DAGs.
+\end{theorem}
+
+Finally, we note that the above algorithm does not take into account
+the latency constraint.  It is possible, however, given a latency
+constraint, $L$, to modify the algorithm to return an optimal solution
+such that the total latency of the two placements is no more than
+$2L$.  Such a solution is guaranteed to be optimal in terms of costs.
+It is also easy to see that in such solution at least one of the
+placements has lower latency than $L$ and the other one has latency
+that is at most $2L$.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%Fault tolerant placement: two service chains?
-
-%FPT algorithm where the number of servers whose degree is larger than
-%two is a parameter?
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\clearpage
 

### 2018-07-22 src/chain.tex
dror

@@
 %
-Figure~\ref{fig:layer-transform}.  depicts this process.  It is
+Figure~\ref{fig:layer-transform} depicts this process.  It is
 straightforward to see that the resulting graph $G'$ is indeed a
@@
 %
-We remaind that $\cost^i_{v_i}(\gamma_i,\beta_i)$ is the cost, with respect to
-$c_i$, of a minimum cost path from $\gamma_i$ to $\beta_i$ whose total
-processing requirement can be handled by $v_i$.  
-Consider the following recursive definition:
+Recall that $\cost^i_{v_i}(\gamma_i,\beta_i)$ is the cost, with
+respect to $c_i$, of a minimum cost path from $\gamma_i$ to $\beta_i$
+whose total processing requirement can be handled by $v_i$.
+%
+Consider the following recursive definition.  First,
 \[
 \ft((\alpha_1,\zeta_1),(\alpha_2,\zeta_2),s,s)
-= \cost^1_{s}(\sigma \leadsto \alpha_1) + \cost^2_{s}(\sigma \leadsto \alpha_2) 
+= \cost^1_{s}(\sigma \leadsto \alpha_1) +
+  \cost^2_{s}(\sigma \leadsto \alpha_2)
+~.
 \]
-otherwise, for $v_1 \neq v_2$, where $v_1$ and
-$v_2$ in the same layer, we have
+Otherwise, for $v_1 \neq v_2$, such that $v_1, v_2 \in L_i$, for some
+$i$, we have
 \[
@@
 \ft((\gamma_1,\beta_1),(\gamma_2,\beta_2),u_1,u_2) \\ 
-+ \cost^1_{v_1}(\beta_1 \leadsto \alpha_1) \\
-+ \cost^2_{v_2}(\beta_2 \leadsto \alpha_2)
++~ \cost^1_{v_1}(\beta_1 \leadsto \alpha_1) 
++~ \cost^2_{v_2}(\beta_2 \leadsto \alpha_2)
 \end{array}
@@
 \]
-
-Where we take the minimum over all the possible virtual functions and
-physical nodes such that:
-
+where we take the minimum over all the possible virtual functions
+$\gamma_1, \beta_1, \gamma_2, \beta_2$ and physical nodes $u_1, u_2$,
+such that:
 \begin{itemize}
-  \item $\gamma_i \preceq \alpha_i$
-  \item $\beta_i \preceq \alpha_i \lor \beta_i = \zeta_i$ 
-  \item $(\gamma_i,\beta_i) \in \calE$
-  \item $u_1 \neq u_2 \lor u_1 = u_2 = s$
-  \item $(u_i,v_i) \in E$
+  \item $\gamma_i \preceq \alpha_i$,
+  \item $\beta_i \preceq \alpha_i$ or $\beta_i = \zeta_i$,
+  \item $(\gamma_i,\beta_i) \in \calE$,
+  \item $u_1 \neq u_2$ or $u_1 = u_2 = s$,
+  \item $(u_i,v_i) \in E$, and
   \item $b(\gamma_i,\beta_i) \leq b(u_i,v_i)$
@@
 cost of an optimal $2$-robust placement, and as usual, one may compute
-an optimal $2$-robust placement using stanard techniques.
+an optimal $2$-robust placement using standard techniques.
 
@@
 
-\clearpage
-
 \bibliographystyle{abbrv}

### 2019-01-24 src/chain.tex
fix journal

@@
 client.  Hence, a focal issue is a central agent that is able to
-received reports from network components and client requests, and as a
+receive reports from network components and client requests, and as a
 result can alter the allocation of resources in the networks.  This
@@
 
-Foerster, Parham abd Schmid~\cite{FPS17} considered the
+Foerster, Parham and Schmid~\cite{FPS17} considered the
 \textsc{Bidirectional Waypoint Routing} problem, where the input
@@
 service chain placement problem (without latency) in which two
-virtuals paths are placed in two vertex joint paths.
+virtual paths are placed in two vertex joint paths.
 
@@
 
-We foramlly define the problem in this section.
+We formally define the problem in this section.
 
@@
 }
-\caption{An example of an \scp instance and a solution.}
+\caption{
+  An example of an \scp instance and a solution.
+  The left DAG represents the collection of alternative service chains as requested by the client.
+  Each node of this graph represent a single service and the number written inside the node is the processing demand of this service.
+  The value on the arcs are the minimum bandwidth required to transmit the output of one service to the next service.
+  \\
+  The right DAG represents a physical network. 
+  The numbers on the nodes represent processing capacities and the number on the arcs represent the available bandwidth.
+  \\
+  The blue, dashed, arcs represent the chosen service chain and a physical route respectively, and the dotted, purple, arrows show a placement of this service chain into the physical route.
+}
 \label{fig:solution}
@@
 there are two edges $(s,v)$ and $(v,t)$.  The capacity of $v$ is $p(v)
-= \half \sum_i a_i$.  Edge bandwidth are zero.
+= \half \sum_i a_i$.  Edge bandwidths are zero.
 %
@@
 %
-Also, it is not hard to verify that $\set{a_1, \ldots, a_n} \in
-\textsc{Partition}$ if and only if there exists a solution whose cost
-is $\half \sum_i a_i$.
+Note that any service chain is of the form $\sigma, \gamma_1, \dots, \gamma_n, \tau$ where $\gamma_i \in \{\alpha_i, \beta_i\}$. 
+This implies that given a service chain, the sum of its cost and its total processing demand equals to $\sum_i a_i$ and thus (as forced by the processing capacity of $v$), $\set{a_1, \ldots, a_n} \in \textsc{Partition}$ if and only if there exists a solution whose cost is $\half \sum_i a_i$.
 \end{proof}
@@
 %
-One can verify that $a_i$ is either counted in the latency of in the
+One can verify that $a_i$ is either counted in the latency or in the
 cost.  Hence, $\set{a_1, \ldots, a_n} \in \textsc{Partition}$ if and
@@
 bounded.  Our algorithm is similar to the FPTAS for the
-\textsc{Minimum Knapsack} problem.
+\textsc{Minimum Knapsack} problem~\cite{lawler1979fast}.
 
@@
      \sum_{\alpha}
-       \paren{ c(\alpha,f(\alpha)) \cdot \frac{\eps c_{\max}}{n} + 1} \\
+       \paren{ c(\alpha,f(\alpha)) \cdot \frac{n}{\eps c_{\max} + 1}} \\
 %& =    c(f) + \frac{\eps c_{\max}}{n} \cdot n \\
@@
 
+We assume w.l.o.g that the physical network does not contain any leafs (beside, maybe, $s$ and $t$), otherwise, these nodes, for the purpose of our computation, can be safely removed from the network.
+
 Our randomized algorithm consists of $k!$ iterations of the following
@@
 Let $\pi:N \to N$ be a random permutation.  We direct the edges
-according to $\pi$.  Observe that each edge $e \in E$ is found on a
+according to $\pi$.  
+Observe that each edge $e \in E$ is found on a
 simple path between two neighborly nodes $v_e$ and $v'_e$, in which
@@
 the probability that $\pi$ agrees with $\pi'$ in $k!$ iterations is $1
-- (1 - 1/k!)^{k!} \geq 1 - e^{-1}$.  One may amplify the success
-probability to $1 - \inv{n}$ using $\log n$ repetitions.
+- (1 - 1/k!)^{k!} \geq 1 - e^{-1}$.  
+This means that the probability to fail in a single attempt is less than $e^{-1}$.
+If one makes $i$ attempts then the probability to fail in all those attempts is less than $e^{-i}$ so using $\ln n$ repetitions reduces the probability to fail to less than $\frac{1}{n}$ and increases the probability to succeed to at least $1 - \inv{n}$.
 \end{proof}
@@
 
-The orientation works as follow.  Given an undirected graph $G =
-(V,E)$, we first compute its \emph{block-cut} tree.  (Recall that
-every vertex in the block tree is a maximal subgraph of $G$ without a
-cut-vertex.)  Computing such a tree can be done in linear
-time~\cite{HopcroftTarjan73}.
+A biconnected component (block) of an undirected graph is a maximal biconnected subgraph.
+Any connected graph decomposes into a tree of biconnected components called the block-cut tree of the graph. The blocks are attached to each other at shared vertices called cut vertices.
+Computing such a tree can be done in linear time~\cite{HopcroftTarjan73}.
+The orientation works as follow.  
+Given an undirected graph $G = (V,E)$, we first compute its block-cut tree.
 %
@@
 \abs{N_i}$ times, where $N_i$ is the set of internal neighborly
-vertices in $B_i$.  See example in Figure~\ref{fig:or2}.
+vertices in $B_i$.  See Figure~\ref{fig:or2} for an example.
 
@@
 \caption{An undirected graph whose blocks on the way from $s$ to $t$
-  marked in a dashed, green lines.
+  marked in dashed green lines.
 \label{fig:or2}
@@
 
+We say that two (physical) paths are \emph{internal vertex disjoint} if they do not have any internal (all vertices beside the first and last one) vertex in common.
 Formally, given a physical network, a virtual specification, and a
@@
 cost of an optimal $2$-robust placement, and as usual, one may compute
-an optimal $2$-robust placement using standard techniques.
-
-sing the same approach as was used in Section~\ref{sub:fptas} we
+an optimal $2$-robust placement using stanard techniques.
+
+Using the same approach as was used in Section~\ref{sub:fptas} we
 obtain the following result.

### 2019-01-28 src/chain.tex
fix

@@
 
+% FIX
+\newcommand{\fix}[1]{{\color{purple}\textbf{#1}}}
 % DEBUG
@@
 In this paper we consider an SDN network that employs
-NVF~\cite{SDN-NFV15}.  Such networks attracted a lot of attention in
+NFV~\cite{SDN-NFV15}.  Such networks attracted a lot of attention in
 the networking community, especially from a systems point of view
@@
 %
-  Without loss of generality, we assume that $p(s) = p(t) = 0$.
+  % Without loss of generality, we assume that $p(s) = p(t) = 0$.
 
@@
 %
-  Without loss of generality, we assume that $p(s) = p(t) = 0$.  
-%
   The DAG $\calG$ has a source node $\sigma \in \calV$ and a
@@
 %
-  Without loss of generality, we assume that $p(\sigma) = p(\tau) =
+  Without loss of generality, we assume that $p(s) = p(t) = p(\sigma) = p(\tau) =
   0$.  Each edge $\eps \in \calE$ has a bandwidth demand $b(\eps)$.
@@
 }
-\caption{
+\caption{\fix{
   An example of an \scp instance and a solution.
@@
   The blue, dashed, arcs represent the chosen service chain and a physical route respectively, and the dotted, purple, arrows show a placement of this service chain into the physical route.
-}
+}}
 \label{fig:solution}
@@
 %
+\fix{
 Note that any service chain is of the form $\sigma, \gamma_1, \dots, \gamma_n, \tau$ where $\gamma_i \in \{\alpha_i, \beta_i\}$. 
 This implies that given a service chain, the sum of its cost and its total processing demand equals to $\sum_i a_i$ and thus (as forced by the processing capacity of $v$), $\set{a_1, \ldots, a_n} \in \textsc{Partition}$ if and only if there exists a solution whose cost is $\half \sum_i a_i$.
+}
 \end{proof}
@@
 costs, namely without the assumption that costs are polynomially
-bounded.  Our algorithm is similar to the FPTAS for the
-\textsc{Minimum Knapsack} problem~\cite{lawler1979fast}.
+bounded.  
+\fix{
+We use similar techniques as in the  FPTAS for the
+\textsc{Minimum Knapsack} problem~\cite{islam2009approximation}.
+}
 
@@
 possible value of $c_{\max}$, and choose the best placement.
-According to Lemma~\ref{lemma:guess} the best placement is
-$(1+\eps)$-approximate.  The running time is polynomial in the input
-size and in $1/\eps$.
+\fix{Since we check all the possible values of $c_max$ and for each such value we compute an optimal solution with respect to $c'$, then} according to Lemma~\ref{lemma:guess} the best placement is $(1+\eps)$-approximate.
+The running time is polynomial in the input size and in $1/\eps$.
 \end{proof}
@@
 
-We assume w.l.o.g that the physical network does not contain any leafs (beside, maybe, $s$ and $t$), otherwise, these nodes, for the purpose of our computation, can be safely removed from the network.
-
+\fix{We assume w.l.o.g that the physical network does not contain any leafs (beside, maybe, $s$ and $t$), otherwise, these nodes, for the purpose of our computation, can be safely removed from the network.}
 Our randomized algorithm consists of $k!$ iterations of the following
@@
 This means that the probability to fail in a single attempt is less than $e^{-1}$.
-If one makes $i$ attempts then the probability to fail in all those attempts is less than $e^{-i}$ so using $\ln n$ repetitions reduces the probability to fail to less than $\frac{1}{n}$ and increases the probability to succeed to at least $1 - \inv{n}$.
+\fix{If one makes $i$ attempts then the probability to fail in all those attempts is less than $e^{-i}$ so using $\ln n$ repetitions reduces the probability to fail to less than $\frac{1}{n}$ and increases the probability to succeed to at least $1 - \inv{n}$.
+}
 \end{proof}
@@
 
+\fix{
 A biconnected component (block) of an undirected graph is a maximal biconnected subgraph.
@@
 Computing such a tree can be done in linear time~\cite{HopcroftTarjan73}.
+}
 The orientation works as follow.  
@@
 
-We say that two (physical) paths are \emph{internal vertex disjoint} if they do not have any internal (all vertices beside the first and last one) vertex in common.
+\fix{We say that two (physical) paths are \emph{internal vertex disjoint} if they do not have any internal (all vertices beside the first and last one) vertex in common.}
 Formally, given a physical network, a virtual specification, and a
@@
 \]
-Otherwise, for $v_1 \neq v_2$, such that $v_1, v_2 \in L_i$, for some
+Otherwise, for $v_1 \neq v_2$ or $v_1 = v_2 = t$, such that $v_1, v_2 \in L_i$, for some
 $i$, we have

### 2019-03-12 src/chain.tex
all comments

@@
 based on LP-rounding for several special cases.
+%
+\fix{Sahhaf et al.~\cite{SAHHAF2015492} studied a generalization of the Virtual Network Embedding
+Problem where each network function can be decomposed into multiple network function graphs.
+They proposed two novel approaches to use service
+decompositions at the time of service embedding (i) an
+ILP-based algorithm that finds an optimal embedding and (ii) a heuristic-based algorithm to cop with the scalability issues of the first algorithm.}
 
@@
 
+\begin{proof}
+  \fix{From the above discussions it follows that the algorithm finds an optimal robust embedding with respect to c', using Lemma~\ref{lemma:guess} we know that its cost is at most $(1 + \varepsilon)$ times the cost of the optimal robust embedding, for every $\varepsilon > 0$.}
+\end{proof}
+
 Finally, we note that the above algorithm does not take into account
@@
 
+\section{Conclusion}
+\fix{%
+Network service chaining is a service concept which has gained much interest from both practitioners and researchers, it promises increased flexibility and cost-efficiency for future carrier networks.
+In this model clients request high level services from the network provider which translate into a service chain that need to be embedded into the physical network.
+To ensure efficient utilization of the underline physical network relaible algorithms are needed.
+}
+
+\fix{%
+In this paper we propose an efficient algorithm that finds an optimal embedding for a single request.
+This algorithm works, however, only when the underline network is acyclic.
+For general networks we propose an algorithm that finds an optimal embedding with a running time that depends on the topology of the network, more specifically on the number of nodes in the network with more than two connections.
+We also propose a heuristic that improves the running time of the last algorithm, for cactus networks, for example, this heuristic is guaranteed to run in polynomial time.
+}
+
+\fix{%
+Some questions regarding service chain placement remain open. 
+Some of these questions are (i) how should we handle multiple (concurrent) requests?
+(ii) can we find better solutions if we allow embedding a service chain on a walk instead of a path?
+(iii) is there an efficient (approximation) algorithm that works on real world networks?\footnote{As even the feasibilty problem for general networks is NP-hard some further assumptions need to be made in order to answer this question affirmatively.}
+We believe that our results and techniques can serve as a starting point for future work dealing with those questions.
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-03-13 src/chain.tex
fix lemma 1 + bib
elsarticle

@@
-%\nonstopmode
-\documentclass[11pt]{article}
-%\documentclass[runningheads]{llncs}
-
-\usepackage{amsmath,amssymb,mathtools}
-\usepackage{amsthm}
-\usepackage{fullpage}
+\nonstopmode
+\documentclass[preprint,12pt]{elsarticle}
+
+\usepackage{amsmath,amssymb,mathtools,amsthm}
+% \usepackage{fullpage}
 \usepackage{xspace}
-\usepackage{color,soul}
+\usepackage{xcolor}
 \usepackage{paralist}
@@
 
-% \usepackage[linesnumbered, ruled]{algorithm2e}
-
-%\usepackage[final]{microtype}
 \usepackage[final]{hyperref}
 \usepackage{subfig}
-%\usepackage{subcaption}
-
-% FIX
-\newcommand{\fix}[1]{{\color{purple}\textbf{#1}}}
-% DEBUG
-%\usepackage{lipsum}
-%\usepackage{todonotes}
-%\usepackage{lineno}
-%\linenumbers
-
-% EXTRA
-%\usepackage{authblk}
 
@@
 
-\renewcommand{\floatpagefraction}{0.6}
-
-\parskip = \smallskipamount
-
-\sloppy
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% handy theorems
-
-\newtheorem{lemma}{Lemma}
-\newtheorem{observation}[lemma]{Observation}
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{property}{Property}
-\newtheorem{corollary}{Corollary}
-\newtheorem{proposition}{Proposition}
-
-%\spnewtheorem{observation}{Observation}{\bfseries}{\itshape}
+\journal{Discrete Applied Mathematics}
 
@@
 
-\newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}
+% \newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}
 
@@
 
+% handy theorems
+
+\newtheorem{lemma}{Lemma}
+\newtheorem{observation}[lemma]{Observation}
+\newtheorem{theorem}{Theorem}
+\newtheorem{definition}{Definition}
+\newtheorem{property}{Property}
+\newtheorem{corollary}{Corollary}
+\newtheorem{proposition}{Proposition}
+
+% FIX
+\newcommand{\fix}[1]{{\color{violet}\textbf{#1}}}
+
 \begin{document}
-
-\title{\bf Service Chain Placement in SDNs%
-\thanks{%
-%
+\begin{frontmatter}
+
+\title{Service Chain Placement in SDNs\tnoteref{t1}}
+\tnotetext[t1]{
 A preliminary version appeared in the 3rd International Workshop on
@@
 Research supported in part by Network Programming (Neptune)
-Consortium, Israel.}
-%
-}
-
-%\titlerunning{Service Chain Placement in SDNs}
-
-%\author[1]{Gilad Kutiel%
-%\thanks{E-mail: \texttt{gkutiel@cs.technion.ac.il}}}
-
-%\author[2]{Dror Rawitz%
-%\thanks{Partially supported by the Israel Science Foundation
-%  (grant no.~497/14).  E-mail: \texttt{dror.rawitz@biu.ac.il}}}
-
-%\affil[1]{Department of Computer Science, Technion, Haifa, Israel}
-%\affil[2]{Faculty of Engineering, Bar Ilan University, Ramt-Gan, Israel}
-
-\author{%
-Gilad Kutiel%
-\thanks{Department of Computer Science, Technion, Haifa 32000, Israel.} \\
-{\tt\small gkutiel@cs.technion.ac.il}
-\and
-Dror Rawitz%
-\thanks{Faculty of Engineering, Bar Ilan University, Ramt-Gan 52900, Israel. Partially supported by the Israel Science Foundation
-  (grant no.~497/14). } \\
-{\tt\small dror.rawitz@biu.ac.il}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{titlepage}
-
-\maketitle
+Consortium, Israel.
+}
+
+\author{Gilad Kutiel}
+\ead{gkutiel@cs.technion.ac.il}
+\address{Department of Computer Science, Technion, Haifa 32000, Israel.}
+
+\author{Dror Rawitz\fnref{f1}}
+\ead{dror.rawitz@biu.ac.il}
+\address{Faculty of Engineering, Bar Ilan University, Ramt-Gan 52900, Israel.}
+\fntext[f1]{Partially supported by the Israel Science Foundation (grant no.~497/14).}
 
@@
 
-\bigskip
-
-\noindent
-\textbf{Keyworks}:
-approximation algorithms,
-randomized algorithms,
-network function virtualization,
-resource allocation,
-service chaining,
-software defined network.
-
-\renewcommand{\thepage}{}
-\end{titlepage}
-\pagenumbering{arabic}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{keyword}
+approximation algorithms \sep randomized algorithms \sep network function virtualization \sep resource allocation \sep service chaining \sep software defined network.
+
+\end{keyword}
+
+\end{frontmatter}
 
@@
 
-%%%%%
-
 \subsection{Our Results}
@@
 virtual paths are placed in two vertex joint paths.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\begin{figure}[t]
+\begin{figure}[]
 \centering
@@
 
-\begin{figure}[t]
+\begin{figure}[]
   \centering
@@
      \sum_{\alpha}
-       \paren{ c(\alpha,f(\alpha)) \cdot \frac{n}{\eps c_{\max} + 1}} \\
+       \paren{ c(\alpha,f(\alpha)) \cdot \frac{n}{\eps c_{\max}} + 1} \\
 %& =    c(f) + \frac{\eps c_{\max}}{n} \cdot n \\
@@
 possible value of $c_{\max}$, and choose the best placement.
-\fix{Since we check all the possible values of $c_max$ and for each such value we compute an optimal solution with respect to $c'$, then} according to Lemma~\ref{lemma:guess} the best placement is $(1+\eps)$-approximate.
+\fix{Since we check all the possible values of $c_{max}$ and for each such value we compute an optimal solution with respect to $c'$, then} according to Lemma~\ref{lemma:guess} the best placement is $(1+\eps)$-approximate.
 The running time is polynomial in the input size and in $1/\eps$.
@@
 
-\bibliographystyle{abbrv}
+\bibliographystyle{elsarticle-num} 
 \bibliography{chain}
-
 \end{document}

### 2019-03-13 src/chain.tex
fix typos

@@
 %
-  Without loss of generality, we assume that $p(s) = p(t) = p(\sigma) = p(\tau) =
-  0$.  Each edge $\eps \in \calE$ has a bandwidth demand $b(\eps)$.
+\fix{Without loss of generality, we assume that $p(s) = p(t) = p(\sigma) = p(\tau) =
+  0$}.  Each edge $\eps \in \calE$ has a bandwidth demand $b(\eps)$.
 
@@
   The cost function enforces each $\alpha_i$ to be placed either in
-  $v_i^-$ or in $v_i^+$.  In the former case this placement incure no
+  $v_i^-$ or in $v_i^+$.  In the former case this placement incurs no
   cost but additional latency of $a_i$, in the later case there will
@@
 \end{align*}
-where the second inequality is due to the optimality of $f'$ with
+where the second inequality is due to the optimally of $f'$ with
 respect to $c'$.
@@
 Network service chaining is a service concept which has gained much interest from both practitioners and researchers, it promises increased flexibility and cost-efficiency for future carrier networks.
-In this model clients request high level services from the network provider which translate into a service chain that need to be embedded into the physical network.
+In this model clients request compound services from the network provider which translate into a service chain that need to be embedded into the physical network.
 To ensure efficient utilization of the underline physical network relaible algorithms are needed.

### 2019-03-13 src/chain.tex
amiri

@@
 
-Foerster, Parham and Schmid~\cite{FPS17} considered the
-\textsc{Bidirectional Waypoint Routing} problem, where the input
-consists of a graph $G = (V,E)$ with edge weights and capacities, a
-source $s$, a destination $t$, and a subset of the vertices $W$.  A
-feasible solution is a route from $s$ to $t$ that visits the vertices
-in $W$.  If $W$ is ordered, the route should visit the vertices of $W$
-according to the given order.  The goal is to find a minimum weight
-solution.
-%
-Foerster et al.~\cite{FPS17} showed that the unordered
-problem has no PTAS, assuming P$\neq$NP and gave a
-$1.53$-approximation algorithm.  They also presented polynomial time
-algorithms for special cases.
+\fix{Amiri1 et al.~\cite{AmiriLatin2018, AmiriCCR2018, AmiriIFIP2018} considered the \textsc{Waypoint Routing} problem.
+In this problem we are given an edge weighted graph $G=(V, E)$, a source $s \in V$, destination $t \in V$ and a set of waypoints $W \subseteq V$.
+The goal is to find a shortest walk from $s$ to $t$ that traverses all the waypoints.
+Two variants of this problem exists, namely when the waypoints need to be traversed in a particular or in an arbitrary order.
+It is also possible that we have additional capacity consistents, i.e. a limitation on the number of times a walk can go through each edge.
+Amiri1 et al.
+show that (i) There exists a polynomial algorithm for bounded treewidth graph for arbitrary number of waypoints and for general graphs for logarithmically bounded number of waypoints.
+(ii) This problem is NP-hard in general.
+(iii) This problem is NP-hard for directed graphs even when there is a single waypoint.
+(iv) There is a polynomial algorithm for cactus topologies.
+}
+
+% Foerster, Parham and Schmid~\cite{FPS17} considered the
+% \textsc{Bidirectional Waypoint Routing} problem, where the input
+% consists of a graph $G = (V,E)$ with edge weights and capacities, a
+% source $s$, a destination $t$, and a subset of the vertices $W$.  A
+% feasible solution is a route from $s$ to $t$ that visits the vertices
+% in $W$.  If $W$ is ordered, the route should visit the vertices of $W$
+% according to the given order.  The goal is to find a minimum weight
+% solution.
+% %
+% Foerster et al.~\cite{FPS17} showed that the unordered
+% problem has no PTAS, assuming P$\neq$NP and gave a
+% $1.53$-approximation algorithm.  They also presented polynomial time
+% algorithms for special cases.
 %

### 2019-03-13 src/chain.tex
fix bib

@@
 %
-Rost and Schmid~\cite{RostSchmid16} considered variant of this
+Rost and Schmid~\cite{RostSchmid18} considered variant of this
 problem, where each node can host a subset of the VNFs.  In addition,
@@
 
-We note that cactus graphs were also considered in~\cite{FPS17}.
+We note that cactus graphs were also considered in~\cite{RostSchmid18}.
 

### 2019-03-14 src/response.tex
dror

\documentclass[11pt]{article}

\usepackage{amsmath,latexsym,amssymb} 
\usepackage{fullpage,ifthen}
\usepackage{color,soul,colordvi}
\usepackage{mdwlist,paralist}

%\renewcommand{\baselinestretch}{1.02}

%\parskip=\smallskipamount

\sloppy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\ceil}[1]{\left\lceil {#1} \right\rceil}
\newcommand{\floor}[1]{\left\lfloor {#1} \right\rfloor}
\newcommand{\paren}[1]{\left( #1 \right)}
\newcommand{\set}[1]{\left\{ #1 \right\}}

\newcommand{\eps}{\varepsilon}

\newcommand{\calC}{\mathcal{C}}
\newcommand{\sigmad}{\sigma_{\$}}

\newcommand{\ans}[1]{\begin{quotation}{\noindent \sl {#1}}\end{quotation}}

\newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}
\newcommand{\ben}[1]{\sethlcolor{green}\hl{Ben: #1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{\textbf{Service Chain Placement in SDN} \\
  {\Large Response to Reviewers: Submission DA10028}}

\author{Gilad Kutiel \and Dror Rawitz}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We thank the referee for the time that was spent on reviewing our
paper and for their thoughtful comments.  The paper was revised
according to these comments.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\medskip

\section*{Response to Review \#1}

\begin{enumerate}

\item \textbf{Comment}: In Sec.~5.1 for the randomized algorithm it is
  claimed in p.11 row 29, that ``... each edge $e$ in $E$ is found on
  a simple path between two neighborly nodes $v_e$ and $v_{e'}$, in
  which all internal vertices are in $V \ N$''.  $N$ denotes the set
  of neighborly nodes. Here it is not clear for me, how this is ensured
  if, e.g, $G$ is a tree and $N$ is the set of internal nodes with
  degree greater than two.  It needs more explanation. The approach
  described in Sec 5.2 eliminates this problem.

\item[] \textbf{Response}: Before Section 5.1 we observe, that
  w.l.o.g., we may focus on vertices that are located on a path from
  $s$ to $t$.  It follows that each such vertex has degree at least
  $2$.
%
  In Section~5.1 we now consider edges that are located between $s$ or
  $t$ and a neighborly vertex.

\item \textbf{Comment}: In proof of Lemma 1, p.10 row 16: $\leq \eps
  c_{\max} / n \cdot \sum_\alpha (c(\alpha,f(\alpha))\cdot \eps
  c_{max} / n + 1)$ $\longrightarrow$ $\leq \eps c_{\max} / n \cdot
  \sum_\alpha (c(\alpha,f(\alpha))\cdot n / (\eps c_{max}) + 1)$

\item[] \textbf{Response}: Corrected.

\item \textbf{Comment}: In p.~15 row 24: ``... for $v_1 \neq v_2$
  ...'' I suppose, it must be ``... for $v_1 \neq v_2$ or $v_1 = v_2 =
  t$ ...''

\item[] \textbf{Response}: Corrected.

\item \textbf{Comment}: In p.~15 row 34: ``$\beta_i \preceq \alpha_i$
  or $\beta_i = \zeta_i$''.  What does then $\text{COST}^i(\zeta_i \to
  \alpha_i)$ mean in row 26?

\item[] \textbf{Response}: First, we changed $i$ to $j$, since $i$ is
  used for the layer number.

  If $\beta_j = \zeta_j$, then $\textsc{cost}^j_{v_j}(\zeta_j \to
  \alpha_j) = 0$.  We added a footnote about this issue.

\item \textbf{Comment}: In p.~15 after row 37, to my opinion, an
  additional item should be inserted: $v_1 \neq v_2$ or $v_1 = v_2 =
  t$.

\item[] \textbf{Response}: First, this is handled by the response to
  comment 3.  Also, $v_1$ and $v_2$ are not variables over which the
  minimum is taken.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage

\section*{Response to Review \#2}

We corrected all typos in the list.

\subsection*{Additional references/explanations}

\begin{enumerate}

\item \textbf{Comment}: Please expand the explanations for Figure 1,
  the introductory example. For a first-time reader, it is not
  intuitive.

\item[] \textbf{Response}: Done.

\item \textbf{Comment}: Please expand the explanation at the end of
  Theorem 2 a bit.

\item[] \textbf{Response}: Done.

\item \textbf{Comment}: Please provide a reference to the FPTAS for
  the MINIMUM KNAPSACK problem.

\item[] \textbf{Response}: Done.

\item \textbf{Comment}: Please expand the explanation at the end of
  Theorem 5 a bit and/or provide a citation.

\item[] \textbf{Response}: The proof was extended.

\item \textbf{Comment}: Please provide a reference for the block-cut
  tree and expand the explanation a bit.

\item[] \textbf{Response}: Done.

\item \textbf{Comment}: Please expand the proof of Theorem 4, it is a
  bit short at the moment (maybe it is obvious and I don't see it?)

\item[] \textbf{Response}: Done.

\item \textbf{Comment}: Please define internal vertex disjoint on page
  12.

\item[] \textbf{Response}: The definition was added in a footnote.

\item \textbf{Comment}: Please expand the explanation at the end of
  Theorem 9, I don't see it right now.

\item[] \textbf{Response}: The explanations before and after Theorem 9
  were extended.

\item \textbf{Comment}: reference 5 has been extended at TOCS 2018
  (On-Line Path Computation and Function Placement in SDNs)
  https://link.springer.com/article/10.1007/s00224-018-9863-4

\item[] \textbf{Response}: A citation was added.

\item \textbf{Comment}: reference 8 has been extended for the
  unordered case (LATIN 2018 (Walking Through Waypoints):
  https://link.springer.com/chapter/10.1007\%2F978-3-319-77404-6\_4),
  and the ordered case (CCR 2018 (Charting the Algorithmic Complexity
  of Waypoint Routing):
  https://dl.acm.org/citation.cfm?doid=3211852.3211859, and IFIP
  Networking 2018 (Waypoint Routing in Special Networks):
  https://files.ifi.uzh.ch/stiller/IFIP\%20Networking\%202018-Proceedings.pdf).

\item[] \textsc{Response}: The paper are mentioned in the intro.

\item \textbf{Comment}: Lastly, reference 15 has been extended at IFIP
  Networking 2018 as well (see
  https://files.ifi.uzh.ch/stiller/IFIP\%20Networking\%202018-Proceedings.pdf). The
  same authors also presented some prior work in Computer Networks
  (https://www.sciencedirect.com/science/article/abs/pii/S138912861500359X?via\%3Dihub)
  which should be briefly discussed

\item[] \textsc{Response}: The paper are mentioned in the intro.

\item \textbf{Comment}: Please include a small conclusion with open
  questions at the end. For example, how about walks instead of paths?
  How about multiple concurrent requests?

\item[] \text{Response}: Added.

\end{enumerate}

\end{document}

### 2019-03-14 src/chain.tex
dror

--- 2019-03-13 src/chain.tex
@@
-\nonstopmode
-\documentclass[preprint,12pt]{elsarticle}
-
-\usepackage{amsmath,amssymb,mathtools,amsthm}
-% \usepackage{fullpage}
+%\nonstopmode
+\documentclass[11pt]{article}
+%\documentclass[runningheads]{llncs}
+
+\usepackage{amsmath,amssymb,mathtools}
+\usepackage{amsthm}
+\usepackage{fullpage}
 \usepackage{xspace}
-\usepackage{xcolor}
+\usepackage{color,soul}
 \usepackage{paralist}
@@
 
+% \usepackage[linesnumbered, ruled]{algorithm2e}
+
+%\usepackage[final]{microtype}
 \usepackage[final]{hyperref}
 \usepackage{subfig}
+%\usepackage{subcaption}
+
+% DEBUG
+%\usepackage{lipsum}
+%\usepackage{todonotes}
+%\usepackage{lineno}
+%\linenumbers
+
+% EXTRA
+%\usepackage{authblk}
 
@@
 
-\journal{Discrete Applied Mathematics}
+\renewcommand{\floatpagefraction}{0.6}
+
+\parskip = \smallskipamount
+
+\sloppy
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% handy theorems
+
+\newtheorem{lemma}{Lemma}
+\newtheorem{observation}[lemma]{Observation}
+\newtheorem{theorem}{Theorem}
+\newtheorem{definition}{Definition}
+\newtheorem{property}{Property}
+\newtheorem{corollary}{Corollary}
+\newtheorem{proposition}{Proposition}
+
+%\spnewtheorem{observation}{Observation}{\bfseries}{\itshape}
 
@@
 
-% \newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}
+\newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}
 
@@
 
-% handy theorems
-
-\newtheorem{lemma}{Lemma}
-\newtheorem{observation}[lemma]{Observation}
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{property}{Property}
-\newtheorem{corollary}{Corollary}
-\newtheorem{proposition}{Proposition}
-
-% FIX
-\newcommand{\fix}[1]{{\color{violet}\textbf{#1}}}
-
 \begin{document}
-\begin{frontmatter}
-
-\title{Service Chain Placement in SDNs\tnoteref{t1}}
-\tnotetext[t1]{
+
+\title{\bf Service Chain Placement in SDNs%
+\thanks{%
+%
 A preliminary version appeared in the 3rd International Workshop on
@@
 Research supported in part by Network Programming (Neptune)
-Consortium, Israel.
+Consortium, Israel.}
+%
 }
 
-\author{Gilad Kutiel}
-\ead{gkutiel@cs.technion.ac.il}
-\address{Department of Computer Science, Technion, Haifa 32000, Israel.}
-
-\author{Dror Rawitz\fnref{f1}}
-\ead{dror.rawitz@biu.ac.il}
-\address{Faculty of Engineering, Bar Ilan University, Ramt-Gan 52900, Israel.}
-\fntext[f1]{Partially supported by the Israel Science Foundation (grant no.~497/14).}
+%\titlerunning{Service Chain Placement in SDNs}
+
+%\author[1]{Gilad Kutiel%
+%\thanks{E-mail: \texttt{gkutiel@cs.technion.ac.il}}}
+
+%\author[2]{Dror Rawitz%
+%\thanks{Partially supported by the Israel Science Foundation
+%  (grant no.~497/14).  E-mail: \texttt{dror.rawitz@biu.ac.il}}}
+
+%\affil[1]{Department of Computer Science, Technion, Haifa, Israel}
+%\affil[2]{Faculty of Engineering, Bar Ilan University, Ramt-Gan, Israel}
+
+\author{%
+Gilad Kutiel%
+\thanks{Department of Computer Science, Technion, Haifa 32000, Israel.} \\
+{\tt\small gkutiel@cs.technion.ac.il}
+\and
+Dror Rawitz%
+\thanks{Faculty of Engineering, Bar Ilan University, Ramt-Gan 52900, Israel. Partially supported by the Israel Science Foundation
+  (grant no.~497/14). } \\
+{\tt\small dror.rawitz@biu.ac.il}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{titlepage}
+
+\maketitle
 
@@
 
-\begin{keyword}
-approximation algorithms \sep randomized algorithms \sep network function virtualization \sep resource allocation \sep service chaining \sep software defined network.
-
-\end{keyword}
-
-\end{frontmatter}
+\bigskip
+
+\noindent
+\textbf{Keyworks}:
+approximation algorithms,
+randomized algorithms,
+network function virtualization,
+resource allocation,
+service chaining,
+software defined network.
+
+\renewcommand{\thepage}{}
+\end{titlepage}
+\pagenumbering{arabic}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %
+Sahhaf et al.~\cite{STRSCPD15} also studied placement of network
+service chains.  They presented an algorithm which minimizes the cost
+of the placement and is based on integer linear programming.  They
+also present a heuristic in order to cope with the non-practical
+running time of the first algorithm.
+%
 Rost and Schmid~\cite{RostSchmid16} considered variant of this
@@
 %
-\fix{Sahhaf et al.~\cite{SAHHAF2015492} studied a generalization of the Virtual Network Embedding
-Problem where each network function can be decomposed into multiple network function graphs.
-They proposed two novel approaches to use service
-decompositions at the time of service embedding (i) an
-ILP-based algorithm that finds an optimal embedding and (ii) a heuristic-based algorithm to cop with the scalability issues of the first algorithm.}
-
-Even, Medina, and Patt-Shamir~\cite{EMP16} studied online path
-computation and VNF placement.  They considered compound requests that
-arrive in an online manner.  Each request is a flow with a
-specification of routing and VNF requirements which is represented by
-a directed acyclic graph (DAG) whose vertices are VNFs.  Each VNF can
-be performed by a specified subset of servers in the system.  Upon
-arrival of a request, the algorithm either rejects the request or
-accepts it with a specific routing and VNF assignment, under given
-server capacity constraints.  Each request has a benefit that is
-gained if it is accepted, and the goal is to maximize the total
-benefit gained by accepted requests.
+Rost and Schmid~\cite{RostSchmid18} considered a more general version
+of the problem in which requests are graphs that should be placed
+within the physical graph.  They provided hardness of approximation
+results for this problem.
+
+Even, Medina, and Patt-Shamir~\cite{EMP16} (see, also~\cite{EMP18})
+studied online path computation and VNF placement.  They considered
+compound requests that arrive in an online manner.  Each request is a
+flow with a specification of routing and VNF requirements which is
+represented by a directed acyclic graph (DAG) whose vertices are VNFs.
+Each VNF can be performed by a specified subset of servers in the
+system.  Upon arrival of a request, the algorithm either rejects the
+request or accepts it with a specific routing and VNF assignment,
+under given server capacity constraints.  Each request has a benefit
+that is gained if it is accepted, and the goal is to maximize the
+total benefit gained by accepted requests.
 %
@@
 cactus graphs with constant link capacities.
+%
+Amiri et al.~\cite{AFS18} considered the unordered case, and they
+presneted a polynomial-time algorithm for graphs of bounded treewidth.
+%
+Amiri et al.~\cite{AFJPS18} studied the ordered case, and they
+gave algorithms for special networks.
+%
+An overview of waypoint routing is given in ~\cite{AFJS18}.
+
+%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Preliminaries}
@@
 %
-  % Without loss of generality, we assume that $p(s) = p(t) = 0$.
+  Without loss of generality, we assume that $p(s) = p(t) = 0$.
 
@@
 %
+%   Without loss of generality, we assume that $p(s) = p(t) = 0$.  
+%
   The DAG $\calG$ has a source node $\sigma \in \calV$ and a
@@
 %
-\fix{Without loss of generality, we assume that $p(s) = p(t) = p(\sigma) = p(\tau) =
-  0$}.  Each edge $\eps \in \calE$ has a bandwidth demand $b(\eps)$.
+  Without loss of generality, we assume that $p(\sigma) = p(\tau) =
+  0$.  Each edge $\eps \in \calE$ has a bandwidth demand $b(\eps)$.
 
@@
 
-\begin{figure}[]
+\begin{figure}[t]
 \centering
@@
 }
-\caption{\fix{
-  An example of an \scp instance and a solution.
-  The left DAG represents the collection of alternative service chains as requested by the client.
-  Each node of this graph represent a single service and the number written inside the node is the processing demand of this service.
-  The value on the arcs are the minimum bandwidth required to transmit the output of one service to the next service.
-  \\
-  The right DAG represents a physical network. 
-  The numbers on the nodes represent processing capacities and the number on the arcs represent the available bandwidth.
-  \\
-  The blue, dashed, arcs represent the chosen service chain and a physical route respectively, and the dotted, purple, arrows show a placement of this service chain into the physical route.
-}}
+\caption{An example of an \scp instance and a solution.
+%
+The DAG on the left is the virtual DAG, and the numbers on its
+vertices and edges are their demands.
+%
+The DAG on the right is the physical DAG, and the numbers of its
+vertices and edges are their capacities.
+%
+The dashed blue line on the left is the chosen the chosen virtual
+path, while the dashed blue line on the right is the chosen physical
+path.  Dotted lines are used to represent the allocation of each set
+of virtual vertices to each physical vertex along the path.
+%
+}
 \label{fig:solution}
@@
 %
-\fix{
-Note that any service chain is of the form $\sigma, \gamma_1, \dots, \gamma_n, \tau$ where $\gamma_i \in \{\alpha_i, \beta_i\}$. 
-This implies that given a service chain, the sum of its cost and its total processing demand equals to $\sum_i a_i$ and thus (as forced by the processing capacity of $v$), $\set{a_1, \ldots, a_n} \in \textsc{Partition}$ if and only if there exists a solution whose cost is $\half \sum_i a_i$.
-}
+Furthermore, observe that any service chain must be of the form
+$\sigma, \gamma_1, \ldots, \gamma_n, \tau$, where $\gamma_i \in
+\set{\alpha_i,\beta_i}$.  By the construction, we have that the total
+processing demands plus the total cost is $\sum_i a_i$.  Since $p(v) =
+\half \sum_i a_i$, we have that the total cost is at least $\sum_i
+a_i$.  Hence, it is not hard to verify that $\set{a_1, \ldots, a_n}
+\in \textsc{Partition}$ if and only if there exists a solution whose
+cost is $\half \sum_i a_i$.
 \end{proof}
 
-\begin{figure}[]
+\begin{figure}[t]
   \centering
@@
   The cost function enforces each $\alpha_i$ to be placed either in
-  $v_i^-$ or in $v_i^+$.  In the former case this placement incurs no
+  $v_i^-$ or in $v_i^+$.  In the former case this placement incure no
   cost but additional latency of $a_i$, in the later case there will
@@
 costs, namely without the assumption that costs are polynomially
-bounded.  
-\fix{
-We use similar techniques as in the  FPTAS for the
-\textsc{Minimum Knapsack} problem~\cite{islam2009approximation}.
-}
+bounded.  Our algorithm is similar to the FPTAS for the
+\textsc{Minimum Knapsack} problem (see \cite{KPP04}[Chapter 13] and
+references therein).
 
@@
      \sum_{\alpha}
-       \paren{ c(\alpha,f(\alpha)) \cdot \frac{n}{\eps c_{\max}} + 1} \\
+       \paren{ \frac{c(\alpha,f(\alpha))}{c_{\max}} \cdot \frac{n}{\eps} + 1} \\
 %& =    c(f) + \frac{\eps c_{\max}}{n} \cdot n \\
@@
 \end{align*}
-where the second inequality is due to the optimally of $f'$ with
+where the second inequality is due to the optimality of $f'$ with
 respect to $c'$.
@@
 \begin{proof}
-Given $\eps>0$, run the dynamic programming algorithm from
+First, observe that there are $\abs{\calV} \cdot \abs{V}$ candidates
+for the value of $c_{\max}$, one for each pair of virtual function and
+physical vertex.  
+%
+Hence, given $\eps>0$, we run the dynamic programming algorithm from
 Section~\ref{sub:DPL} $\abs{\calV} \cdot \abs{V}$ times, once for each
 possible value of $c_{\max}$, and choose the best placement.
-\fix{Since we check all the possible values of $c_{max}$ and for each such value we compute an optimal solution with respect to $c'$, then} according to Lemma~\ref{lemma:guess} the best placement is $(1+\eps)$-approximate.
+%
+According to Lemma~\ref{lemma:guess} the placement that was computed
+for the value of $c_{\max}$ that corresponds to an optimal solution is
+$(1+\eps)$-approximate.  Hence, the best placement is also
+$(1+\eps)$-approximate.
+%
 The running time is polynomial in the input size and in $1/\eps$.
@@
 
+Before presenting our algorithms we assume without loss of generality
+that each vertex in the network is found on a path from $s$ to $t$,
+since otherwise it can be eliminated.  In particular, it follows that
+the degree of any vertex, besides maybe $s$ and $t$, is at least $2$.
+In addition this implies that the network is connected.
+
 %%%%%
@@
 
-\fix{We assume w.l.o.g that the physical network does not contain any leafs (beside, maybe, $s$ and $t$), otherwise, these nodes, for the purpose of our computation, can be safely removed from the network.}
 Our randomized algorithm consists of $k!$ iterations of the following
@@
 %
-Let $\pi:N \to N$ be a random permutation.  We direct the edges
-according to $\pi$.  
-Observe that each edge $e \in E$ is found on a
-simple path between two neighborly nodes $v_e$ and $v'_e$, in which
-all internal vertices are in $V \setminus N$.  The edge $e$ is
+Let $\pi:N \to N$ be a random permutation.  Define $\pi(s) = 0$, and
+$\pi(t) = N+1$.  We direct the edges according to $\pi$.
+%
+Observe that each edge $e \in E$ is found on a simple path between two
+neighborly nodes $v_e$ and $v'_e$, between $v_e = s$ and a neighborly
+node $v'_e$, or between neighborly node $v_e$ and $v_e = t$.  In this
+path all internal vertices are in $V \setminus N$.  The edge $e$ is
 directed towards $v_e$, if $\pi(v_e) > \pi(v'_e)$, and otherwise it is
@@
   permutation and the dashed path represents a path of an optimal
-  placement.  The orientated physical network is on the right.  It is
+  placement.  The oriented physical network is on the right.  It is
   enough that the internal ordering of the nodes on the dashed path is
@@
 \begin{proof}
-Consider an optimal placement with at most $k$ neighborly vertices,
-and let $\pi'$ be the permutation it induces on the neighborly
-vertices in the physical path.
-%
-If the random permutation $\pi$ orders the neighborly vertices
-correctly, i.e., if $\pi(v) = \pi'(v)$, for every $v \in N$, then the
+Consider an optimal placement with at most $k$ neighborly vertices
+whose set is denoted by $N'$, and let $\pi'$ be the permutation it
+induces on the neighborly vertices in the physical path.
+%
+If the random permutation $\pi$ orders the neighborly vertices in $N'$
+correctly, i.e., if $\pi(v) = \pi'(v)$, for every $v \in N'$, then the
 optimal placement is feasible with respect to $G_\pi$.  Hence, the
@@
 with respect to $G$.
-%
-The permutation $\pi$ agrees with $\pi'$ with probability $1/k!$, and
-the probability that $\pi$ agrees with $\pi'$ in $k!$ iterations is $1
-- (1 - 1/k!)^{k!} \geq 1 - e^{-1}$.  
-This means that the probability to fail in a single attempt is less than $e^{-1}$.
-\fix{If one makes $i$ attempts then the probability to fail in all those attempts is less than $e^{-i}$ so using $\ln n$ repetitions reduces the probability to fail to less than $\frac{1}{n}$ and increases the probability to succeed to at least $1 - \inv{n}$.
-}
+
+The permutation $\pi$ agrees with $\pi'$ with probability $1/\abs{N'}!
+\geq 1/k!$, and thus the probability that $\pi$ agrees with $\pi'$ in
+$k!$ independent iterations is at least $1 - (1 - 1/k!)^{k!} \geq 1 -
+e^{-1}$.  One may amplify the success probability to $1 - \inv{n}$
+using $O(\log n)$ repetitions: $1 - (1 - 1/k!)^{\ln n \cdot k!} \geq 1
+- e^{-\ln n} = 1 - 1/n$.
 \end{proof}
@@
 described above, and then executes the FPTAS for DAGs given in
-Section~\ref{sub:fptas}.  
-Thus the running time of the algorithm is $O(k! \cdot \text{\rm poly}(n))$.
+Section~\ref{sub:fptas}.  Thus the running time of the algorithm is
+$O(k! \cdot \text{\rm poly}(n))$.
 %
@@
 
-\fix{
-A biconnected component (block) of an undirected graph is a maximal biconnected subgraph.
-Any connected graph decomposes into a tree of biconnected components called the block-cut tree of the graph. The blocks are attached to each other at shared vertices called cut vertices.
-Computing such a tree can be done in linear time~\cite{HopcroftTarjan73}.
-}
-The orientation works as follow.  
-Given an undirected graph $G = (V,E)$, we first compute its block-cut tree.
-%
-Then on the unique path from $s$ to $t$ in the block-cut tree we
-internally orient each block arbitrarily to produce a DAG.  Note that
-if $B_1, \ldots, B_\ell$ are the blocks of $G$ on the path from $s$ to
-$t$ then the first and last vertices with respect to each block are
-known and only the order of the internal neighborly vertices in each
-block is needed to be determined, thus, we can find all relevant
-orientations by repeating the process above $\Pi_{i = 1}^\ell
+Given a connected graph $G$, a \emph{bi-connected component} (or a
+\emph{block}) in $G$ is a maximal bi-connected subgraph of $G$.  Any
+connected graph can be decomposed into bi-connected subgraphs that
+form a tree called a \emph{block-cut tree}.  In this tree every vertex
+is a block of $G$ and two blocks are attached if they share a vertex,
+which is called a \emph{cut-vertex}.
+%
+Computing such a tree can be done in linear
+time~\cite{HopcroftTarjan73}.
+
+The orientation works as follow.  Given an undirected graph $G =
+(V,E)$, we first compute its \emph{block-cut} tree.  Then on the
+unique path from $s$ to $t$ in the block-cut tree we internally orient
+each block arbitrarily to produce a DAG.
+%
+Note that if $B_1, \ldots, B_\ell$ are the blocks of $G$ on the path
+from $s$ to $t$ then the first and last vertices with respect to each
+block are known and only the order of the internal neighborly vertices
+in each block is needed to be determined, thus, we can find all
+relevant orientations by repeating the process above $\Pi_{i = 1}^\ell
 \abs{N_i}$ times, where $N_i$ is the set of internal neighborly
@@
 
-\fix{We say that two (physical) paths are \emph{internal vertex disjoint} if they do not have any internal (all vertices beside the first and last one) vertex in common.}
 Formally, given a physical network, a virtual specification, and a
@@
 collection of $r$ placements, $f_1,\ldots,f_r$, that correspond to $r$
-internal vertex disjoint physical paths.  In the fault tolerant
+internal vertex disjoint physical paths.%
+\footnote{Two paths are internal vertex disjoint is they do not share
+  a vertex apart from, maybe, the first and last vertices on the
+  paths.}
+%
+In the fault tolerant
 version of \scp we are given $r$ costs functions $c_1,\ldots,c_r$, and
@@
 %
-Recall that $\cost^i_{v_i}(\gamma_i,\beta_i)$ is the cost, with
-respect to $c_i$, of a minimum cost path from $\gamma_i$ to $\beta_i$
-whose total processing requirement can be handled by $v_i$.
+Recall that $\cost^j_{v_j}(\gamma_j,\beta_j)$ is the cost, with
+respect to $c_j$, of a minimum cost path from $\gamma_j$ to $\beta_j$
+whose total processing requirement can be handled by $v_j$, where $j
+\in \set{1,2}$.
 %
@@
 \]
-Otherwise, for $v_1 \neq v_2$ or $v_1 = v_2 = t$, such that $v_1, v_2 \in L_i$, for some
-$i$, we have
+Otherwise, for $v_1 \neq v_2$ of $v_1 = v_2 = t$, such that $v_1, v_2
+\in L_i$, for some $i$, we have
 \[
@@
 \begin{itemize}
-  \item $\gamma_i \preceq \alpha_i$,
-  \item $\beta_i \preceq \alpha_i$ or $\beta_i = \zeta_i$,
-  \item $(\gamma_i,\beta_i) \in \calE$,
+  \item $\gamma_j \preceq \alpha_j$,
+  \item $\beta_j \preceq \alpha_j$ or $\beta_j = \zeta_j$,%
+\footnote{Note that if $\beta_j = \zeta_j$, then
+  $\cost^j_{v_j}(\zeta_j \to \alpha_j) = 0$.}
+  \item $(\gamma_j,\beta_j) \in \calE$,
   \item $u_1 \neq u_2$ or $u_1 = u_2 = s$,
-  \item $(u_i,v_i) \in E$, and
-  \item $b(\gamma_i,\beta_i) \leq b(u_i,v_i)$
+  \item $(u_j,v_j) \in E$, and
+  \item $b(\gamma_j,\beta_j) \leq b(u_j,v_j)$
 \end{itemize}
@@
 
-The running time is polynomial, since there is a polynomial number of
-states and the computation of $\cost^i_{v_i}(\gamma_i,\beta_i)$ can be
-done in polynomial time, as shown in
-Section~\ref{sec:chain-placement}.  The above algorithm computes the
-cost of an optimal $2$-robust placement, and as usual, one may compute
-an optimal $2$-robust placement using standard techniques.
+If all costs are polynomially bounded, then computation of
+$\ft((\alpha_1,\zeta_1),(\alpha_2,\zeta_2),v_1,v_2)$ can be done in
+polynomial time, since the minimum is taken over a polynomial number
+of candidates and the computation of $\cost^j_{v_j}(\gamma_j,\beta_j)$
+can be done in polynomial time, as shown in
+Section~\ref{sec:chain-placement}.  Hence, the overall running time is
+polynomial.
+%
+The above algorithm computes the cost of an optimal $2$-robust
+placement, and as usual, one may compute an optimal $2$-robust
+placement using standard techniques.
 
@@
 \end{theorem}
-
-\begin{proof}
-  \fix{From the above discussions it follows that the algorithm finds an optimal robust embedding with respect to c', using Lemma~\ref{lemma:guess} we know that its cost is at most $(1 + \varepsilon)$ times the cost of the optimal robust embedding, for every $\varepsilon > 0$.}
-\end{proof}
 
@@
 such that the total latency of the two placements is no more than
-$2L$.  Such a solution is guaranteed to be optimal in terms of costs.
-It is also easy to see that in such solution at least one of the
+$2L$.  This is done in a manner which is similar to what was done in
+Section~\ref{sub:DPL}, but with an upper bound on the total latency of
+both paths.  Such a solution is guaranteed to be optimal in terms of
+costs.  Also, if the total latency is $2L$, then at least one of the
 placements has lower latency than $L$ and the other one has latency
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusion}
-\fix{%
-Network service chaining is a service concept which has gained much interest from both practitioners and researchers, it promises increased flexibility and cost-efficiency for future carrier networks.
-In this model clients request compound services from the network provider which translate into a service chain that need to be embedded into the physical network.
-To ensure efficient utilization of the underline physical network relaible algorithms are needed.
-}
-
-\fix{%
-In this paper we propose an efficient algorithm that finds an optimal embedding for a single request.
-This algorithm works, however, only when the underline network is acyclic.
-For general networks we propose an algorithm that finds an optimal embedding with a running time that depends on the topology of the network, more specifically on the number of nodes in the network with more than two connections.
-We also propose a heuristic that improves the running time of the last algorithm, for cactus networks, for example, this heuristic is guaranteed to run in polynomial time.
-}
-
-\fix{%
-Some questions regarding service chain placement remain open. 
-Some of these questions are (i) how should we handle multiple (concurrent) requests?
-(ii) can we find better solutions if we allow embedding a service chain on a walk instead of a path?
-(iii) is there an efficient (approximation) algorithm that works on real world networks?\footnote{As even the feasibilty problem for general networks is NP-hard some further assumptions need to be made in order to answer this question affirmatively.}
-We believe that our results and techniques can serve as a starting point for future work dealing with those questions.
-}
+
+Chaining of virtual network functions is a service concept which has
+gained much attention from both practitioners and researchers, since
+it promises increased flexibility and cost-efficiency for future
+carrier networks.
+%
+In this setting a client requests a compound service from the network
+provider which translates into a service chain that needs to be
+embedded into the physical network.  To ensure efficient utilization
+of the underline physical network, the placement of the service chain
+should be done carefully and efficiently.
+%
+In this paper we define a model for service chain placement in SDNs.
+We show that the placement problem is computationally hard even in
+very simple cases.  Given these hardness results, we propose an FPTAS
+for the placement problem in acyclic physical networks.  For general
+networks we propose a randomized algorithm and an fixed parameter
+algorithm whose running time depends on the topology of the network,
+more specifically on the number of nodes in the network with more than
+two neighbors.  Finally, we extend our results to a fault tolerant
+setting.
+
+Several questions regarding service chain placement remain open:
+\begin{inparaenum}[(i)]
+\item Are there (practical) networks (other than DAGs) that are
+  computationaly easy?
+\item Can our results be extended to the case where the service chain
+  is placed within a walk instead of a path?
+\item Can multiple requests be treated within our model?
+\end{inparaenum}
+We believe that our results and techniques can serve as a starting
+point for future work dealing with those questions.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%\section{Extensions}
-
-%Costs by sets of VNFS
+\subsection*{Acknowledgement}
+
+We thank Reuven Bar-Yehuda for helpful discussions.
 
@@
 
-\subsection*{Acknowledgement}
-
-We thank Reuven Bar-Yehuda for helpful discussions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{elsarticle-num} 
+\bibliographystyle{abbrv}
 \bibliography{chain}
+
 \end{document}

### 2019-05-24 src/chain.tex
fix model
final DAM

@@
 %
-An overview of waypoint routing is given in ~\cite{AFJS18}.
+An overview of waypoint routing is given in \cite{AFJS18}.
 
@@
 %
-  Without loss of generality, we assume that $p(s) = p(t) = 0$.
+%  Without loss of generality, we assume that $p(s) = p(t) = 0$.
 
@@
 %
-%   Without loss of generality, we assume that $p(s) = p(t) = 0$.  
+  Without loss of generality, we assume that $p(s) = p(t) = 0$.  
 %
@@
 internal vertex disjoint physical paths.%
-\footnote{Two paths are internal vertex disjoint is they do not share
+\footnote{Two paths are internal vertex disjoint if they do not share
   a vertex apart from, maybe, the first and last vertices on the
